### 2024-10-19 distinction.qmd
Let's go

---
title: "Jilbert's Distinction Centrality"
execute: 
  eval: true
  echo: true
  output: true
  warning: false
  message: false
format: 
   html:
      code-line-numbers: true
---

```{r}
   library(igraph)
   library(ggraph)
```

According to @jilbert24, the Distinction Centrality of a node is a function of the status of each focal node and the degree of status independence of its alters.

It is given by:

$$
   D_i = \alpha S_i(G)  + (1-\alpha) \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
$$

Where $S_i(G)$ is the (normalized to have maximum 1.0) eigenvector centrality of node $i$ computed in the full graph $G$, $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$. The Distinction of a node thus increases with its own status and decreases to the extent that others would gain status if that node was not around.

```{r}
   plot.graph <- function(x, l) { #plotting function
      library(ggraph)
      if (is.null(V(x)$name) == TRUE) {
         n <- 1:vcount(x)
         c <- "white"
         s <- 12
         }
      if (is.null(V(x)$name) == FALSE) {
         n <- V(x)$name
         c <- "blue"
         s <- 0
         }
      p <- ggraph(x, layout = l)
      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
      p <- p + geom_node_point(aes(x = x, y = y), size = s, color = "tan2") 
      p <- p + geom_node_text(aes(label = n), size = 6, color = c)
      p <- p + theme_graph() 
   return(p)
   }

   tab.cent <- function(x) { #table function
   library(kableExtra)
   t <- kbl(x, 
       digits = 2, 
       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
   return(t)
   }

```

```{r}
    g1 <- make_star(7, mode = "undirected") # star graph
    g2 <- g1 + edge(2,3)
    g2 <- g2 + edge(2,4)
    g2 <- g2 + edge(3,4)
    g2 <- g2 + edge(5,6)
    g2 <- g2 + edge(5,7)
    g2 <- g2 + edge(6,7) # structural fold
    g3 <- g1 + edge(2,3)
    g3 <- g3 + edge(3,4)
    g3 <- g3 + edge(5,6)
    g3 <- g3 + edge(5,7) # intra-connected clusters
    g4 <- g3 + edge(2,7) # inter-connected clusters
```

```{r}
#| fig-cap: "A star graph with seven nodes."
#| fig-height: 5
#| fig-width: 5
   plot.graph(g1, "star")
```

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph."
   tab.cent(distinction(g1))
```

```{r}
#| fig-cap: "A structural fold with seven nodes."
#| fig-height: 5
#| fig-width: 5
   plot.graph(g2, "kk")
```

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
   tab <- data.frame(distinction(g2)[1:4])
   tab.cent(tab)
```

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
   tab <- data.frame(distinction(g3)[1:4])
   tab.cent(tab)
```

```{r}
#| fig-height: 5
#| fig-width: 5
   plot.graph(g3)
```

```{r}
   library(networkdata)
   g <- flo_marriage
   plot.graph(g, l = "kk")
```

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
   tab <- data.frame(distinction(g)[1:4])
   tab.cent(tab)
```

```{r}
   library(kableExtra)
   kbl(d[,c(1, 3:5)], 
       digits = 2, 
       col.names = c("Node", "Distinction", "Status", "Uniqueness")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
```

Jilbert's Distinction Equivalence

### 2024-10-19 distinction.R

@@ -1,0 +1,33 @@
+distinction <- function(x) { #distinction centrality function
+   n <- vcount(x)
+   V(x)$name <- 1:n
+   s <- eigen_centrality(x)$vector
+   d <- 0
+   u <- 0
+   for (i in 1:n) {
+      j <- names(neighbors(x, i))
+      x.d <- x - i
+      c <- as.numeric(is_connected(x.d) == TRUE)
+      e <- as.numeric(ecount(x.d) != 0)
+      if (c == 1 & e == 1) { #connected non-empty graph
+         s.a <- eigen_centrality(x.d)$vector[j]
+      } #end if
+      else if (c == 0 & e == 0) { #empty graph
+         s.a <- 0
+      } #end else 1
+      else if (c == 0 & e == 1) { #disconnected non-empty graph
+         C <- components(x.d)$membership
+         s.a <- eigen_centrality(subgraph(x.d, which(C == 1)))$vector
+         for (k in 2:max(C)) {
+            s.a <- c(s.a, eigen_centrality(subgraph(x.d, which(C == k)))$vector)
+         }
+         s.a <- s.a[j]
+      } #end else 2
+      u[i] <- sum(s.a) * 1/length(s.a) #average neighbor centrality
+      d[i] <- s[i] - u[i] #distinction centrality
+   } #end i for loop
+   d[is.na(d)] <- 0
+   u[is.na(u)] <- 0
+   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u)
+   return(dat)
+} #end function

### 2024-10-19 distinction.qmd
stuff

@@
       code-line-numbers: true
+bibliography: networks.bib
 ---
 
-```{r}
+```{r Loading Functions}
    library(igraph)
    library(ggraph)
+   library(here)
+   library(networkdata)
+   source("distinction.R")
 ```
@@
 $$
-   D_i = \alpha S_i(G)  + (1-\alpha) \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
+   D_i = S_i(G)  + \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
 $$
@@
 
-```{r}
-   plot.graph <- function(x, l) { #plotting function
+```{r Custom Functions}
+#| echo: false
+   plot.graph <- function(x, l, vs = 12, ts = 6) { #plotting function
       library(ggraph)
+      d <- distinction(x)$d
+      nc <- rep("", length(d))
+      nc[which(d < -0.05)] <- "red"
+      nc[which(d > 0.05)] <- "blue"
+      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
       if (is.null(V(x)$name) == TRUE) {
          n <- 1:vcount(x)
-         c <- "white"
-         s <- 12
+         tc <- "white"
+         s <- vs
          }
@@
          n <- V(x)$name
-         c <- "blue"
-         s <- 0
+         tc <- nc
+         vs <- 0
          }
@@
       p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
-      p <- p + geom_node_point(aes(x = x, y = y), size = s, color = "tan2") 
-      p <- p + geom_node_text(aes(label = n), size = 6, color = c)
+      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
+      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
       p <- p + theme_graph() 
@@
    t <- kbl(x, 
-       digits = 2, 
+       digits = 2, row.names = FALSE,
        col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
@@
     g2 <- g2 + edge(6,7) # structural fold
-    g3 <- g1 + edge(2,3)
+    g3 <- g1 + edge(2,4)
     g3 <- g3 + edge(3,4)
@@
    plot.graph(g1, "star")
+   ggsave(here("Plots", "star.png"), width = 6, height = 6)
 ```
@@
    plot.graph(g2, "kk")
+   ggsave(here("Plots", "sfold.png"), width = 6, height = 6)
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g2)[1:4])
-   tab.cent(tab)
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold."
+   tab.cent(distinction(g2))
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g3)[1:4])
-   tab.cent(tab)
+#| fig-cap: "Intraconnected Clusters."
+#| fig-height: 5
+#| fig-width: 5
+   plot.graph(g3, "star")
+   ggsave(here("Plots", "intra-clusters.png"), width = 6, height = 6)
 ```
@@
 ```{r}
-#| fig-height: 5
-#| fig-width: 5
-   plot.graph(g3)
+#| tbl-cap: "Distinction Centrality Scores of Nodes in Intraconnected Clusters."
+   tab.cent(distinction(g3))
 ```
@@
 ```{r}
-   library(networkdata)
-   g <- flo_marriage
-   plot.graph(g, l = "kk")
+#| fig-cap: "Interconnected Clusters."
+#| fig-height: 5
+#| fig-width: 5
+   plot.graph(g4, "star")
+   ggsave(here("Plots", "inter-clusters.png"), width = 6, height = 6)
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g)[1:4])
-   tab.cent(tab)
+#| tbl-cap: "Distinction Centrality Scores of Nodes in Interconnected Clusters."
+   tab.cent(distinction(g4))
 ```
@@
 ```{r}
-   library(kableExtra)
-   kbl(d[,c(1, 3:5)], 
-       digits = 2, 
-       col.names = c("Node", "Distinction", "Status", "Uniqueness")) %>% 
-      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
+#| fig-cap: "Regular Graph."
+#| fig-height: 5
+#| fig-width: 5
+   set.seed(1234)
+   g5 <- sample_k_regular(7, 4)
+   plot.graph(g5, "circle")
+   ggsave(here("Plots", "regular.png"), width = 6, height = 6)
+```
+
+```{r}
+#| tbl-cap: "Distinction Centrality Scores of Nodes in a Regular Graph."
+   tab.cent(distinction(g5))
+```
+
+```{r}
+#| fig-cap: "Karate Club Graph."
+#| fig-height: 8
+#| fig-width: 8
+   set.seed(1234)
+   plot.graph(karate, "dh", vs = 8, ts = 4)
+   ggsave(here("Plots", "karate.png"), width = 6, height = 6)
+```
+
+```{r}
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Karate Club."
+   tab.cent(distinction(karate))
+```
+
+```{r}
+#| fig-cap: "Florentine Families Graph."
+#| fig-height: 12
+#| fig-width: 12
+   set.seed(1234)
+   iso <- which(degree(flo_marriage) == 0)
+   g <- delete_vertices(flo_marriage, iso)
+   plot.graph(g, "star", ts = 8)
+   ggsave(here("Plots", "flo-marriage.png"), width = 12, height = 12)
+```
+
+```{r}
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Florentine Families."
+   tab.cent(distinction(g))
 ```

### 2024-10-19 distinction.R

@@ -1,6 +1,5 @@
 distinction <- function(x) { #distinction centrality function
    n <- vcount(x)
-   V(x)$name <- 1:n
    s <- eigen_centrality(x)$vector
    d <- 0
    u <- 0
@@ -11,23 +10,29 @@ distinction <- function(x) { #distinction centrality function
       e <- as.numeric(ecount(x.d) != 0)
       if (c == 1 & e == 1) { #connected non-empty graph
          s.a <- eigen_centrality(x.d)$vector[j]
-      } #end if
+         } #end if
       else if (c == 0 & e == 0) { #empty graph
          s.a <- 0
-      } #end else 1
+         } #end else 1
       else if (c == 0 & e == 1) { #disconnected non-empty graph
          C <- components(x.d)$membership
          s.a <- eigen_centrality(subgraph(x.d, which(C == 1)))$vector
          for (k in 2:max(C)) {
             s.a <- c(s.a, eigen_centrality(subgraph(x.d, which(C == k)))$vector)
-         }
+            }
          s.a <- s.a[j]
-      } #end else 2
+         } #end else 2
       u[i] <- sum(s.a) * 1/length(s.a) #average neighbor centrality
       d[i] <- s[i] - u[i] #distinction centrality
    } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
-   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u)
+   if (is.null(V(x)$name) == TRUE) {
+      lab <- 1:vcount(x)
+      }
+   else if (is.null(V(x)$name) == FALSE) {
+      lab <- V(x)$name
+      }
+   dat <- data.frame(n = lab, d = d, s = s, u = u)
    return(dat)
 } #end function

### 2024-10-19 distinction.R
okay

@@ -1,5 +1,6 @@
 distinction <- function(x) { #distinction centrality function
    n <- vcount(x)
+   V(x)$name <- 1:vcount(x)
    s <- eigen_centrality(x)$vector
    d <- 0
    u <- 0

### 2025-01-26 index.qmd
make it so

--- 2024-10-19 distinction.qmd
@@
    library(networkdata)
+   library(ggpubr)
    source("distinction.R")
@@
 
-   tab.cent <- function(x) { #table function
+   tab.cent <- function(x, d = 3) { #table function
    library(kableExtra)
    t <- kbl(x, 
-       digits = 2, row.names = FALSE,
+       digits = d, row.names = FALSE,
        col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
@@
    }
-
 ```
@@
 ```{r}
+#| fig-cap: "Small World Graph."
+#| fig-height: 5
+#| fig-width: 5
+   set.seed(1234)
+   g6 <- sample_smallworld(dim = 1, 7, 2, 0.05)
+   plot.graph(g6, "circle")
+   ggsave(here("Plots", "sw.png"), width = 6, height = 6)
+```
+
+```{r}
+#| tbl-cap: "Distinction Centrality Scores of Nodes in a Small World Graph."
+   tab.cent(distinction(g6))
+```
+
+```{r}
 #| fig-cap: "Karate Club Graph."
@@
 
+```{r}
+   p <- seq(0.1, 0.9, 0.01)
+   r <- rep(0, length(p))
+   for (i in 1:length(p)) {
+      set.seed(123)
+      g <- sample_smallworld(dim = 1, 15, 3, p[i]) 
+      d <- distinction(g)$u
+      b <- betweenness(g)
+      r[i] <- cor(d, b)
+      }
+   dat <- data.frame(p, r)
+   ggscatter(data = dat, "p", "r", add = "loess") 
+```
+
 Jilbert's Distinction Equivalence

### 2025-01-26 distinction.R

@@ -1,14 +1,15 @@
 distinction <- function(x) { #distinction centrality function
-   n <- vcount(x)
-   V(x)$name <- 1:vcount(x)
+   if (is.null(V(x)$name) == TRUE) {
+      V(x)$name <- 1:vcount(x)
+      }
    s <- eigen_centrality(x)$vector
    d <- 0
    u <- 0
-   for (i in 1:n) {
+   for (i in 1:vcount(x)) {
       j <- names(neighbors(x, i))
       x.d <- x - i
-      c <- as.numeric(is_connected(x.d) == TRUE)
-      e <- as.numeric(ecount(x.d) != 0)
+      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
+      e <- as.numeric(ecount(x.d) != 0) #checking for empty
       if (c == 1 & e == 1) { #connected non-empty graph
          s.a <- eigen_centrality(x.d)$vector[j]
          } #end if
@@ -28,12 +29,6 @@ distinction <- function(x) { #distinction centrality function
    } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
-   if (is.null(V(x)$name) == TRUE) {
-      lab <- 1:vcount(x)
-      }
-   else if (is.null(V(x)$name) == FALSE) {
-      lab <- V(x)$name
-      }
-   dat <- data.frame(n = lab, d = d, s = s, u = u)
+   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u)
    return(dat)
 } #end function

### 2025-03-01 index.qmd
do it

--- 2024-10-19 distinction.qmd
@@
       code-line-numbers: true
+bibliography: networks.bib
 ---
 
-```{r}
+```{r Loading Functions}
    library(igraph)
    library(ggraph)
+   library(here)
+   library(networkdata)
+   library(ggpubr)
+   source("distinction.R")
 ```
 
-According to @jilbert24, the Distinction Centrality of a node is a function of the status of each focal node and the degree of status independence of its alters.
-
-It is given by:
+According to @jilbert24, the Distinction Centrality ($D_i$) of a node is given by the difference between the *status* ($S_i(G)$) and the *constraint* ($C_i(G)$) experienced by each node:
 
 $$
-   D_i = \alpha S_i(G)  + (1-\alpha) \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
+   D_i = S_i(G)  - C_i(G)
 $$
 
-Where $S_i(G)$ is the (normalized to have maximum 1.0) eigenvector centrality of node $i$ computed in the full graph $G$, $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$.
+Status is measured using the usual Bonacich eigenvector centrality (normalized to have maximum 1.0) computed in the full graph $G$.
+Constraint, in turn, is given by the average status of $i$'s neighbor in the *node deleted subgraph* that excludes $i$.
+
+$$
+C_i(G) = \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
+$$
+
+Where $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$.
+Nodes are more constrained to the extent that others gain status in their absence.
 The Distinction of a node thus increases with its own status and decreases to the extent that others would gain status if that node was not around.
 
-```{r}
-   plot.graph <- function(x, l) { #plotting function
+The normalized version of Distinction Centrality ($D^*$) multiplies each node's status score by the parameter $\theta$, which is ratio of the average of constrain scores and the average of status scores of each node in the the network:
+
+$$
+\gamma = \frac{\frac{1}{N}\sum_i C_i(G)}{\frac{1}{N}\sum_i S_i(G)}
+$$
+
+The normalized distinction is then given by:
+
+$$
+D^*_i = \gamma S_i(G)  - C_i(G)
+$$
+
+```{r Custom Functions}
+#| echo: false
+   plot.graph <- function(x, l, vs = 12, ts = 6) { #plotting function
       library(ggraph)
+      d <- distinction(x)$d
+      nc <- rep("", length(d))
+      nc[which(d < -0.05)] <- "red"
+      nc[which(d > 0.05)] <- "blue"
+      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
       if (is.null(V(x)$name) == TRUE) {
          n <- 1:vcount(x)
-         c <- "white"
-         s <- 12
+         tc <- "white"
+         s <- vs
          }
@@
       p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
-      p <- p + geom_node_point(aes(x = x, y = y), size = s, color = "tan2") 
-      p <- p + geom_node_text(aes(label = n), size = 6, color = c)
+      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
+      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
+      p <- p + theme_graph() 
+   return(p)
+   }
+   plot.graph.norm <- function(x, l, vs = 12, ts = 6) { #plotting function
+      library(ggraph)
+      d <- distinction(x, norm = TRUE)$d
+      nc <- rep("", length(d))
+      nc[which(d < -0.05)] <- "red"
+      nc[which(d > 0.05)] <- "blue"
+      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
+      if (is.null(V(x)$name) == TRUE) {
+         n <- 1:vcount(x)
+         tc <- "white"
+         s <- vs
+         }
+      if (is.null(V(x)$name) == FALSE) {
+         n <- V(x)$name
+         tc <- nc
+         vs <- 0
+         }
+      p <- ggraph(x, layout = l)
+      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
+      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
+      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
       p <- p + theme_graph() 
@@
 
-   tab.cent <- function(x) { #table function
+   tab.cent <- function(x, d = 3) { #table function
    library(kableExtra)
    t <- kbl(x, 
-       digits = 2, 
+       digits = d, row.names = FALSE,
        col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
@@
 ```{r}
-#| fig-cap: "A star graph with seven nodes."
-#| fig-height: 5
-#| fig-width: 5
-   plot.graph(g1, "star")
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph."
+   tab.cent(distinction(g1)[, 1:4])
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph."
-   tab.cent(distinction(g1))
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph (Normalized)."
+   tab.cent(distinction(g1, norm = TRUE)[, 1:4])
 ```
@@
 ```{r}
-#| fig-cap: "A structural fold with seven nodes."
-#| fig-height: 5
-#| fig-width: 5
-   plot.graph(g2, "kk")
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold."
+   tab.cent(distinction(g2)[, 1:4])
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g2)[1:4])
-   tab.cent(tab)
+#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold (Normalized)."
+   tab.cent(distinction(g2, norm = TRUE)[, 1:4])
 ```
-
-```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g3)[1:4])
-   tab.cent(tab)
-```
-
-```{r}
-#| fig-height: 5
-#| fig-width: 5
-   plot.graph(g3)
-```
-
-```{r}
-   library(networkdata)
-   g <- flo_marriage
-   plot.graph(g, l = "kk")
-```
-
-```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold"
-   tab <- data.frame(distinction(g)[1:4])
-   tab.cent(tab)
-```
-
-```{r}
-   library(kableExtra)
-   kbl(d[,c(1, 3:5)], 
-       digits = 2, 
-       col.names = c("Node", "Distinction", "Status", "Uniqueness")) %>% 
-      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
-```
-
-Jilbert's Distinction Equivalence

### 2025-03-01 old.qmd
do it

--- 2024-10-19 distinction.qmd
@@
 ---
-title: "Jilbert's Distinction Centrality"
-execute: 
-  eval: true
-  echo: true
-  output: true
-  warning: false
-  message: false
-format: 
-   html:
-      code-line-numbers: true
-bibliography: networks.bib
+title: "Untitled"
+format: html
+editor: visual
 ---
-
-```{r Loading Functions}
-   library(igraph)
-   library(ggraph)
-   library(here)
-   library(networkdata)
-   source("distinction.R")
-```
-
-According to @jilbert24, the Distinction Centrality of a node is a function of the status of each focal node and the degree of status independence of its alters.
-
-It is given by:
-
-$$
-   D_i = S_i(G)  + \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
-$$
-
-Where $S_i(G)$ is the (normalized to have maximum 1.0) eigenvector centrality of node $i$ computed in the full graph $G$, $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$.
-The Distinction of a node thus increases with its own status and decreases to the extent that others would gain status if that node was not around.
-
-```{r Custom Functions}
-#| echo: false
-   plot.graph <- function(x, l, vs = 12, ts = 6) { #plotting function
-      library(ggraph)
-      d <- distinction(x)$d
-      nc <- rep("", length(d))
-      nc[which(d < -0.05)] <- "red"
-      nc[which(d > 0.05)] <- "blue"
-      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
-      if (is.null(V(x)$name) == TRUE) {
-         n <- 1:vcount(x)
-         tc <- "white"
-         s <- vs
-         }
-      if (is.null(V(x)$name) == FALSE) {
-         n <- V(x)$name
-         tc <- nc
-         vs <- 0
-         }
-      p <- ggraph(x, layout = l)
-      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
-      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
-      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
-      p <- p + theme_graph() 
-   return(p)
-   }
-
-   tab.cent <- function(x) { #table function
-   library(kableExtra)
-   t <- kbl(x, 
-       digits = 2, row.names = FALSE,
-       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
-      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
-   return(t)
-   }
-
-```
-
-```{r}
-    g1 <- make_star(7, mode = "undirected") # star graph
-    g2 <- g1 + edge(2,3)
-    g2 <- g2 + edge(2,4)
-    g2 <- g2 + edge(3,4)
-    g2 <- g2 + edge(5,6)
-    g2 <- g2 + edge(5,7)
-    g2 <- g2 + edge(6,7) # structural fold
-    g3 <- g1 + edge(2,4)
-    g3 <- g3 + edge(3,4)
-    g3 <- g3 + edge(5,6)
-    g3 <- g3 + edge(5,7) # intra-connected clusters
-    g4 <- g3 + edge(2,7) # inter-connected clusters
-```
 
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph."
-   tab.cent(distinction(g1))
+#| fig-cap: "A star graph with seven nodes."
+#| fig-height: 5
+#| fig-width: 5
+   plot.graph.norm(g1, "star")
+   ggsave(here("Plots", "star.png"), width = 6, height = 6)
 ```

### 2025-03-01 distinction.R

@@ -1,4 +1,4 @@
-distinction <- function(x) { #distinction centrality function
+distinction <- function(x, norm = FALSE) { #distinction centrality function
    if (is.null(V(x)$name) == TRUE) {
       V(x)$name <- 1:vcount(x)
       }
@@ -9,14 +9,14 @@ distinction <- function(x) { #distinction centrality function
       j <- names(neighbors(x, i))
       x.d <- x - i
       c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
-      e <- as.numeric(ecount(x.d) != 0) #checking for empty
-      if (c == 1 & e == 1) { #connected non-empty graph
+      e <- as.numeric(ecount(x.d) == 0) #checking for empty
+      if (c == 1 & e == 0) { #connected non-empty graph
          s.a <- eigen_centrality(x.d)$vector[j]
          } #end if
-      else if (c == 0 & e == 0) { #empty graph
+      else if (c == 0 & e == 1) { #empty graph
          s.a <- 0
          } #end else 1
-      else if (c == 0 & e == 1) { #disconnected non-empty graph
+      else if (c == 0 & e == 0) { #disconnected non-empty graph
          C <- components(x.d)$membership
          s.a <- eigen_centrality(subgraph(x.d, which(C == 1)))$vector
          for (k in 2:max(C)) {
@@ -29,6 +29,11 @@ distinction <- function(x) { #distinction centrality function
    } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
-   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u)
+   scalar <- (mean(u)/mean(s))
+   if (norm == TRUE) {
+      s <- s * scalar
+      }
+   d <- s - u
+   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u, scalar = scalar)
    return(dat)
 } #end function

### 2025-03-01 index.qmd
do it

@@
 #| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph (Normalized)."
-   tab.cent(distinction(g1, norm = TRUE)[, 1:4])
+   tab.cent(distinction(g1, scale = TRUE)[, 1:4])
 ```
@@
 #| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold (Normalized)."
-   tab.cent(distinction(g2, norm = TRUE)[, 1:4])
+   tab.cent(distinction(g2, scale = TRUE)[, 1:4])
 ```

### 2025-03-01 distinction.R

@@ -1,4 +1,5 @@
-distinction <- function(x, norm = FALSE) { #distinction centrality function
+distinction <- function(x, scale = FALSE) { #distinction centrality function
+   library(igraph)
    if (is.null(V(x)$name) == TRUE) {
       V(x)$name <- 1:vcount(x)
       }
@@ -30,7 +31,7 @@ distinction <- function(x, norm = FALSE) { #distinction centrality function
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- (mean(u)/mean(s))
-   if (norm == TRUE) {
+   if (scale == TRUE) {
       s <- s * scalar
       }
    d <- s - u

### 2025-03-27 index.qmd
do it

@@
    library(ggpubr)
+   library(here)
    source("distinction.R")
@@
 
-   tab.cent <- function(x, d = 3) { #table function
+   tab.cent <- function(x, d = 3, name = "name") { #table function
    library(kableExtra)
@@
        digits = d, row.names = FALSE,
-       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
+       col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar")) %>% 
       kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) 
-   return(t)
+   save_kable(file = paste(name, ".pdf", sep = ""))
    }
@@
     g4 <- g3 + edge(2,7) # inter-connected clusters
+```
+
+```{r}
+   medici1 <- as.matrix(read.csv(here("MediciEdgeList.csv")))
+   medici1 <- graph_from_edgelist(medici1, directed = FALSE)
+   medici2 <- as.matrix(read.csv(here("MediciEdgeListMarriageCut.csv")))
+   medici2 <- graph_from_edgelist(medici2, directed = FALSE)
+   nomedici <- as.matrix(read.csv(here("NoMediciEdgeList.csv")))
+   nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
+   distinction(medici1)
+   distinction(medici2)
+   distinction(nomedici)
+   tab.cent(distinction(medici1))
 ```

### 2025-03-27 jilbert.qmd
do it

---
title: "Untitled"
format: html
---

```{r}
   library(tidyverse)
   library(dplyr)
   library(tidygraph)
   library(ggraph)
   library(igraph)
```

##Parameter Test Networks

#startest.csv
startest <- read.csv(file.choose(), header=TRUE)
stardf<-as.matrix(startest)
stargraph<-graph_from_edgelist(stardf, directed=FALSE)
distinction(stargraph)
plot(stargraph)

#startest2.csv
star2 <- read.csv(file.choose(), header=TRUE)
star2df<-as.matrix(star2)
stargraph2<-graph_from_edgelist(star2df, directed=FALSE)
distinction(stargraph2)
plot(stargraph2)

#intraclustertest.csv
intracluster <- read.csv(file.choose(), header=TRUE)
intraclusterdf<-as.matrix(intracluster)
intraclustergraph<-graph_from_edgelist(intraclusterdf, directed=FALSE)
distinction(intraclustergraph)
plot(intraclustergraph)

#intraclustertest2.csv
intracluster2 <- read.csv(file.choose(), header=TRUE)
intracluster2df<-as.matrix(intracluster2)
intraclustergraph2<-graph_from_edgelist(intracluster2df, directed=FALSE)
distinction(intraclustergraph2)
plot(intraclustergraph2)

##Medici Network

#MediciEdgeList.csv
medici <- read.csv(file.choose(), header=TRUE)

#AlbizziEditMediciEdgeList.csv
nomedici <- read.csv(file.choose(), header=TRUE)

medicidf<-as.matrix(medici)
medicigraph<-graph_from_edgelist(medicidf, directed=FALSE)

nomedicidf<-as.matrix(nomedici)
nomedicigraph<-graph_from_edgelist(nomedicidf, directed=FALSE)

betweenness(medicigraph)
betweenness(nomedeigenicigraph)

eigen_centrality(medicigraph)
eigen_centrality(nomedicigraph)

```

### 2025-03-27 distinction.R

@@ -30,11 +30,13 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
    } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
-   scalar <- (mean(u)/mean(s))
+   scalar <- mean(u)/mean(s)
    if (scale == TRUE) {
       s <- s * scalar
       }
    d <- s - u
-   dat <- data.frame(n = V(x)$name, d = d, s = s, u = u, scalar = scalar)
+   sd <- (s*scalar) - u
+   dat <- data.frame(n = V(x)$name, d = d, sd = sd, s = s, u = u, scalar = scalar)
+   rownames(dat) <- 1:nrow(dat)
    return(dat)
 } #end function

### 2025-03-27 manuscript.tex

\documentclass[12pt]{article}
\usepackage[left=1.15in, right=1.15in, top=1in, bottom=1.5in]{geometry}
\usepackage{natbib}
\usepackage{verbatim}
\usepackage{setspace}
\bibpunct[: ]{(}{)}{;}{a}{}{,} 
\usepackage{authblk}
\renewcommand\Authfont{\normalsize}
\renewcommand\Affilfont{\footnotesize}

\begin{document}
\title{The Network Origins of Social Distinction}
\author[1]{Author Isaac Jilbert\thanks{issac.jilbert@gmail.com}}
\author[1]{Omar Lizardo\thanks{olizardo@soc.ucla.edu}}
\affil[1]{Department of Sociology, UCLA}

\renewcommand\Authands{ and }

\date{\normalsize \today}	
\maketitle

\newpage
\begin{abstract}	
\end{abstract}

\newpage
\section{What is Distinction?}

Distinction, as the expression of status and uniqueness, is a social end in itself. While cultural distinction is empirically a matter of the deference given to symbolic forms of differentiation \citep{bourdieu84}, a generalized sense of social distinction---that which emerges from a network of concrete social relations---has been less precisely conceptualized, and measurement strategies are naturally lacking. Instead, social distinction is often measured as the shadow of cultural distinction or collapsed into the concept of status more generally, which ignores questions of how network constraint impacts the capacity of actors to be distinct.

For instance, Pierre Bourdieu’s idea of distinction focuses on how individuals adopt and inherit particular cultural practices that demarcate class membership and how these markers become constant signifiers of the underlying social hierarchy. From this perspective, cultural practices reflect past and present relationships and facilitate future connections \citep{bourdieu84}. Here, the focus is placed on cultural distinction, which reflects one’s position in an interconnected system, sometimes referred to as a ``field.'' Distinction is a mark of status where those participating in the same cultural forms share similar social standing in a hierarchy.

In developing a broader understanding and measure of social distinction,  actor-level incentives and structural impediments to action become apparent. When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly retrodicted.

In addition to being a mark of differentiation from others outside the relevant milieu (as in the symbolic status model), for an actor, distinction can also be a question of uniqueness within a delimited set of relationships within which the actor is embedded. Even within a group that shares cultural practices, there are rewards to being differentiated within the category. Complete cultural conformity is a trade-off, where one is completely enmeshed within the group's expectations. Here, the failure to be unique means that one is incapable of asserting autonomy when action is required. For an actor, achieving cultural distinction thus becomes an optimization problem, trading off connectedness for uniqueness.

In this respect, rather than distinction being a phenomenon about culture and network positioning, it is a more general expression of the interaction between status and uniqueness. When it comes to questions of political power rather than cultural cache, network status is another name for \textit{influence} and uniqueness for \textit{autonomy} in a social topology. An actor with high capacity is well connected to others who can be mobilized for action. An actor with high autonomy is not constrained by these connections or forced into action by them \citep{burt76}. We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy.

\subsection{A Relational Understanding of Distinction}
To simplify a bit for argument's sake, as we have intimated, the first aspect of social distinction generally is \textit{status}. Status is the internal stratification of all members of the network, along with connections of deference and obligation. In the case of politics, status is the ability to access those who themselves have higher levels of access, with those most central to the access network having the ability to make decisions. This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich72}. Status is higher for actors when the people they are connected to are themselves important, and accessibility is just a political reframing of the context. The internal stratification of individuals is determined by who has greater connections to those who have greater connections, with those with few connections to other unimportant people being at the bottom of the hierarchy (Bonacich).

The second aspect of social distinction is \textit{autonomy}, which is the absence of network constraint. Being structurally unique minimizes the social constraints placed on an individual. The tighter the interconnections of the group, the more its pressures constrain the individual. In politics, this aspect of distinction takes the form of constraint. When an actor is one of many densely interconnected individuals, their ability to act contrary to their networked group is greatly weakened. However, when one is only a weakly dependent and connected member of a group, they have a greater ability to operate independently. Their ability to act is a source of distinction as they are able to take independent action. The question of structural uniqueness and autonomy is the same underlying consideration as captured by measures of path centrality. The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt92}.

\citet[1263-4]{padgett_ansell94} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions. Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because strong actions favoring one side would upset the other side. However, such a constraint was not an issue because Medici’s interests were in perpetuating his central role as broker, and, as the only source of interest, he was able to maintain the position. With regard to conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side. The decisions derive from ensuring the continuation of their position at the center of the network.

The interaction of influence and autonomy combines to create an actor’s overall distinction in the network. The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction. An increase in one aspect can often, but not necessarily, lead to a decrease in the other. For example, a connection with someone with high accessibility can lead to a decrease in one’s autonomy, and new access comes with new constraints. However, the trade-off can maximize one’s overall distinction, so there are gains from the connection. Without such gains, the connection would not be formed.

\bibliography{networks}
\bibliographystyle{apalike}

\end{document}

### 2025-04-01 index.qmd
do it

--- 2025-03-01 index.qmd
@@
 
-```{r Custom Functions}
-#| echo: false
-   plot.graph <- function(x, l, vs = 12, ts = 6) { #plotting function
+```{r}
+   tab.cent <- function(x, d = 3, name = "name", caption = "", label = "label") { #table function
+   library(kableExtra)
+   t <- kbl(x, 
+            format = "latex", booktabs = TRUE, linesep = "",
+            digits = d, row.names = FALSE,
+            col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
+            caption = caption, label = label
+            ) %>% 
+            kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
+            save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))
+   }
+```
+
+```{r Toy Examples}
+    g1 <- make_star(7, mode = "undirected") # star graph
+    g2 <- g1 + edge(2,3)
+    g2 <- g2 + edge(2,4)
+    g2 <- g2 + edge(3,4)
+    g2 <- g2 + edge(5,6)
+    g2 <- g2 + edge(5,7)
+    g2 <- g2 + edge(6,7) # structural fold
+    g3 <- g1 + edge(2,4)
+    g3 <- g3 + edge(3,4)
+    g3 <- g3 + edge(5,6)
+    g3 <- g3 + edge(5,7) # intra-connected clusters
+    g4 <- g3 + edge(2,7) # inter-connected clusters
+    tab.cent(distinction(g1), name = "star", label = "tab:star")
+    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
+    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
+    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
+```
+
+```{r}
+   plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
       library(ggraph)
-      d <- distinction(x)$d
+      d <- distinction(x)[,3]
       nc <- rep("", length(d))
@@
       p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
-      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
+      p <- p + geom_node_text(aes(label = n), size = ts, color = tc, fontface = "bold")
       p <- p + theme_graph() 
    return(p)
-   }
-   plot.graph.norm <- function(x, l, vs = 12, ts = 6) { #plotting function
-      library(ggraph)
-      d <- distinction(x, norm = TRUE)$d
-      nc <- rep("", length(d))
-      nc[which(d < -0.05)] <- "red"
-      nc[which(d > 0.05)] <- "blue"
-      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
-      if (is.null(V(x)$name) == TRUE) {
-         n <- 1:vcount(x)
-         tc <- "white"
-         s <- vs
-         }
-      if (is.null(V(x)$name) == FALSE) {
-         n <- V(x)$name
-         tc <- nc
-         vs <- 0
-         }
-      p <- ggraph(x, layout = l)
-      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
-      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
-      p <- p + geom_node_text(aes(label = n), size = ts, color = tc)
-      p <- p + theme_graph() 
-   return(p)
-   }
-
-   tab.cent <- function(x, d = 3) { #table function
-   library(kableExtra)
-   t <- kbl(x, 
-       digits = d, row.names = FALSE,
-       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
-      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
-   return(t)
    }
@@
 ```{r}
-    g1 <- make_star(7, mode = "undirected") # star graph
-    g2 <- g1 + edge(2,3)
-    g2 <- g2 + edge(2,4)
-    g2 <- g2 + edge(3,4)
-    g2 <- g2 + edge(5,6)
-    g2 <- g2 + edge(5,7)
-    g2 <- g2 + edge(6,7) # structural fold
-    g3 <- g1 + edge(2,4)
-    g3 <- g3 + edge(3,4)
-    g3 <- g3 + edge(5,6)
-    g3 <- g3 + edge(5,7) # intra-connected clusters
-    g4 <- g3 + edge(2,7) # inter-connected clusters
+   png(here("Plots", "star.png"))
+   plot.graph.norm(g1)
+   dev.off()
+   png(here("Plots", "sf.png"))
+   plot.graph.norm(g2)
+   dev.off()
+   png(here("Plots", "intra.png"))
+   plot.graph.norm(g3)
+   dev.off()
+   png(here("Plots", "inter.png"))
+   plot.graph.norm(g4)
+   dev.off()
 ```
@@
 ```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph."
-   tab.cent(distinction(g1)[, 1:4])
+   medici1 <- as.matrix(read.csv(here("Data", "MediciEdgeList.csv")))
+   medici1 <- graph_from_edgelist(medici1, directed = FALSE)
+   medici2 <- as.matrix(read.csv(here("Data", "MediciEdgeListMarriageCut.csv")))
+   medici2 <- graph_from_edgelist(medici2, directed = FALSE)
+   nomedici <- as.matrix(read.csv(here("Data", "NoMediciEdgeList.csv")))
+   nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
+   png(here("Plots", "medici.png"), height = 600, width = 1000)
+      plot.graph.norm(medici1, ts = 5)
+   dev.off()
+   png(here("Plots", "nomedici.png"), height = 600, width = 1000)
+      plot.graph.norm(nomedici, ts = 5)
+   dev.off()
+
 ```
-
-```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph (Normalized)."
-   tab.cent(distinction(g1, norm = TRUE)[, 1:4])
-```
-
-```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold."
-   tab.cent(distinction(g2)[, 1:4])
-```
-
-```{r}
-#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold (Normalized)."
-   tab.cent(distinction(g2, norm = TRUE)[, 1:4])
-```

### 2025-04-17 distinction.R
updated function

@@ -6,7 +6,7 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
    s <- eigen_centrality(x)$vector
    d <- 0
    u <- 0
-   for (i in 1:vcount(x)) {
+   for (i in V(x)$name) {
       j <- names(neighbors(x, i))
       x.d <- x - i
       c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
@@ -38,5 +38,5 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
    sd <- (s*scalar) - u
    dat <- data.frame(n = V(x)$name, d = d, sd = sd, s = s, u = u, scalar = scalar)
    rownames(dat) <- 1:nrow(dat)
-   return(dat)
+   return(round(dat, 4))
 } #end function

### 2025-04-17 distinction.R
fixed function

@@ -5,10 +5,10 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
       }
    s <- eigen_centrality(x)$vector
    d <- 0
-   u <- 0
-   for (i in V(x)$name) {
+   u <- rep(vcount(x), 0)
+   for (i in as.character(V(x)$name)) {
       j <- names(neighbors(x, i))
-      x.d <- x - i
+      x.d <- delete_vertices(x, i)
       c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
       e <- as.numeric(ecount(x.d) == 0) #checking for empty
       if (c == 1 & e == 0) { #connected non-empty graph
@@ -19,15 +19,22 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
          } #end else 1
       else if (c == 0 & e == 0) { #disconnected non-empty graph
          C <- components(x.d)$membership
-         s.a <- eigen_centrality(subgraph(x.d, which(C == 1)))$vector
-         for (k in 2:max(C)) {
-            s.a <- c(s.a, eigen_centrality(subgraph(x.d, which(C == k)))$vector)
+         names(C) <- V(x)$name[-as.numeric(i)]
+         s.a <- rep(0, length(C))
+         for (k in unique(C)) {
+            sub.g <- subgraph(x.d, names(which(C == k)))
+            if (vcount(sub.g) > 1) {
+               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
+               }
             }
+         names(s.a) <- names(C)
          s.a <- s.a[j]
          } #end else 2
-      u[i] <- sum(s.a) * 1/length(s.a) #average neighbor centrality
+      u[i] <- sum(s.a)/length(s.a) #average neighbor centrality
       d[i] <- s[i] - u[i] #distinction centrality
    } #end i for loop
+   print(s)
+   print(u)
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)

### 2025-04-17 distinction.R
do it

@@ -1,6 +1,12 @@
 distinction <- function(x, scale = FALSE) { #distinction centrality function
    library(igraph)
-   if (is.null(V(x)$name) == TRUE) {
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   if (has.labels == 0) {
+      V(x)$name <- 1:vcount(x)
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
       V(x)$name <- 1:vcount(x)
       }
    s <- eigen_centrality(x)$vector
@@ -33,8 +39,6 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
       u[i] <- sum(s.a)/length(s.a) #average neighbor centrality
       d[i] <- s[i] - u[i] #distinction centrality
    } #end i for loop
-   print(s)
-   print(u)
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)
@@ -43,7 +47,9 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
       }
    d <- s - u
    sd <- (s*scalar) - u
-   dat <- data.frame(n = V(x)$name, d = d, sd = sd, s = s, u = u, scalar = scalar)
+   dat <- data.frame(d = d, sd = sd, s = s, u = u, scalar = scalar)
+   dat <- round(dat, 4)
+   dat <- data.frame(n = names, dat)
    rownames(dat) <- 1:nrow(dat)
-   return(round(dat, 4))
+   return(dat)
 } #end function

### 2025-04-17 manuscript.tex
Updates from Overleaf

@@
 \usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{subcaption}
 \bibpunct[: ]{(}{)}{;}{a}{}{,} 
@@
 \begin{document}
-\title{The Network Origins of Social Distinction}
-\author[1]{Author Isaac Jilbert\thanks{issac.jilbert@gmail.com}}
+\title{Network Origins of Social Distinction}
+\author[1]{Author Isaac Jilbert\thanks{isaac.jilbert@gmail.com}}
 \author[1]{Omar Lizardo\thanks{olizardo@soc.ucla.edu}}
@@
 \begin{abstract}	
+In this paper a new network measure, distinction centrality, is introduced.
+The measure is derived from Bourdieu's theory of the competition for distinction in a field where actors act both with agency and within the constraints imposed by other actors.
+The measure subtracts the autonomy of each actor \textit{i} within the network from their constraint.
+Autonomy is measured using eigenvector centrality for each actor \textit{i}.
+In contrast, constraint is measured by calculating the average eigenvector of nodes \textit{i}'s neighbors in a recalculated network with node \textit{i} removed.
+A scalar is then applied to create mathematical and sociological equivalence between autonomy and constraint.
+The resulting node-level measures create a measure of distinction, where the uniqueness of a node's associations is more heavily rewarded than under eigenvector centrality.
+The resulting measure is applied to both Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club to show that the observed actions of the agents involved are consistent with distinction maximization.
+The resulting measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.
 \end{abstract}
@@
 \newpage
-\section{What is Distinction?}
+\section{Distinction Beyond Taste}
+Popular within cultural sociology, the idea of distinction has generated a rich literature to explain cultural differentiation.
+Distinction, as the expression of status and uniqueness, is a social end in itself.
+The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation \citep{bourdieu1984distinction}.
+Broader social distinction is often measured as the shadow of cultural distinction or collapsed into the concept of status more generally, which ignores questions of how network constraint impacts the capacity of actors to be distinct.
+A generalized, measured ordering of social distinction that is derivative from a network of concrete social relations would give Bourdieu's generalized conception of distinction a broader methodological base from which to conduct empirical analysis.
 
-Distinction, as the expression of status and uniqueness, is a social end in itself.
-While cultural distinction is empirically a matter of the deference given to symbolic forms of differentiation \citep{bourdieu84}, a generalized sense of social distinction---that which emerges from a network of concrete social relations---has been less precisely conceptualized, and measurement strategies are naturally lacking.
-Instead, social distinction is often measured as the shadow of cultural distinction or collapsed into the concept of status more generally, which ignores questions of how network constraint impacts the capacity of actors to be distinct.
+\subsection{What is Distinction?}
+Pierre Bourdieu was interested in the competition among people for positions within the hierarchy.
+Bourdieu defined the field as a social space where actors operate within socially negotiated boundaries that arbitrate relevant competitive claims over position.
+In interplay with the field, individuals develop a habitus of embodied dispositions, expressed as a cognitive ease with particular types of settings, objects, and performances.
+An actor's position in the field influences their habitus.
+In the same way, their habitus determines their future possibilities within the field, while also structuring the opportunities available for others in the field.
+Actors compete for positions in the field via various forms of capital, or resources that are socially-agreed upon as desirable within a field, thereby facilitating the formation of connections that both order and reflect the hierarchy of the field.
+The interaction of the desirability and uniqueness of the capitals possessed by an individual determines their place in the field's positional hierarchy.
 
-For instance, Pierre Bourdieu’s idea of distinction focuses on how individuals adopt and inherit particular cultural practices that demarcate class membership and how these markers become constant signifiers of the underlying social hierarchy.
-From this perspective, cultural practices reflect past and present relationships and facilitate future connections \citep{bourdieu84}.
-Here, the focus is placed on cultural distinction, which reflects one’s position in an interconnected system, sometimes referred to as a ``field.'' Distinction is a mark of status where those participating in the same cultural forms share similar social standing in a hierarchy.
+Bourdieu \citeyearpar{bourdieu1984distinction} most famously used the conceptualization of distinction to explain the persistence of the relationship between class and cultural hierarchies.
+Cultural elites in France distinguished themselves from their inferiors by adopting differentiated cultural practices that had undergone a process of consecration, which set them apart from the common.
+There is a strong correlation between those in the position of cultural and economic elites.
+Still, such correlation is not guaranteed at the individual level even if it is relevant at the level of the fields.
+
+While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}.
+For example, while cultural practices may be a marker of difference, the absence of association with others outside the milieu, distinction is also a matter of agency within the milieu, a question of the constraint imposed by the set of relationships within which the actor is embedded.
+For Bourdieu, the struggle for position in a field was a product of a field of action and a field of forces \citep{martin2003field}.
+The field of action describes the agency of actors actively advancing their position.
+In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be upset by positional transformations.
+
+In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}.
+Translated to network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle is reflective of the constraint neighbors put on an actor.
+An actor with high influence is well-connected to others who can be mobilized for effective action.
+An actor with high autonomy is not constrained by their pattern connections or forced into action by them \citep{burt76}.
+We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy.
+Nevertheless, we use status and autonomy below as general terms to describe the ability of actors to take action versus the level of imposition from the forces of constraint.
 
 In developing a broader understanding and measure of social distinction, actor-level incentives and structural impediments to action become apparent.
-When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly retrodicted.
+When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly forecaste.
 
-In addition to being a mark of differentiation from others outside the relevant milieu (as in the symbolic status model), for an actor, distinction can also be a question of uniqueness within a delimited set of relationships within which the actor is embedded.
-Even within a group that shares cultural practices, there are rewards to being differentiated within the category.
-Complete cultural conformity is a trade-off, where one is completely enmeshed within the group's expectations.
-Here, the failure to be unique means that one is incapable of asserting autonomy when action is required.
-For an actor, achieving cultural distinction thus becomes an optimization problem, trading off connectedness for uniqueness.
+\subsection{Position as the Relational Basis for a Distinction Measure}
+Bourdieu's separation of distinction into habitus and position is no sociological problem at all, but creates the analytical problem of how an actor's network position creates dispositions and how dispositions create the opportunity for network mobility.
+Both dispositions and positions are fundamentally relational outcomes in sociological terms, but in creating a network measure of distinction, only the relational basis of position can be considered.
 
-In this respect, rather than distinction being a phenomenon about culture and network positioning, it is a more general expression of the interaction between status and uniqueness.
-When it comes to questions of political power rather than cultural cache, network status is another name for \textit{influence} and uniqueness for \textit{autonomy} in a social topology.
-An actor with high capacity is well connected to others who can be mobilized for action.
-An actor with high autonomy is not constrained by these connections or forced into action by them \citep{burt76}.
-We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy.
+However, to the extent that position and habitus reflect each other through their symbiotic fabrication, the ability to empirically capture only one of the two components is sufficiently accurate to measure a social system's distinction hierarchy with confidence over a short window of time.
+Actors simply should not have a network position that does not match their habitus, and their ability to radically change positions is governed by their current habitus and social position.
+If the transformation of habitus is a stepwise interplay with positional movement that unfolds over time, the measure becomes less informative if capturing networks over extended time periods.
+However, even over long periods of time this theoretical collapse that permits a network measured methodological shortcut may still be adequate in a moderately stable social environment.
 
-\subsection{A Relational Understanding of Distinction}
-To simplify a bit for argument's sake, as we have intimated, the first aspect of social distinction generally is \textit{status}.
+To put the measure of distinction on a firm theoretical foundation, it is first important to make explicit the relationship between empirical data and social theory that is the basis of social network analysis.
+Network measures are fundamentally based on the idea that researchers are in some way capturing a relationship between two objects.
+A tie between two nodes is capturing in some way their connection however so defined.
+Such connections can be broadly classified as mutual in the case of the relationship quality being equal in both directions, or directional in the case of the qualities being unequal.
+In the absence of direct measurement of qualities however, many networks are measured as consisting of mutual ties.
+However, even in the case of networks composed of only mutual ties, hierarchy can still be assessed from the pattern of relationships.
+In such networks, we are still able to rank the direction of power and deference through the absence of ties between lower and higher nodes.
+For example, in an organizational pyramid, we would be able to detect the CEO from the presence of ties with the vice presidents and the absence of ties with middle management and production workers.
+We can do this through the measurement of a node's network status.
+
+The first aspect of social distinction generally is \textit{status}.
 Status is the internal stratification of all members of the network, along with connections of deference and obligation.
 In the case of politics, status is the ability to access those who themselves have higher levels of access, with those most central to the access network having the ability to make decisions.
-This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich72}.
+This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972norms}.
 Status is higher for actors when the people they are connected to are themselves important, and accessibility is just a political reframing of the context.
-The internal stratification of individuals is determined by who has greater connections to those who have greater connections, with those with few connections to other unimportant people being at the bottom of the hierarchy (Bonacich).
+The internal stratification of individuals is determined by who has greater connections to those who have greater connections, with those with few connections to other unimportant people being at the bottom of the hierarchy \citep{bonacich1972norms}.
 
@@
 The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt92}.
-
 \citet[1263-4]{padgett_ansell94} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions.
@@
 
+The interaction of influence and autonomy combine to create an actor’s overall distinction in the network.
+The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction.
+An increase in one aspect can often, but not necessarily, lead to a decrease in the other.
+For example, a connection with a someone with high accessibility other can lead to a decrease in one’s autonomy, and new access comes with new constraints.
+However, the trade-off can maximize one’s overall distinction, so there are gains from the connection.
+Without such gains, the connection would not be formed.
+
+\section{A Generalized Measure of Network Distinction}
+Below we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and point to the availability of an R program so that researcher's may easily implement the measure in their own research.
+
+\subsection{Distinction Centrality}
+
+A formalization of this interaction between status and uniqueness allows for a measure of network distinction.
+Distinction as a theoretical concept is composed of status mediated by autonomy.
+A distinction measure can reflect this by considering an actor'ss status and then discounting their status by the status of their neighbors independent of the actor.
+The more reliant an actors neighbors are on the actor for their status, the lower that actors ability to exert their own influence, and thus the lower their distinction.
+In other words, autonomy is determined by how much one's neighbors need you to sustain their own position in the network.
+
+Distinction centrality can be measured through the implementation of the following algorithm.
+\[\beta_i=Sx_i-{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}} \]
+Let \(\beta\) be the distinction centrality of a given individual \textit{i}.
+The first term captures the status of a given actor.
+Let \textit{x} be the eigenvector centrality \citep{bonacich72} of the designated individual.
+Let S be a scalar that adjusts the social value placed on status compared to constraint, to be discussed below.
+The second terms captures the element of autonomy.
+Removing individual \textit{i} from the network, compute the eigenvectors of the remaining individuals and sum those that are connected to individual \textit{i}, taking the average eigenvector of neighbors \textit{j} as the constraint confronting node \textit{i} in the network.
+This is substantively the same mechanism as conducted in a jackknife resampling procedure, except rather than forming a sampling distribution, we are measuring local constraint.
+Finally, subtract the status of the average neighbor connected to \textit{i} from \textit{i}’s scalar adjusted eigenvector centrality in the whole network.
+
+If a node is an isolate, its eigenvector centrality should be set at 0.
+In the case of a network with no connections (such as a star graph), it can accidentally be calculated as 1.00 in programs, but given that it is still a network of no connections, setting isolates at 0.00 is theoretically appropriate when considering that status is a reflection of connections.
+It would be inappropriate for an isolate to have the same status as the highest status node in a large network.
+Additionally, given the second step of subtraction, it is only theoretically meaningful if set as 0 in the case of distinction centrality.
+
+\subsection{Scalar Adjustment}
+First, a scalar is required because relative value of status and autonomy is not inherently fixed in a social system.
+We might imagine situations where one desires more status at the expense of autonomy if the rewards to status are higher, or value autonomy more highly if the rewards to status are low.
+There cannot be an assumed unadjusted equivalence between the resulting eigenvectors of the two terms for this theoretical level.
+
+Additionally, because of the hierarchical nature of networks, the average constraint in the network is larger than the average status.
+The high average constraint of their neighbors is often much larger than the impact of status.
+The result is that, at the level of the entire network, that those who are deeply embedded among the most elites, without their own basis of supporters, are very indistinct when considering the high constraints placed on them by their high status alters.
+Thus, the calculated results without a scalar can fail to capture the appropriate value on status as compared to constraint.
+
+While an arbitrary scalar is possible, it can lead to erroneous results when tested against empirical networks.
+However, a scalar can be derived from the network itself because of the field positional interplay of status and constraint.
+Imagining two actors of equal status and personal constraint, one in an averagely more constrained system and the other in a less averagely constrained system, with average status otherwise equal.
+In such a case, the status of an actor in the more constrained system has a greater impact on their social distinction than in the less constrained system.
+With high constraint, status takes on greater importance in determining social distinction because it compels deference.
+In other words, it is the difference between hierarchy with constraint, and hierarchy without constraint.
+Status with weak constraint means a weaker compulsion of deference.
+The structure of constraint redounds into the impact of status on social distinction beyond its own contribution.
+
+With this social understanding of how constraint interacts with the transmission of status, an endogenous scalar can be derived from the network.
+The average constraint of actors within in the network divided by the average status of actors in the network creates a scalar that reflects the relationship between status and constraint.
+
+\[S=\frac{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}}{\overline{x_i}} \]
+
+Under conditions of high average constraint and low average status, the scalar is large, reflecting the importance of status in determining social distinction.
+Under conditions where average constraint is low and average status is high, the scalar is weaker, reflecting a system where status is less important in determining social distinction.
+Under very large-scale conditions, the averages of status and constraint should trend towards 1, weakening the necessity of the scalar.
+However, under constrained conditions, particularly elite networks with missing data of the social scaffolding that created the network elites, the scalar is more important for explaining action because the range of eigenvector network measures are otherwise being artificially expanded due to the missing data.
+
+Without a scalar, networks with any degree of hierarchy see the average constraint swamp the average status because many low status nodes tie into high status nodes.
+The advantage of this scalar is to make the average scalar status in the network equal to the average constraint in the network.
+Thus, total status is equal to total constraint, and from there it becomes a matter of distribution among members.
+From there however, it allows for comparability between networks that would otherwise not be possible.
+With the understanding that we have, through the scalar, adjusted for a network where ones combination of status and constraint is better or worse, networks can be compared so long as the unobserved social context within the network changes are made is otherwise stable.
+
+\subsection{Distinction Centrality's Measurement Parameters}
+In Figure 1, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors.
+In each model, there are seven nodes, and node 1 is the best-connected node in the network.
+Thus, node 1 always has an eigenvector centrality of 1.
+However, the distinction of node 1 changes based on the interconnection of the other nodes, demonstrating how distinction centrality captures the question of constraint exerted by neighbors.
+
+\textit{Model (a)} is a star graph where node 1 is completely connected to all other nodes, yet the other nodes share no connections.
+Under such conditions, node 1's eigenvector centrality is 1.00.
+Yet, node 1's constraint is 0.00 because, when node 1 is removed from the network, all of node 1's neighbors have no connections and thus an eigenvector centrality of 0.00.
+Table 1 displays the various measurements for each node.
+The hub of a star graph thus has the maximum possible distance between status and constraint.
+However, with additional spokes added to a star graph, the scalar adjusted distinction measure increases.
+The hub of a star graph with seven spokes is more distinct than a hub with six, allowing a degree of comparability across networks.
+A network composed of a dyad would have a scalar adjusted distinction of 0.00 because the average constraint is 0.
+Distinction becomes a meaningful phenomenon only in networks of three or more nodes.
+
+\textit{Model (b)} presents an idealized depiction of a structural fold \citep{vedres2010structural}.
+The resulting measurement scores are in Table 2.
+While node 1 maintains high eigenvector centrality, the eigenvector centrality of the other nodes increases, while their constraint decreases.
+It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their own subgroups.
+This position of brokerage is more constrained than the star graph because the other actors are connected in subgroups.
+The actors in the subgroup are able to combine their interests to mitigate against the independence of Node 1 in the center.
+In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
+With a scalar adjustment, the stratification increases, giving a bit more privilege to Node 1, but demonstrating the extent to which Node 1's distinction is eroded.
+In a maximally connected graph, the distinction of each node would also go to 0.00, as there is no network differentiation among nodes.
+
+\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
+Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
+Compared to the structural fold,  connection 3-2 and connection 6-7 have been removed.
+Measurement results are in Table 3.
+Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
+The resulting scalar adjusted distinction measures well reflects this stratification, with Node 1 retaining its distinction, Node's 4 and 5 failing in the middle position, and Node's 2, 3, 6, and 7 falling to the bottom.
+
+\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
+This long tie stratifies the network even more than in Model (c) bringing Nodes 2 and 7 quite close to 4 and 5.
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+In fact, all nodes except 3 and 6 have higher distinction in such a case.
+This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
+While the status of Node's 2 and 7 actually increase beyond that of 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1 as their mutual neighbor.
+
+\subsection{R Package}
+The analyses below are conducted with a program that implements the above distinction centrality measure. Omar wrote it. He's a cool guy. Maybe he would like to do a whole separate article on it?
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/star.png}
+            \caption{Star Graph}
+            \label{fig:star}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
+            \caption{Structural Fold}
+            \label{fig:sf}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/intra.png}
+            \caption{2-Connected Subgraphs}
+            \label{fig:intra}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/inter.png}
+            \caption{2-Connected Subgraphs with Long Tie}
+            \label{fig:inter}
+    \end{subfigure}
+    \caption{}
+    \label{fig:toys}
+\end{figure}
+
+\input{Tabs/star}
+\input{Tabs/structfold.tex}
+\input{Tabs/intraclust}
+\input{Tabs/interclust}
+
+\section{Betweenness vs Distinction: Revisiting the Medici Network}
 The interaction of influence and autonomy combines to create an actor’s overall distinction in the network.
@@
 
+One of the consecrated papers of social network analysis is Padgett and Ansell’s (1993) analysis of the centrality of the Medici to Florentine elite marriage and business networks in the 15th century.
+The empirics led to the theory of robust action, demonstrating that one’s position in the network can become the basis of one’s interests, and that through balancing competitors, an actor can amplify their social position.
+
+A puzzle that results from the empirics however is how the balance between antagonistic factions created by the Medici came to be undone within a decade of Padgett and Ansell’s focus.
+Brokerage created social stability, yet in 1432 Rinaldo Albizzi as leader of the combination of conservative old oligarchic families seized the reigns of the Florentine government, exiling the leading Medici from Florence.
+Why was the network position of the Medici as brokers so unstable?
+In other words, what were the network incentives of the old conservative families to attempt to remove the Medici from their network position?
+
+The opportunities for an increase in social distinction explain the attempt by the conservative oligarchs to remove the Medici from the network.
+Padgett and Ansell built their network of Florentine marriages and economic exchange as a series of blockmodels, which capture the inter-relations among families \citep{padgett1993robust} 1276.
+Underneath the blockmodel are even more families in their Appendix B, such that there were 92 elite families overall considered (1276).
+The politics of Florence centered around family alliances consecrated through marriage, trade, and friendship ties ().
+However, over the years many families had developed cadet branches, with many old families having 10 or more households, with the Strozzi and Bardi having more than 50.
+Newer families had smaller, less ancient family networks, and so inter-family political cooperation was important for their social protection (150-1).
+Family capacity through size and wealth was then channeled into inter-elite marriages, creating the networks of power and influence through which Florentine politics was channeled.
+The unity of the households within a single lineage was variable however, often depending on their own marriages.
+For example, the Bardi family largely sided with the old families against the Medici, but the marriage of Contessina de Bardi to Cosimo de Medici (129) meant that the family was not united in opposing the Medici.
+
+To empirically examine the opportunity for gaining social distinction in the Florentine network, Figure 2a from Padgett and Ansell was reproduced as an edgelist, with each tie between blocks counted as a single connection, regardless of its quality or frequency in the original Figure 2a.
+It is essentially a simplified network of blocks, treated as network actors, that are socially connected, indicated by the family names originally used by Padgett and Ansell.
+Ignoring the intensity of ties is unlikely to change the results given that most are singly connected in the original figure, and the multiple ties are still fragmented among a variety of households within a family, so they could inordinately strengthen connections rather than explain fracturing that occurred within families.
+Examining the Florentine network with the above measure of social distinction explains the transformation from political stability to fragmentation as a result of actor level network incentives.
+
+Results are presented in Table X.
+In the original state of the network, the Medici had the highest betweenness (), while the Peruzzi had the highest status.
+The Albizzi, with the second highest status, owed their high status in part to their connection with the Medici.
+Without the marriage connection to the Medici, the Albizzi would still have high status in the networks, but would otherwise be eclipsed by the Guasconi, who were also connected to the Medici and other major families.
+The Medici were actually of relatively middling status in the network, clearly deriving their power from the brokerage leadership.
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{1.0\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/medici.png}
+            \caption{Medici Network}
+            \label{fig:medici}
+    \end{subfigure} \\
+     \begin{subfigure}[b]{1.0\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/nomedici.png}
+            \caption{Medici Network without the Medici}
+            \label{fig:nomedici}
+    \end{subfigure}
+    \caption{}
+    \label{fig:medici}
+\end{figure}
+
+\input{Tabs/medici}
+
+In a comparison of the network with the Medici compared to the one with them absent, one notices that the status of the oligarchic families does not automatically increase.
+While those further away from the Medici such as the Strozzi and Panciatichi would see their status increase in the Medici’s absence as the center of the network would shift its center towards them, the Guasconi and the Albizzi would lose by such a straightforward measure of changing status.
+Considering the matter of constraint, The Guasconi and Albizzi would actually also become more constrained in the absence of the Medici from the network.
+Thus, in a situation where their status decreases and their constraint increase, these families still chose to act against the Medici!
+
+The difference in status and distinction for the Guasconi and Albizzi would still be lower without the Medici in the network than with the Medici.
+However, when adjusting for the level of status and constraint in the system, the Guasconi and Albizzi would, along with the rest of the conservative oligarchs, increase their social distinction.
+The overall decrease within the system as a whole of average status and an increase in constraint would make for the increasing importance of the status that the Guasconi and Albizzi did have at the level of the system.
+The inequality within the system would essentially increase without the presence of the Medici, and ending up in the elite cluster of a more unequal network of elites was an increase in social distinction sufficient to entice members of the Guasconi and Albizzi blocks.
+In contrast to the application of an edge cutting algorithm that may shear the Guasconi and Albizzi blocks from the Medici due to the weight of their connections with the rest of the network, the members of the families in these blocks had distinction to be gained, as long as their own personal connections did not otherwise tie them to the Medici.
+
+It was not just Cosimo de Medici who derived his sphinxlike qualities from his network position, but Rinaldo degli Albizzi was likewise noted for his unwillingness to take strong stances on behalf of the conservative faction of old elite families (Kent 1978:289).
+Given Rinaldo’s similarity to Cosimo’s brokerage network position, the structural incentives towards equivocation were similarly expressed.
+However, Rinaldo’s structural opportunities were transformed with the death of Niccolò da Uzzano, the previous leader of the conservative faction.
+While the Uzzano’s are attached to the Guasconi block in the original graph of relations, the actually shared deep family relations with the Bardi who fell into the same block as the Guasconi.
+Per Table B1 in Padgett and Ansell (1314-6), the Bardi were third in gross family wealth after the Strozzi and Medici.
+Niccolò’s mother was a Bardi, and his brother married into the family (Kent 1978:166), elevating Niccolò’s authority beyond what might otherwise be discernable from the original graph.
+The Uzzano and Bardi leadership of the conservatives balanced the old elites away from Rinaldo, making ties to the Medici more important for their network position.
+Niccolò was also seen largely as moderate despite leading the old families against the new families (Kent 1978:256).
+However, Niccolò’s death in 1432 created the gap in the conservative faction’s leadership for Rinaldo to fill.
+The center of power within the network of old families was renegotiable, and in exchange for eschewing the Medici, the Rinaldo degli Albizzi could seize leadership and shift the networks emphasis towards himself.
+The secondhand data from Padgett and Ansell’s block models does not allow for a clear demonstration of the movement, but the historiography would indicate the underlying shifts in network opportunity.
+
+With Bernardo Guadagni’s rise to Gondolfier, Albizzi and the old families made their move to exile Cosimo and Lorenzo de Medici, seemingly to seize the levers of city government through factional decapitation, thereby avoiding destructive conflict (289-90).
+While the conservatives seized government, the Medicean’s were not undone by the loss of their leaders but rather resisted without prompting crisis (299).
+The moment of crisis came with the lottery, whereby chance the Medici supporters came to dominate the Priors (328).
+The resulting re-entry of the Medicean’s to government power threatened the conservative faction, and Rinaldo’s response was to mobilize the forces of the conservative families to seize the castle where the priors were meeting.
+The Medicean’s gained word and were able to reinforce the castle before the conservatives could arrive.
+In this moment of constitutional crisis, Palla Strozzi refused to commit his large force of support to Rinaldo’s cause, and even the Peruzzi demobilized upon receipt of a deal from the Medicean’s (331-4).
+The crisis itself was negotiated down through the intervention of the Pope, but the crisis shifted momentum to the Medicean’s side through the fragmentation of the conservatives and the outpouring of armed support flowing in from outside the city walls (Kent 1978:330-4).
+The leadership of the old families were subsequently undone for their crimes (Kent 1978:335-48).
+The conservatives would clearly improve their distinction within Florence with the removal of the Medici, yet in the end the elite network does not explain their defeat.
+The threatened major social losses to the newer families explain their dogged resistance to the conservative ascension, yet the support for the Medici’s with the Pope and beyond Florence was critical as the balance of force among the elite families was in the conservative’s favor (see Padgett and Ansell Appendix B).
+
+\section{Group Detection vs Distinction: Revisiting the Karate Club}
+Another consecrated paper in network analysis is Zachary’s (1977) examination of the fissure of a university karate club network.
+Zachary found that the tension in the group centered around questions of compensation for the outside karate teacher with the internal student group leadership.
+However, Zachary finds that the dispute was channeled and resolved along an already existing division in the underlying friendship connections among the club members (1977:454-5).
+
+The paper was an early application of an algorithm to predict the lines along which the group would divide.
+The original Ford-Fulkerson Labeling algorithm was a network flow model which sought to use the length between nodes to detect community membership (1977:454).
+However, in the algorithm, Node 9 was mis-assigned to the Officer’s network using the original algorithm, whereas empirically Node 9 joined the network of the karate teacher, Mr.
+Hi.
+The original discrepancy was explained in reference to Node 9 being near to achieving a black belt, and so the institutional opportunity costs overrode the social network costs.
+
+Contrary to hopes, the application of the distinction centrality measure was not able to explain why Node 9 left for Mr.
+Hi's network.
+The original hypothesis was that, because of the Officer's network closely resembles a star graph, that the level of distinction that Node 9 would command in the network would be low compared to the more heterogeneous network of Mr.
+Hi.
+Results are displayed in Table X.
+The measure demonstrates that Node 9 would have had an overall greater relative distinction if he had stayed in the Officer's network.
+The idea being that, in Mr.
+Hi's network, Node 9 would be more constrained than in the officer's network, but would have higher status because he was directly connected to the high status center in an otherwise stratified network.
+
+The exercise, however, focuses attention on the boundaries of the field.
+The original explanation for the discrepancy points to Node 9's large karate capital.
+If the field is bounded as the ``karate club,'' Node 9's decision is unexpected, but if the field is ``karate practitioners'' then there might be much of the field that is going unobserved in Zachary's original study.
+We do know that some of the students, including Node 9, practiced at Mr.
+Hi's dojo as well as the club.
+The fact that Node 9 had club connections only to the most central members of both the officer's and Mr.
+Hi's networks would indicate that Node 9 only affiliated with likely similarly advanced members of the club.
+If Node 9 was similarly affiliating with advanced students who only attended the dojo, then this would likely influence the decision regarding distinction at the field level.
+Failure to completely capture the positions in the appropriately defined field can create measures that fail to capture empirical outcomes.
+
+\section{Long Ties and Opportunities for Distinction}
+Given that networks are not static, but evolving, the incentives to maximize distinction within a network can inform the evolution of culture as a function of network reorganization.
+As cultural capital is an outcome of both status and uniqueness, the same calculus of optimizing network position can be extended.
+
+Hearkening to the stereotypical model of a village society, we can imagine a social world composed of dense local clusters interconnected only through elite networks.
+In such a network, most individuals would have dense ties within their local subgroup, but have few if any ties outside of the subgroup.
+Such extra-local relationships would be managed by a handful of elites who would derive their status from the deference paid to them locally and through their brokerage with the wider world (see Tilly 1978 on the brokerage role of French priests and the nobility in France prior to the Revolution).
+The incentives for distinguishing oneself in the context of a dense local subgroup through local stratification was liable to engender a decline in the actors status.
+In a tightly connected subgroup, stratification is low, and so the ability to differentiate is also low.
+Any initial actions are likely to lead to a loss of status greater that outweighs the gain in autonomy.
+
+With these initial network conditions, the network pressures for cultural innovation are low.
+However, as economic and technological change brings actors into greater contact, the network of positions also undergoes transformation.
+The changes also begin to create greater local stratification.
+These changes create an opportunity structure for actors to create new connections in the network to increase their own distinction.
+
+We would expect to see in large datasets a tendency for people who are locally constrained and of middling status to attempt to reduce their constraint by attempting to form long ties because it can improve both their status and their autonomy.
+Those of high status might not jeopardize their distinction by associating with those of lower standing, while those of low status are constrained by the reluctance of others to associate with them.
+The expected result would be a flourishing of long tie formation in the middle levels of the distinction hierarchy.
+This prediction can be tested against large longitudinal, well-circumscribed networks such as \citep{bearman2004chains} in the future.
+
+The insight that it is the middling levels that are most likely to form long ties to create their distinction indicates that it is structures with a level of stratification and the opportunity to form long ties that are most likely to create cultural heterogeneity, or in other words a flourishing of subcultures.
+Colleges are not merely opportunities for people from many backgrounds to recombine their cultural repertoires, but are actually network structures that encourage the pursuit of cultural distinction given the long ties that accompany the students new position.
+The expansion of higher education beyond the old elites in the 1950s and 60s was a network transformation that beget the major cultural shifts that began in these institutions.
+These cultural transformations were neither inherent in the students nor the institutions, but came out of the network structure that enabled the pursuit of cultural distinction to match the newly acquired network position.
+
+The cultural practices of elites in a society are similarly dictated by the tradeoffs of status and autonomy that derive from network structure.
+The French elite of Bourdieu presents the ideal haute elite in terms of a stratified cultural disposition from the lower status members of society.
+However, the modern American elite has been characterized not by its sanctification of a limited set of cultural practices, but rather by its embrace of variety, or its cultural omnivorousness \citep{bryson1996anything}.
+Sentence that connects to this citation-> \citep{lizardo2014omnivorousness}.
+The divergence in an elite interested in limited consecration and an elite interested in omnivorousness can be found in the network structure created by national geography and institutions.
+France, dominated by a single major capital as far back as the 1600s, had a singularly concentrated national elite who formed dense interconnections.
+The opportunity for enterprising distinction was foreclosed by interconnection.
+America's varied national elite geography conversely created locally cohesive elites that were connected less intensely at the national level.
+When brought into deeper integration after 1945, the elite themselves similarly formed long ties, creating the positional opportunity for the proliferation of elite cultural forms.
+
+While the above exploration of how network shape changes diversity in cultural distinction practices is at least informative about how understanding the network of positions structures the cultural markers of distinction.
+
+\section{Capital Conversion as Network Integration of Fields}
+One of the problems with the relationship between multiple fields is how capital might be converted between fields.
+The ``rate'' between fields has always been a matter of confusion because it is difficult to quantify.
+Yet, it is an essential feature of an individual's navigation between the positional hierarchies of various fields.
+Seeking to convert a distinct position from one field to a better position in another is a critical strategy in the overall positional portfolio of agents.
+
+However, when thought of as horizontally interlinked networks of vertical fields, the problem of capital conversion becomes tractable as a network problem.
+If someone from an economic field (broadly speaking) were to associate with someone high in some form of cultural capital, it refracts into the economic network as well because associations are at the level of the connections between individuals.
+Personal associations may be somewhat field-specific decisions, but unless field boundaries are rigorously enforced, associations between individuals are largely portfolio-level decisions.
+
+Such a network position perspective aligns with the observation that those high in different types of capital are often willing to associate with one another, borrowing their mutual endorsements to advance their portfolios.
+Thus, those who are ``low'' in certain forms of capital can associate with those who are ``high'' in another type, insofar as it does not create undesirable network ties.
+The prototypical example is the artist and the benefactor.
+While the artist imparts cultural capital to the benefactor, the economic rewards, even if meager, are necessary for the artist.
+However, what is important for the benefactor is that the artist has the \textit{right type} of low economic capital.
+If the economic capital of those at the height of the economy is built upon a workforce, associations with those who buttress their economic position would erode the overall portfolio.
+Such associations would close the distance that is necessary for having a distinct position.
+
+Instead, one can associate with those who are low in economic capital \textit{insofar} as they are not interconnected with the economic structures that buttress the position of the elites of the economic field.
+The artist connected to, or a part of, the proper working class undermines the structure of the economic field.
+The artist with a university education who may work a menial job is, through their social distance from the proper working class, does not erode the structure of the field.
+The conversion of cultural capital into economic capital is fundamentally about not having connections to the core structures of the economic field.
+Thus, those low in one type of capital and high in another will have the most success if the capital they lack is largely peripheral to the main structure of stratification in the field.
+
+Note: "the real logic of the functioning of capital [is the] conversion from one type to another" (1997,54) in Scott 238.
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{1.0\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/PortfolioIntegration.png}
+            \caption{Model of Viable Portfolio Integration}
+            \label{fig:medici}
+    \end{subfigure} \\
+    \caption{}
+    \label{fig:integration}
+\end{figure}
+
+Similarly, those who are in distinct positions created by commonality in the individuals that structure the lower rungs of the network structure are able to easily transfer their position across fields.
+A sports star of low background being elevated in their social status by the working classes is no threat to the economic elites to affiliate freely with such an individual.
+The fields may differ, but they share a common scaffolding of working individuals.
+
+Thus, the demarcation of the field becomes incredibly important in determining whether capital can be transferred.
+Within a field, practices become stratified, but when the field becomes defined as separate, capital among those most distinct in their fields can be exchanged if they share a common scaffolding.
+The key is the stratification rather than the cultural practice.
+Sports might be declasse from the perspective of cultural stratification, but the stratification is generally equivalent (general equivalence citation).
+Furthermore, stratifying the consumption experience is another way to make the ``same'' cultural object maintain the boundaries of distinction.
+
+Floor or box seats, or season tickets, reinforce distinction while allowing for common consumption.
+Similarly, pop culture can be popular because of this aspect of stratification, the pedestal on which a producer of culture is placed.
+Common consumption is not equivalent to common performance.
+Common consumption has the elevation of the producer, but common production lacks stratification, and thus must be stratified through avoidance by the distinct.
+Stratified common consumption is acceptable to elites, but un-stratified common consumption is to be avoided.
+However, those whose economic position may more closely match those who build up the scaffold must avoid common consumption because it would push their position into being coincident with those whom they are seeking to differentiate themselves from.
+This explains the avoidance of those who rely on cultural distinction for their position from popular cultural forms.
+At the same time, those who derive their capital from other fields are able to freely associate with popular cultural productions (which are stratified fields) while eschewing practices (which are un-stratified habitus within the cultural field).
+Capital conversion is not a mechanism of exchange conversion, but network integration.
+Understanding it as integration becomes theoretically generative.
+
+\section{Limitations on Positional Agency}
+One problem with the above measure is that is creates the spectre of limitless positional agency: if a connection is mutually distinction increasing, actors should pursue it.
+Given that distinction increasing positional changes are possible, but go un-enacted, there must be constraints to distinction maximizing action.
+Theoretical considerations must be made to account for costs that constrict connection formation for distinction optimization.
+
+First, there is the matter of social foci \citep{feld1981focused}, or the physical and social spaces that create co-location for the formation of connections as an \textit{opportunity structure.} Brokers are particularly effective when they connect different clusters that would not otherwise be connected (Burt 1992), yet their advantaged position is otherwise threatened if the clusters begin to more directly connect.
+If the distance between them is maintained by the lack of overlap in their social foci, then re-positionings are foreclosed.
+
+Second, there is the problem of \textit{bargaining power}.
+The losers of positional change can retaliate by withdrawing their own connection to the changed node.
+This is particularly effective when multiple nodes withdraw their support in conjunction, with the retaliation leading the changed node to suffer a net decrease in network distinction.
+This runs counter to the predictions that would otherwise emerge from principles of triadic balance, as the maintenance of relational fragmentation is a legitimate strategy for producing high social distinction.
+Those who have experienced secondary education may be able to relate.
+Under conditions of fragmentation, where sides must be chosen, there is less of an issue of counter retaliation.
+
+Third is the matter of \textit{cognitive load}.
+Humans have a limited cognitive capacity and time to successfully maintain the commitments requisite of social relationships \citep{dunbar1995neocortex}.
+While data may capture the structure of a specific field, people are part of many fields that remain unobserved in many empirical studies, but take away resources on their ability to act within the field of concern.
+
+Fourth, is the \textit{cross linkages of fields} in that re-positionings in one field can come at a cost in another field because while the fields are separated in their boundaries, they are interconnected at the level of the individual.
+The formation of a business connection with someone could create positional ramifications in the field of politics for example, and so positional change is otherwise unenacted.
+For example, in the case of the Medici, the economic ties that they formed with the new families had political implications that otherwise prevented the old families from forming similar connections because it would hurt their standing.
+It was only the Medici's earlier fall from grace that enabled such a toleration \textit{padgett1993robust}.
+
+Fifth is \textit{positional uncertainty} about another's position in the field.
+While people are remarkably adept at inferring position in a field through the observation of habitus and capital resources, there remains a good deal of uncertainty about how new connections may upset existing competition structures, particularly in environments that are more circumscribed such as schools or organizations.
+
+Sixth, differences in \textit{habitus} mean that potential connections can fail to form because of the impacts it would have on their overall portfolio of positions.
+Just because of a potential gain in one area does not mean that it would not have costs in other areas that are unobserved.
+This is the problem above where capital conversion is not quite conversion, but incorporation.
+
+While it is difficult to build such impediments to positional agency into the distinction measure, study designs can carefully control for the problems they may otherwise impose.
+Studies of societal conflict which aggregates across fields and within constrained social units can significantly alleviate limitations on positional agency that are external to the distinction measure.
+
+\section{Conclusion}
+Above we have introduced a way of constructing a general measure of distinction from network structure.
+The measure theorizes social distinction as a joint function of status and constraint derived from the pattern of network relations.
+
+In considering how social actors make decisions to maximize their social distinction within a network, scholars must consider the network counterfactuals that actors themselves weigh.
+In the case of the Medici network, actors considered their position within a network both with the Medici and without the Medici, and those who would increase their social distinction in the Medici’s absence undertook action to remove them.
+In the case of the karate network, the decision of the network to split was not made by Node 9, but 9 was forced to decide which pattern of relations to maintain.
+Imagining Node 9 in each of the two networks, 9’s social distinction was higher in Mr.
+Hi’s group than in the officer’s group, and so 9 chose this more desirable place in the social world.
+
+None of this is to suggest that actors are able to do the macro-level network calculation of distinction for the entire network when making decisions about their pattern of relations.
+However, humans are remarkable good at inputting in the network picture despite lacking the particulars and intuiting their position and optimal moves.
+Exploring the cognitive shortcuts that people use to map the complex details of their surrounding networks is an area ripe for academic inquiry.
+In addition, there is a future where computer modeling can estimate network evolution through individual maximization.
+
+This paper simply seeks to establish a measure of social distinction within a network structure.
+While the examples have focused on social distinction in shaping group politics, it is hoped that the measure proposed can be applied to and expand understandings of all forms of social distinction.
+Within sociology, the measure may prove particularly useful for developing new theory and explanations for shifts in competition over cultural distinction.
+However, use cases are anticipated to expand beyond the social world.
+The benefit of the measure maintains the rank of the highest status nodes within a system, but elevates those nodes that derive their position from non-redundant nomination sources.
+In the social world of power, politics, and alliances, it rewards the independence of one's support.
+In a task such as ordering search results, it increases the diversity of information that would be selected in the generation of a ranked list, eliminating redundant information from central cliques of high-status actors.
+The measure may hopefully find a wide variety of future applications.
+
+\newpage
+
+\newpage
 \bibliography{networks}
+
 \bibliographystyle{apalike}

### 2025-04-18 distinction.R
updated

@@ -1,17 +1,18 @@
-distinction <- function(x, scale = FALSE) { #distinction centrality function
+distinction <- function(x) { #distinction centrality function
    library(igraph)
    has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   V <- vcount(x)
    if (has.labels == 0) {
-      V(x)$name <- 1:vcount(x)
+      V(x)$name <- 1:V
       names <- V(x)$name 
       }
    if (has.labels == 1) {
       names <- V(x)$name 
-      V(x)$name <- 1:vcount(x)
+      V(x)$name <- 1:V
       }
    s <- eigen_centrality(x)$vector
-   d <- 0
-   u <- rep(vcount(x), 0)
+   d <- rep(V, 0)
+   u <- rep(V, 0)
    for (i in as.character(V(x)$name)) {
       j <- names(neighbors(x, i))
       x.d <- delete_vertices(x, i)
@@ -22,7 +23,7 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
          } #end if
       else if (c == 0 & e == 1) { #empty graph
          s.a <- 0
-         } #end else 1
+         } #end first else 
       else if (c == 0 & e == 0) { #disconnected non-empty graph
          C <- components(x.d)$membership
          names(C) <- V(x)$name[-as.numeric(i)]
@@ -35,17 +36,14 @@ distinction <- function(x, scale = FALSE) { #distinction centrality function
             }
          names(s.a) <- names(C)
          s.a <- s.a[j]
-         } #end else 2
-      u[i] <- sum(s.a)/length(s.a) #average neighbor centrality
-      d[i] <- s[i] - u[i] #distinction centrality
+         } #end second else
+      print(i)
+      print(s.a)
+      u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
+      d[i] <- s[i] - u[i] #i's distinction centrality
    } #end i for loop
-   d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)
-   if (scale == TRUE) {
-      s <- s * scalar
-      }
-   d <- s - u
    sd <- (s*scalar) - u
    dat <- data.frame(d = d, sd = sd, s = s, u = u, scalar = scalar)
    dat <- round(dat, 4)

### 2025-04-18 distinction.R
extra extra

@@ -42,6 +42,7 @@ distinction <- function(x) { #distinction centrality function
       u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
       d[i] <- s[i] - u[i] #i's distinction centrality
    } #end i for loop
+   d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)
    sd <- (s*scalar) - u

### 2025-07-05 manuscript.tex

@@
 \usepackage{subcaption}
+\usepackage[hidelinks]{hyperref}
 \bibpunct[: ]{(}{)}{;}{a}{}{,} 
@@
 \begin{abstract}	
-In this paper a new network measure, distinction centrality, is introduced.
-The measure is derived from Bourdieu's theory of the competition for distinction in a field where actors act both with agency and within the constraints imposed by other actors.
-The measure subtracts the autonomy of each actor \textit{i} within the network from their constraint.
-Autonomy is measured using eigenvector centrality for each actor \textit{i}.
-In contrast, constraint is measured by calculating the average eigenvector of nodes \textit{i}'s neighbors in a recalculated network with node \textit{i} removed.
+This paper introduces the concept of \textit{distinction centrality}, developing a network metric designed to capture it.
+The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, where other actors and their actions provide opportunities and constraints to maximize social positioning.
+The basic idea behind the network metric of distinction is to subtract the \textit{autonomy} of each actor within the network from their \textit{constraint}, such that highly autonomous (and therefore less constrained) actors have more distinction.
+Autonomy is given by the focal actor's Eigenvector Centrality score (recording connections to well-placed others), and constraint is defined by the average Eigenvector Centrality score of each actor's neighbors in a hypothetical network where the focal actor is removed (indicating how others would benefit from that actor's exiting the network).
 A scalar is then applied to create mathematical and sociological equivalence between autonomy and constraint.
-The resulting node-level measures create a measure of distinction, where the uniqueness of a node's associations is more heavily rewarded than under eigenvector centrality.
-The resulting measure is applied to both Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club to show that the observed actions of the agents involved are consistent with distinction maximization.
-The resulting measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.
+The resulting node-level measures create a measure of \textit{distinction}, where the uniqueness of an actor's relations is more heavily rewarded than under the standard Eigenvector Centrality score.
+We analyze two classic datasets, Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club, to demonstrate that the observed actions of the agents involved are consistent with the maximization of distinction.
+We close by outlining how the resulting distinction measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.
 \end{abstract}
@@
 \section{Distinction Beyond Taste}
-Popular within cultural sociology, the idea of distinction has generated a rich literature to explain cultural differentiation.
-Distinction, as the expression of status and uniqueness, is a social end in itself.
-The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation \citep{bourdieu1984distinction}.
-Broader social distinction is often measured as the shadow of cultural distinction or collapsed into the concept of status more generally, which ignores questions of how network constraint impacts the capacity of actors to be distinct.
+Popular within cultural sociology, the concept of distinction has generated a rich body of literature aimed at explaining cultural differentiation within social fields.
+From this perspective, the pursuit of distinction, as the expression of an actor's status and uniqueness, is an end in itself, providing the basic motivation for action \citep{martin2003field}.
+The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation enacted by designated institutional authorities \citep{bourdieu1984distinction}.
+
+In this last respect, the more encompassing notion of \textit{social} distinction, implying an actor's embeddedness in a relational field \citep{erikson2013formalist-400, fuhse2021social-9cb}, is often measured as the shadow counterpart of cultural distinction or collapsed into the concept of status more generally \citep{podolny2010status-1a6}.
+This approach overlooks questions of how network constraints impact the capacity of actors to be distinct.
 A generalized, measured ordering of social distinction that is derivative from a network of concrete social relations would give Bourdieu's generalized conception of distinction a broader methodological base from which to conduct empirical analysis.
@@
 \subsection{What is Distinction?}
-Pierre Bourdieu was interested in the competition among people for positions within the hierarchy.
-Bourdieu defined the field as a social space where actors operate within socially negotiated boundaries that arbitrate relevant competitive claims over position.
-In interplay with the field, individuals develop a habitus of embodied dispositions, expressed as a cognitive ease with particular types of settings, objects, and performances.
+Bourdieu was primarily interested in the competition among actors for positions within the hierarchy implied by the field \citep{anheier1995forms, bourdieu1993field-8ad}.
+Bourdieu defined the field as a social space where actors operate within socially negotiated boundaries that arbitrate relevant competitive claims over position \citep{bourdieu1996rules-393}.
+In interplay with the field, individuals develop a habitus of embodied dispositions, expressed as cognitive ease with particular types of settings, objects, and performances.
 An actor's position in the field influences their habitus.
-In the same way, their habitus determines their future possibilities within the field, while also structuring the opportunities available for others in the field.
-Actors compete for positions in the field via various forms of capital, or resources that are socially-agreed upon as desirable within a field, thereby facilitating the formation of connections that both order and reflect the hierarchy of the field.
+Similarly, their habitus determines their future possibilities within the field, while also shaping the opportunities available to others in the field.
+Actors compete for positions in the field via various forms of capital or resources that are socially agreed upon as desirable within a field \citep{martin2003field}, thereby facilitating the formation of connections that both order and reflect the hierarchy of the field.
 The interaction of the desirability and uniqueness of the capitals possessed by an individual determines their place in the field's positional hierarchy.
@@
 There is a strong correlation between those in the position of cultural and economic elites.
-Still, such correlation is not guaranteed at the individual level even if it is relevant at the level of the fields.
+Still, such a correlation is not guaranteed at the individual level, even if it is relevant at the field level.
 
 While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}.
-For example, while cultural practices may be a marker of difference, the absence of association with others outside the milieu, distinction is also a matter of agency within the milieu, a question of the constraint imposed by the set of relationships within which the actor is embedded.
+For example, while cultural practices may be a marker of difference, the absence of association with others outside the milieu is also a matter of agency within the milieu, a question of the constraints imposed by the set of relationships within which the actor is embedded.
 For Bourdieu, the struggle for position in a field was a product of a field of action and a field of forces \citep{martin2003field}.
-The field of action describes the agency of actors actively advancing their position.
+The field of action refers to the agency of actors actively advancing their interests.
 In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be upset by positional transformations.
@@
 In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}.
-Translated to network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle is reflective of the constraint neighbors put on an actor.
+Translated to network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle is reflective of the constraints neighbors put on an actor.
 An actor with high influence is well-connected to others who can be mobilized for effective action.
@@
 We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy.
-Nevertheless, we use status and autonomy below as general terms to describe the ability of actors to take action versus the level of imposition from the forces of constraint.
+Nevertheless, we use ``status" and ``autonomy" below as general terms to describe the ability of actors to take action versus the level of imposition from the forces of constraint.
 
 In developing a broader understanding and measure of social distinction, actor-level incentives and structural impediments to action become apparent.
-When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly forecaste.
+When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly forecasted.
 
 \subsection{Position as the Relational Basis for a Distinction Measure}
-Bourdieu's separation of distinction into habitus and position is no sociological problem at all, but creates the analytical problem of how an actor's network position creates dispositions and how dispositions create the opportunity for network mobility.
-Both dispositions and positions are fundamentally relational outcomes in sociological terms, but in creating a network measure of distinction, only the relational basis of position can be considered.
+Bourdieu's separation of distinction into habitus and position is not a sociological problem at all, but rather creates the analytical problem of how an actor's network position generates dispositions and how these dispositions create opportunities for network mobility.
+Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when creating a network measure of distinction, only the relational basis of position can be considered.
 
 However, to the extent that position and habitus reflect each other through their symbiotic fabrication, the ability to empirically capture only one of the two components is sufficiently accurate to measure a social system's distinction hierarchy with confidence over a short window of time.
-Actors simply should not have a network position that does not match their habitus, and their ability to radically change positions is governed by their current habitus and social position.
-If the transformation of habitus is a stepwise interplay with positional movement that unfolds over time, the measure becomes less informative if capturing networks over extended time periods.
-However, even over long periods of time this theoretical collapse that permits a network measured methodological shortcut may still be adequate in a moderately stable social environment.
+Actors should not hold a network position that does not align with their habitus, and their current habitus and social position determine their ability to radically change positions.
+If the transformation of habitus is a stepwise interplay with positional movement that unfolds over time, the measure becomes less informative if it captures networks over extended periods.
+However, even over long periods, this theoretical collapse, which permits a network-measured methodological shortcut, may still be adequate in a moderately stable social environment.
 
-To put the measure of distinction on a firm theoretical foundation, it is first important to make explicit the relationship between empirical data and social theory that is the basis of social network analysis.
-Network measures are fundamentally based on the idea that researchers are in some way capturing a relationship between two objects.
-A tie between two nodes is capturing in some way their connection however so defined.
-Such connections can be broadly classified as mutual in the case of the relationship quality being equal in both directions, or directional in the case of the qualities being unequal.
-In the absence of direct measurement of qualities however, many networks are measured as consisting of mutual ties.
+To establish a firm theoretical foundation for the measure of distinction, it is first essential to make explicit the relationship between empirical data and social theory that forms the basis of social network analysis.
+Network measures are fundamentally based on the idea that researchers are capturing a relationship between two objects in some way.
+A tie between two nodes captures, in some way, their connection, however it is defined.
+Such connections can be broadly classified as mutual, in the case where the relationship quality is equal in both directions, or directional, in the case where the qualities are unequal.
+In the absence of direct measurement of qualities, however, many networks are measured as consisting of mutual ties.
 However, even in the case of networks composed of only mutual ties, hierarchy can still be assessed from the pattern of relationships.
-In such networks, we are still able to rank the direction of power and deference through the absence of ties between lower and higher nodes.
-For example, in an organizational pyramid, we would be able to detect the CEO from the presence of ties with the vice presidents and the absence of ties with middle management and production workers.
+In such networks, we can still rank the direction of power and deference through the absence of ties between lower and higher nodes.
+For example, in an organizational pyramid, we can detect the CEO by observing the presence of ties with vice presidents and the absence of ties with middle management and production workers.
 We can do this through the measurement of a node's network status.
 
-The first aspect of social distinction generally is \textit{status}.
-Status is the internal stratification of all members of the network, along with connections of deference and obligation.
-In the case of politics, status is the ability to access those who themselves have higher levels of access, with those most central to the access network having the ability to make decisions.
+The first aspect of social distinction is \textit{status}.
+Status refers to the internal stratification of all network members, along with the connections of deference and obligation.
+In the case of politics, status refers to the ability to access those who themselves have higher levels of access, with those most central to the access network having the authority to make decisions.
 This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972norms}.
-Status is higher for actors when the people they are connected to are themselves important, and accessibility is just a political reframing of the context.
-The internal stratification of individuals is determined by who has greater connections to those who have greater connections, with those with few connections to other unimportant people being at the bottom of the hierarchy \citep{bonacich1972norms}.
+Status is higher for actors when the people they are connected to are themselves influential, and accessibility is merely a political reframe of the context.
+The internal stratification of individuals is determined by who has greater connections to those with even greater connections, with those having few connections to other important people being at the bottom of the hierarchy \citep{bonacich1972norms}.
 
@@
 
-The interaction of influence and autonomy combine to create an actor’s overall distinction in the network.
+The interaction of influence and autonomy combines to create an actor’s overall distinction in the network.
 The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction.
 An increase in one aspect can often, but not necessarily, lead to a decrease in the other.
-For example, a connection with a someone with high accessibility other can lead to a decrease in one’s autonomy, and new access comes with new constraints.
+For example, a connection with someone with high accessibility can lead to a decrease in one’s autonomy, and new access comes with new constraints.
 However, the trade-off can maximize one’s overall distinction, so there are gains from the connection.
@@
 \section{A Generalized Measure of Network Distinction}
-Below we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and point to the availability of an R program so that researcher's may easily implement the measure in their own research.
+Below, we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and indicate the availability of an R program to facilitate easy implementation of the measure in further wok.
 
@@
 Distinction as a theoretical concept is composed of status mediated by autonomy.
-A distinction measure can reflect this by considering an actor'ss status and then discounting their status by the status of their neighbors independent of the actor.
-The more reliant an actors neighbors are on the actor for their status, the lower that actors ability to exert their own influence, and thus the lower their distinction.
-In other words, autonomy is determined by how much one's neighbors need you to sustain their own position in the network.
+A distinction measure can reflect this by considering an actor's status and then discounting their status by the status of their neighbors, independent of the actor.
+The more reliant an actor's neighbors are on the actor for their status, the lower the actor's ability to exert their influence, and thus the lower their distinction.
+In other words, autonomy is determined by how much one's neighbors rely on you to maintain their position in the network.
 
-Distinction centrality can be measured through the implementation of the following algorithm.
-\[\beta_i=Sx_i-{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}} \]
-Let \(\beta\) be the distinction centrality of a given individual \textit{i}.
+Distinction centrality can be measured using the following expression:
+\begin{equation}
+\beta_i=Sx_i-{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}} 
+\end{equation}
+
+Let $\beta_i$ be the distinction centrality of a given individual \textit{i}.
 The first term captures the status of a given actor.
 Let \textit{x} be the eigenvector centrality \citep{bonacich72} of the designated individual.
-Let S be a scalar that adjusts the social value placed on status compared to constraint, to be discussed below.
+Let S be a scalar that adjusts the social value placed on status relative to constraint, as discussed below.
 The second terms captures the element of autonomy.
 Removing individual \textit{i} from the network, compute the eigenvectors of the remaining individuals and sum those that are connected to individual \textit{i}, taking the average eigenvector of neighbors \textit{j} as the constraint confronting node \textit{i} in the network.
-This is substantively the same mechanism as conducted in a jackknife resampling procedure, except rather than forming a sampling distribution, we are measuring local constraint.
+This is substantively the same mechanism as conducted in a jackknife resampling procedure, except that rather than forming a sampling distribution, we are measuring local constraint.
 Finally, subtract the status of the average neighbor connected to \textit{i} from \textit{i}’s scalar adjusted eigenvector centrality in the whole network.
@@
 If a node is an isolate, its eigenvector centrality should be set at 0.
-In the case of a network with no connections (such as a star graph), it can accidentally be calculated as 1.00 in programs, but given that it is still a network of no connections, setting isolates at 0.00 is theoretically appropriate when considering that status is a reflection of connections.
+In the case of a network with no connections (such as a star graph), it can be accidentally calculated as 1.00 in programs.
+However, given that it is still a network with no connections, setting isolates at 0.00 is theoretically appropriate, considering that status is a reflection of connections.
 It would be inappropriate for an isolate to have the same status as the highest status node in a large network.
@@
 \subsection{Scalar Adjustment}
-First, a scalar is required because relative value of status and autonomy is not inherently fixed in a social system.
-We might imagine situations where one desires more status at the expense of autonomy if the rewards to status are higher, or value autonomy more highly if the rewards to status are low.
+First, a scalar is required because the relative value of status and autonomy is not inherently fixed in a social system.
+We might imagine situations where one desires more status at the expense of autonomy if the rewards to status are higher, or values autonomy more highly if the rewards to status are low.
 There cannot be an assumed unadjusted equivalence between the resulting eigenvectors of the two terms for this theoretical level.
 
-Additionally, because of the hierarchical nature of networks, the average constraint in the network is larger than the average status.
+Additionally, due to the hierarchical nature of networks, the average constraint in the network is greater than the average status.
 The high average constraint of their neighbors is often much larger than the impact of status.
-The result is that, at the level of the entire network, that those who are deeply embedded among the most elites, without their own basis of supporters, are very indistinct when considering the high constraints placed on them by their high status alters.
-Thus, the calculated results without a scalar can fail to capture the appropriate value on status as compared to constraint.
+The result is that, at the level of the entire network, those who are deeply embedded among the most elite, without a basis of supporters, are very indistinct when considering the high constraints placed on them by their high-status alters.
+Thus, the calculated results without a scalar may fail to capture the appropriate value of status compared to the constraint.
 
-While an arbitrary scalar is possible, it can lead to erroneous results when tested against empirical networks.
-However, a scalar can be derived from the network itself because of the field positional interplay of status and constraint.
+While an arbitrary scalar is possible, it can yield erroneous results when applied to empirical networks.
+However, a scalar can be derived from the network itself due to the field positional interplay between status and constraint.
 Imagining two actors of equal status and personal constraint, one in an averagely more constrained system and the other in a less averagely constrained system, with average status otherwise equal.
@@
 With high constraint, status takes on greater importance in determining social distinction because it compels deference.
-In other words, it is the difference between hierarchy with constraint, and hierarchy without constraint.
-Status with weak constraint means a weaker compulsion of deference.
-The structure of constraint redounds into the impact of status on social distinction beyond its own contribution.
+In other words, it is the difference between a hierarchical system with and without constraints.
+Status with a weak constraint means a weaker compulsion of deference.
+The structure of constraint redounds into the impact of status on social distinction beyond its contribution.
 
 With this social understanding of how constraint interacts with the transmission of status, an endogenous scalar can be derived from the network.
-The average constraint of actors within in the network divided by the average status of actors in the network creates a scalar that reflects the relationship between status and constraint.
+The average constraint of actors within the network divided by the average status of actors in the network creates a scalar that reflects the relationship between status and constraint.
 
@@
 
-Under conditions of high average constraint and low average status, the scalar is large, reflecting the importance of status in determining social distinction.
-Under conditions where average constraint is low and average status is high, the scalar is weaker, reflecting a system where status is less important in determining social distinction.
+Under conditions of high average constraint and low average status, the scalar is large, indicating the significant role of status in determining social distinction.
+Under conditions where the average constraint is low and the average status is high, the scalar is weaker, reflecting a system in which status is less important in determining social distinction.
 Under very large-scale conditions, the averages of status and constraint should trend towards 1, weakening the necessity of the scalar.
-However, under constrained conditions, particularly elite networks with missing data of the social scaffolding that created the network elites, the scalar is more important for explaining action because the range of eigenvector network measures are otherwise being artificially expanded due to the missing data.
+However, under constrained conditions, particularly in elite networks with missing data on the social scaffolding that created the network elites, the scalar is more important for explaining action because the range of eigenvector network measures is otherwise artificially expanded due to the missing data.
 
-Without a scalar, networks with any degree of hierarchy see the average constraint swamp the average status because many low status nodes tie into high status nodes.
-The advantage of this scalar is to make the average scalar status in the network equal to the average constraint in the network.
+Without a scalar, networks with any degree of hierarchy see the average constraint overwhelm the average status because many low-status nodes are tied to high-status nodes.
+The advantage of this scalar is to ensure that the average scalar status in the network equals the average constraint in the network.
 Thus, total status is equal to total constraint, and from there it becomes a matter of distribution among members.
-From there however, it allows for comparability between networks that would otherwise not be possible.
-With the understanding that we have, through the scalar, adjusted for a network where ones combination of status and constraint is better or worse, networks can be compared so long as the unobserved social context within the network changes are made is otherwise stable.
+From there, however, it enables comparability between networks that would otherwise be impossible.
+With the understanding that we have, through the scalar, adjusted for a network where one's combination of status and constraint is better or worse, networks can be compared so long as the unobserved social context within the network remains stable.
 
@@
 While node 1 maintains high eigenvector centrality, the eigenvector centrality of the other nodes increases, while their constraint decreases.
-It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their own subgroups.
+It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their respective subgroups.
 This position of brokerage is more constrained than the star graph because the other actors are connected in subgroups.
@@
 In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
-With a scalar adjustment, the stratification increases, giving a bit more privilege to Node 1, but demonstrating the extent to which Node 1's distinction is eroded.
+With a scalar adjustment, the stratification increases, giving Node 1 a bit more privilege, but also demonstrating the extent to which Node 1's distinction is eroded.
 In a maximally connected graph, the distinction of each node would also go to 0.00, as there is no network differentiation among nodes.
@@
 Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
-Compared to the structural fold,  connection 3-2 and connection 6-7 have been removed.
+Compared to the structural fold, connections 3-2 and 6-7 have been removed.
 Measurement results are in Table 3.
 Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
-The resulting scalar adjusted distinction measures well reflects this stratification, with Node 1 retaining its distinction, Node's 4 and 5 failing in the middle position, and Node's 2, 3, 6, and 7 falling to the bottom.
+The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
 
 \textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
-This long tie stratifies the network even more than in Model (c) bringing Nodes 2 and 7 quite close to 4 and 5.
+This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
 The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
@@
 This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Node's 2 and 7 actually increase beyond that of 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1 as their mutual neighbor.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
 
-\subsection{R Package}
-The analyses below are conducted with a program that implements the above distinction centrality measure. Omar wrote it. He's a cool guy. Maybe he would like to do a whole separate article on it?
+\subsection{Implementation}
+To conduct the analyses below, we use a custom function written for the \textit{R} statistical computing environment \citep{R} software.\footnote{The function can be found here \href{https://github.com/olizardo/Jilbert-Distinction-Centrality/blob/main/distinction.R}{https://github.com/olizardo/Jilbert-Distinction-Centrality/blob/main/distinction.R}}
 
@@
     \end{subfigure}
-    \caption{}
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in blue, nodes with the lowest distinction are shown in red, and nodes with distinction scores close to zero are shown in purple.}
     \label{fig:toys}
@@
 
-\section{Long Ties and Opportunities for Distinction}
+\section{Distinction as Search Algorithm}
+
+\section{Distinction with Structural Holes vs. Structural Folds}
+
+\section{Implications for Theories of Distinction}
+\subsection{Long Ties and Opportunities for Distinction}
 Given that networks are not static, but evolving, the incentives to maximize distinction within a network can inform the evolution of culture as a function of network reorganization.
@@
 
-\section{Capital Conversion as Network Integration of Fields}
+\subsection{Capital Conversion as Network Integration of Fields}
 One of the problems with the relationship between multiple fields is how capital might be converted between fields.
@@
 
-\section{Limitations on Positional Agency}
+\subsection{Limitations on Positional Agency}
 One problem with the above measure is that is creates the spectre of limitless positional agency: if a connection is mutually distinction increasing, actors should pursue it.

### 2025-07-05 index.qmd
updated function
fixed function
new func who dis

@@
    library(ggpubr)
-   library(here)
    source("distinction.R")
@@
 ```{r}
+   source("distinction.new.R")
+   distinction.new(g1, norm = TRUE)
+   distinction.new(g1, norm = FALSE)
+```
+
+```{r}
    plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
@@
 ```
+
+```{r}
+   source("distinction.R")
+   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
+   g <- graph_from_edgelist(g, directed = FALSE)
+   distinction(g)
+```

### 2025-07-05 distinction.new.R

@@ -1,0 +1,72 @@
+distinction.new <- function(x, norm = TRUE) { #distinction centrality function
+   library(igraph)
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   V <- vcount(x)
+   if (has.labels == 0) {
+      V(x)$name <- 1:V
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
+      V(x)$name <- 1:V
+      }
+   s <- eigen_centrality(x)$vector
+  if (norm == FALSE) {
+      s <- abs(eigen(as.matrix(as_adjacency_matrix(x)))$vectors[, 1])
+      names(s) <- V(x)$name
+      }
+   print(s)
+   d <- rep(V, 0)
+   u <- rep(V, 0)
+   for (i in as.character(V(x)$name)) {
+      j <- names(neighbors(x, i))
+      #print(i)
+      #print(j)
+      x.d <- delete_vertices(x, i)
+      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
+      e <- as.numeric(ecount(x.d) == 0) #checking for empty
+      if (c == 1 & e == 0) { #connected non-empty graph
+         s.a <- eigen_centrality(x.d)$vector[j]
+          if (norm == FALSE) {
+             A <- as.matrix(as_adjacency_matrix(x.d))
+             rownames(A) <- V(x.d)$name
+             colnames(A) <- V(x.d)$name
+             s.a <- abs(eigen(A)$vectors[, 1])
+             #print(s.a)
+          } #end sub if
+        } #end main if
+      else if (c == 0 & e == 1) { #empty graph
+         s.a <- 0
+         } #end first else 
+      else if (c == 0 & e == 0) { #disconnected non-empty graph
+         C <- components(x.d)$membership
+         names(C) <- V(x)$name[-as.numeric(i)]
+         s.a <- rep(0, length(C))
+         for (k in unique(C)) {
+            sub.g <- subgraph(x.d, names(which(C == k)))
+            if (vcount(sub.g) > 1) {
+               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
+              if (norm == FALSE) {
+                  A <- as.matrix(as_adjacency_matrix(sub.g))
+                  rownames(A) <- V(sub.g)$name
+                  colnames(A) <- V(sub.g)$name
[…]

### 2025-07-05 distinction.new.R
more new func

@@ -28,10 +28,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
       if (c == 1 & e == 0) { #connected non-empty graph
          s.a <- eigen_centrality(x.d)$vector[j]
           if (norm == FALSE) {
-             A <- as.matrix(as_adjacency_matrix(x.d))
-             rownames(A) <- V(x.d)$name
-             colnames(A) <- V(x.d)$name
-             s.a <- abs(eigen(A)$vectors[, 1])
+             s.a <- abs(eigen(as.matrix(as_adjacency_matrix(x.d)))$vectors[, 1])
              #print(s.a)
           } #end sub if
         } #end main if
@@ -47,10 +44,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
             if (vcount(sub.g) > 1) {
                s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
               if (norm == FALSE) {
-                  A <- as.matrix(as_adjacency_matrix(sub.g))
-                  rownames(A) <- V(sub.g)$name
-                  colnames(A) <- V(sub.g)$name
-                  s.a[which(C == k)] <- abs(eigen(A)$vectors[, 1])
+                  s.a[which(C == k)] <- abs(eigen(as.matrix(as_adjacency_matrix(sub.g)))$vectors[, 1])
                 } #end sub if
             } #end main if
             }

### 2025-07-17 analysis.qmd
new stuff who dis

--- 2025-07-05 index.qmd
@@
 ---
-title: "Jilbert's Distinction Centrality"
+title: "Distinction Centrality Analysis"
 execute: 
   eval: true
-  echo: true
+  echo: false
   output: true
@@
   message: false
-format: 
-   html:
-      code-line-numbers: true
-bibliography: networks.bib
 ---
@@
 ```
-
-According to @jilbert24, the Distinction Centrality ($D_i$) of a node is given by the difference between the *status* ($S_i(G)$) and the *constraint* ($C_i(G)$) experienced by each node:
-
-$$
-   D_i = S_i(G)  - C_i(G)
-$$
-
-Status is measured using the usual Bonacich eigenvector centrality (normalized to have maximum 1.0) computed in the full graph $G$.
-Constraint, in turn, is given by the average status of $i$'s neighbor in the *node deleted subgraph* that excludes $i$.
-
-$$
-C_i(G) = \frac{\sum_{j \in N(i)} S_j(G - i)}{N} 
-$$
-
-Where $N(i)$ is the set of $i$'s neighbors, and $S_j(G -i)$ is the eigenvector centrality of node $j$ in the node deleted subgraph of $G$ that excludes $i$.
-Nodes are more constrained to the extent that others gain status in their absence.
-The Distinction of a node thus increases with its own status and decreases to the extent that others would gain status if that node was not around.
-
-The normalized version of Distinction Centrality ($D^*$) multiplies each node's status score by the parameter $\theta$, which is ratio of the average of constrain scores and the average of status scores of each node in the the network:
-
-$$
-\gamma = \frac{\frac{1}{N}\sum_i C_i(G)}{\frac{1}{N}\sum_i S_i(G)}
-$$
-
-The normalized distinction is then given by:
-
-$$
-D^*_i = \gamma S_i(G)  - C_i(G)
-$$
 
@@
     tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
-```
-
-```{r}
-   source("distinction.new.R")
-   distinction.new(g1, norm = TRUE)
-   distinction.new(g1, norm = FALSE)
 ```
@@
 ```{r}
-   source("distinction.R")
    g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))

### 2025-07-17 diss.status.R

@@ -1,0 +1,25 @@
+diss.status <- function(x) { 
+   library(igraph)
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   V <- vcount(x)
+   if (has.labels == 0) {
+      V(x)$name <- 1:V
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
+      V(x)$name <- 1:V
+      }
+  vertex.sim <- function(w) {
+      z <- as.matrix(as_adjacency_matrix(w))
+      z.p <- z %*% z
+      z.q <- z %*% (1 - z) 
+      z.r <- (1 - z) %*% z
+      s <- z.p / (z.p + z.q + z.r)
+      return(list(sim = s, adj = z))
+      }
+  sim.res <- vertex.sim(x)
+  d.s <- abs(eigen(sim.res$adj * (1 - sim.res$sim))$vectors[, 1])
+  names(d.s) <- V(x)$name
+  return(d.s/max(d.s))
+}

### 2025-07-17 distinction.R

@@ -1,4 +1,4 @@
-distinction <- function(x) { #distinction centrality function
+distinction <- function(x) { 
    library(igraph)
    has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
    V <- vcount(x)

### 2025-07-17 distinction.new.R

@@ -1,66 +1,0 @@
-distinction.new <- function(x, norm = TRUE) { #distinction centrality function
-   library(igraph)
-   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
-   V <- vcount(x)
-   if (has.labels == 0) {
-      V(x)$name <- 1:V
-      names <- V(x)$name 
-      }
-   if (has.labels == 1) {
-      names <- V(x)$name 
-      V(x)$name <- 1:V
-      }
-   s <- eigen_centrality(x)$vector
-  if (norm == FALSE) {
-      s <- abs(eigen(as.matrix(as_adjacency_matrix(x)))$vectors[, 1])
-      names(s) <- V(x)$name
-      }
-   print(s)
-   d <- rep(V, 0)
-   u <- rep(V, 0)
-   for (i in as.character(V(x)$name)) {
-      j <- names(neighbors(x, i))
-      #print(i)
-      #print(j)
-      x.d <- delete_vertices(x, i)
-      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
-      e <- as.numeric(ecount(x.d) == 0) #checking for empty
-      if (c == 1 & e == 0) { #connected non-empty graph
-         s.a <- eigen_centrality(x.d)$vector[j]
-          if (norm == FALSE) {
-             s.a <- abs(eigen(as.matrix(as_adjacency_matrix(x.d)))$vectors[, 1])
-             #print(s.a)
-          } #end sub if
-        } #end main if
-      else if (c == 0 & e == 1) { #empty graph
-         s.a <- 0
-         } #end first else 
-      else if (c == 0 & e == 0) { #disconnected non-empty graph
-         C <- components(x.d)$membership
-         names(C) <- V(x)$name[-as.numeric(i)]
-         s.a <- rep(0, length(C))
-         for (k in unique(C)) {
-            sub.g <- subgraph(x.d, names(which(C == k)))
-            if (vcount(sub.g) > 1) {
-               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
-              if (norm == FALSE) {
-                  s.a[which(C == k)] <- abs(eigen(as.matrix(as_adjacency_matrix(sub.g)))$vectors[, 1])
-                } #end sub if
-            } #end main if
-            }
-         names(s.a) <- names(C)
-         s.a <- s.a[j]
-         } #end second else
[…]

### 2025-07-17 analysis.qmd
some new stuff

@@
    library(ggpubr)
-   source("distinction.R")
-```
-
-```{r}
-   tab.cent <- function(x, d = 3, name = "name", caption = "", label = "label") { #table function
-   library(kableExtra)
-   t <- kbl(x, 
-            format = "latex", booktabs = TRUE, linesep = "",
-            digits = d, row.names = FALSE,
-            col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
-            caption = caption, label = label
-            ) %>% 
-            kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
-            save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))
-   }
+   source(here("Functions", "distinction.R"))
+   source(here("Functions", "plot.graph.norm.R"))
+   source(here("Functions", "tab.cent.R"))
 ```
@@
 
-```{r}
-   plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
-      library(ggraph)
-      d <- distinction(x)[,3]
-      nc <- rep("", length(d))
-      nc[which(d < -0.05)] <- "red"
-      nc[which(d > 0.05)] <- "blue"
-      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
-      if (is.null(V(x)$name) == TRUE) {
-         n <- 1:vcount(x)
-         tc <- "white"
-         s <- vs
-         }
-      if (is.null(V(x)$name) == FALSE) {
-         n <- V(x)$name
-         tc <- nc
-         vs <- 0
-         }
-      p <- ggraph(x, layout = l)
-      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
-      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
-      p <- p + geom_node_text(aes(label = n), size = ts, color = tc, fontface = "bold")
-      p <- p + theme_graph() 
-   return(p)
-   }
-```
-
-```{r}
+```{r Toy Networks Plots}
    png(here("Plots", "star.png"))
@@
 
-```{r}
+```{r Medici Distinction Plots}
    medici1 <- as.matrix(read.csv(here("Data", "MediciEdgeList.csv")))
@@
 
-```{r}
+```{r Search Model Distinction}
    g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
@@
 ```
+
+```{r}
+   make.broker.graphs <- function(n = 10) {
+      g <- make_empty_graph(9, directed = FALSE)
+      g <- g + edge(1,2)
+      g <- g + edge(1,3)
+      g <- g + edge(2,4)
+      g <- g + edge(2,5)
+      g <- g + edge(2,6)
+      g <- g + edge(3,7)
+      g <- g + edge(3,8)
+      g <- g + edge(3,9)
+      el <- vector(mode = "list", length = n)
+      el[[1]] <- g
+      a <- 10
+      b <- 11
+      c <- 12
+      d <- 13
+      for (i in 2:n) {
+         g <- add_vertices(g, 4)
+         g <- g + edge(1,a)
+         g <- g + edge(a,b)
+         g <- g + edge(a,c)
+         g <- g + edge(a,d)
+         el[[i]] <- g
+         a <- a + 4
+         b <- b + 4
+         c <- c + 4
+         d <- d + 4
+      }
+   return(el)
+   }
+   b <- make.broker.graphs(30)
+   c <- lapply(b, distinction)
+   d <- sapply(c, function(x) {x[2, 2]})
+```
+
+    p <- p + geom_node_point(aes(x = x, y = y), size = 18, color = "tan2")
+
+```{r}
+   library(patchwork)
+   library(ggplotify)
+   library(ggraph)
+   gg <- function(x) {
+      n <- vcount(x)
+      V(x)$name <- 1:n
+      w <- ggraph(x, layout = "kk") + 
+      geom_edge_link(color = "steelblue") + theme_graph() +
+      geom_node_point(size = 5, color = c("blue", rep("tan2", n - 1))) + 
+      geom_node_text(aes(label = name), color = "white", size = 3) +
+      ylim(-4,4) + xlim(-4,4) 
+      return(w)
+      }
+   p.list <- lapply(b, gg)
+   for (i in 1:length(p.list)) {
+      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
+         theme(plot.title = element_text(size = 11))
+      }
+   wrap_plots(p.list[c(1:6)], nrow = 2)
+   ggsave(here("Plots", "tree-examples.png"), width = 10, height = 7, units = "in")
+```
+
+```{r}
+   dat <- data.frame(d = d, n = 1:length(d))
+   p <- ggplot(dat, aes(n, d, group = 1)) 
+   p <- p + geom_point(size = 3, color = "blue")
+   p <- p + geom_line(linewidth = 0.75, color = "blue")
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + ylim(-0.1, 1)
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 12),
+                  axis.title = element_text(size = 14, face = "bold"))
+   p
+
+```

### 2025-07-17 Functions/distinction.R

@@ -37,11 +37,9 @@ distinction <- function(x) {
          names(s.a) <- names(C)
          s.a <- s.a[j]
          } #end second else
-      print(i)
-      print(s.a)
       u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
       d[i] <- s[i] - u[i] #i's distinction centrality
-   } #end i for loop
+      } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)

### 2025-07-17 Functions/plot.graph.norm.R

@@ -1,0 +1,24 @@
+plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
+  library(ggraph)
+  d <- distinction(x)[,3]
+  nc <- rep("", length(d))
+  nc[which(d < -0.05)] <- "red"
+  nc[which(d > 0.05)] <- "blue"
+  nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
+  if (is.null(V(x)$name) == TRUE) {
+      n <- 1:vcount(x)
+      tc <- "white"
+      s <- vs
+      }
+  if (is.null(V(x)$name) == FALSE) {
+      n <- V(x)$name
+      tc <- nc
+      vs <- 0
+      }
+  p <- ggraph(x, layout = l)
+  p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
+  p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
+  p <- p + geom_node_text(aes(label = n), size = ts, color = tc, fontface = "bold")
+  p <- p + theme_graph() 
+return(p)
+}

### 2025-07-17 Functions/tab.cent.R

@@ -1,0 +1,11 @@
+tab.cent <- function(x, d = 3, name = "name", caption = "", label = "label") { #table function
+library(kableExtra)
+t <- kbl(x, 
+      format = "latex", booktabs = TRUE, linesep = "",
+      digits = d, row.names = FALSE,
+      col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
+      caption = caption, label = label
+      ) %>% 
+      kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
+      save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))
+      }

### 2025-07-17 analysis.qmd
do it# Please enter the commit message for your changes. Lines starting

@@
    c <- lapply(b, distinction)
-   d <- sapply(c, function(x) {x[2, 2]})
+   e <- sapply(c, function(x) {x[nrow(x), 2]})
+
 ```
@@
 ```{r}
-   dat <- data.frame(d = d, n = 1:length(d))
+   d <- sapply(c, function(x) {x[1, 3]})
+   dat <- data.frame(d = d, n = 1:length(d)) |> 
+      mutate(n = n + 1)
    p <- ggplot(dat, aes(n, d, group = 1)) 
@@
    p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
-   p <- p + ylim(-0.1, 1)
+   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
+   #p <- p + ylim(-0.1, 1)
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 12),
+                  axis.title = element_text(size = 14, face = "bold"))
+   p <- p + ggtitle("Scalar Distinction of Star Node")
+   p
+   ggsave(here("Plots", "star-by-nbranches.png"), width = 7, height = 7, units = "in")
+```
+
+```{r}
+   d <- sapply(c, function(x) {x[2, 3]})
+   dat <- data.frame(d = d, n = 1:length(d)) |> 
+      mutate(n = n + 1)
+   p <- ggplot(dat, aes(n, d, group = 1)) 
+   p <- p + geom_point(size = 3, color = "blue")
+   p <- p + geom_line(linewidth = 0.75, color = "blue")
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
+   #p <- p + ylim(-0.1, 1)
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 12),
+                  axis.title = element_text(size = 14, face = "bold"))
+   p <- p + ggtitle("Scalar Distinction of Star Node")
+   p
+   ggsave(here("Plots", "gatekeeper-by-nbranches.png"), width = 7, height = 7, units = "in")
+```
+
+```{r}
+   d <- sapply(c, function(x) {x[nrow(x), 3]})
+   dat <- data.frame(d = d, n = 1:length(d)) |> 
+      mutate(n = n + 1)
+   p <- ggplot(dat, aes(n, d, group = 1)) 
+   p <- p + geom_point(size = 3, color = "blue")
+   p <- p + geom_line(linewidth = 0.75, color = "blue")
+   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
+   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
    p <- p + theme_minimal()
@@
    p
-
+   ggsave(here("Plots", "pendant-by-nbranches.png"), width = 7, height = 7, units = "in")
 ```

### 2025-07-17 analysis.qmd
bom bom

@@
                   axis.title = element_text(size = 14, face = "bold"))
-   p <- p + ggtitle("Scalar Distinction of Star Node")
+   p <- p + ggtitle("Scalar Distinction of Gatekeeper Node")
    p
@@
                   axis.title = element_text(size = 14, face = "bold"))
+   p <- p + ggtitle("Scalar Distinction of Peripheral Node")
    p

### 2025-07-17 analysis.qmd
more stuff

@@
     tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
+```
+
+```{r}
+   source(here("Functions", "distinction.new.R"))
+   distinction.new(g2, norm = TRUE)
 ```
@@
    b <- make.broker.graphs(30)
-   c <- lapply(b, distinction)
-   e <- sapply(c, function(x) {x[nrow(x), 2]})
-
+   c <- lapply(b, distinction.new, norm = FALSE)
 ```
-
-    p <- p + geom_node_point(aes(x = x, y = y), size = 18, color = "tan2")
 
@@
 ```
+
+```{r}
+   d <- sapply(c, function(x) {x[nrow(x), 6]})
+   dat <- data.frame(d = d, n = 1:length(d)) |> 
+      mutate(n = n + 1)
+   p <- ggplot(dat, aes(n, d, group = 1)) 
+   p <- p + geom_point(size = 3, color = "blue")
+   p <- p + geom_line(linewidth = 0.75, color = "blue")
+   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
+   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 12),
+                  axis.title = element_text(size = 14, face = "bold"))
+   p <- p + ggtitle("Scalar Trajectory")
+   p
+   ggsave(here("Plots", "scalar-by-nbranches.png"), width = 7, height = 7, units = "in")
+```

### 2025-07-17 Functions/distinction.new.R

@@ -1,0 +1,63 @@
+distinction.new <- function(x, norm = TRUE) { #distinction centrality function
+   library(igraph)
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   V <- vcount(x)
+   if (has.labels == 0) {
+      V(x)$name <- 1:V
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
+      V(x)$name <- 1:V
+      }
+   s <- eigen_centrality(x)$vector
+  if (norm == FALSE) {
+      s <- abs(eigen(as.matrix(as_adjacency_matrix(x)))$vectors[, 1])
+      names(s) <- V(x)$name
+      }
+   d <- rep(V, 0)
+   u <- rep(V, 0)
+   for (i in as.character(V(x)$name)) {
+      j <- names(neighbors(x, i))
+      x.d <- delete_vertices(x, i)
+      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
+      e <- as.numeric(ecount(x.d) == 0) #checking for empty
+      if (c == 1 & e == 0) { #connected non-empty graph
+         s.a <- eigen_centrality(x.d)$vector[j]
+         if (norm == FALSE) {
+            s.a <- abs(eigen(as.matrix(as_adjacency_matrix(x.d)))$vectors[, 1])
+            } #end sub if
+         } #end main if
+      else if (c == 0 & e == 1) { #empty graph
+         s.a <- 0
+         } #end first else 
+      else if (c == 0 & e == 0) { #disconnected non-empty graph
+         C <- components(x.d)$membership
+         names(C) <- V(x)$name[-as.numeric(i)]
+         s.a <- rep(0, length(C))
+         for (k in unique(C)) {
+            sub.g <- subgraph(x.d, names(which(C == k)))
+            if (vcount(sub.g) > 1) {
+               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
+               if (norm == FALSE) {
+                  s.a[which(C == k)] <- abs(eigen(as.matrix(as_adjacency_matrix(sub.g)))$vectors[, 1])
+                  } #end sub if
+               } #end main if
+            }
+         names(s.a) <- names(C)
+         s.a <- s.a[j]
+         } #end second else
[…]

### 2025-07-18 analysis.qmd
new plot who dis

@@
 ```{r}
+   d.s <- sapply(c, function(x) {x[1, 3]})
+   d.b <- sapply(c, function(x) {x[2, 3]})
+   dat <- data.frame(d = c(d.s, d.b), 
+         n = c(1:length(d.s)+1, 1:length(d.s)+1),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s))))
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
+   #p <- p + ylim(-0.1, 1)
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 12),
+                  axis.title = element_text(size = 14, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "none"
+                  )
+   p <- p + ggtitle("Scalar Distinction of Star versus Gatekeeper Node")
+   p
+   ggsave(here("Plots", "star-v-gate-by-nbranches.png"), width = 7, height = 7, units = "in")
+```
+
+```{r}
    d <- sapply(c, function(x) {x[1, 3]})
@@
    p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
-   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + labs(y = "", x = "Number of Branches")
    p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
@@
    p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
-   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
+   p <- p + labs(y = "", x = "Number of Branches")
    p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))

### 2025-07-18 Functions/distinction.new.R

@@ -35,7 +35,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
          C <- components(x.d)$membership
          names(C) <- V(x)$name[-as.numeric(i)]
          s.a <- rep(0, length(C))
-         for (k in unique(C)) {
+         for 2(k in unique(C)) {
             sub.g <- subgraph(x.d, names(which(C == k)))
             if (vcount(sub.g) > 1) {
                s.a[which(C == k)] <- eigen_centrality(sub.g)$vector

### 2025-07-18 analysis.qmd
new updated

@@
    source(here("Functions", "distinction.R"))
+   source(here("Functions", "distinction.new.R"))
+   source(here("Functions", "make.broker.trees.R"))
    source(here("Functions", "plot.graph.norm.R"))
@@
 ```{r}
-   make.broker.graphs <- function(n = 10) {
-      g <- make_empty_graph(9, directed = FALSE)
-      g <- g + edge(1,2)
-      g <- g + edge(1,3)
-      g <- g + edge(2,4)
-      g <- g + edge(2,5)
-      g <- g + edge(2,6)
-      g <- g + edge(3,7)
-      g <- g + edge(3,8)
-      g <- g + edge(3,9)
-      el <- vector(mode = "list", length = n)
-      el[[1]] <- g
-      a <- 10
-      b <- 11
-      c <- 12
-      d <- 13
-      for (i in 2:n) {
-         g <- add_vertices(g, 4)
-         g <- g + edge(1,a)
-         g <- g + edge(a,b)
-         g <- g + edge(a,c)
-         g <- g + edge(a,d)
-         el[[i]] <- g
-         a <- a + 4
-         b <- b + 4
-         c <- c + 4
-         d <- d + 4
-      }
-   return(el)
-   }
+
    b <- make.broker.graphs(30)
@@
    d.b <- sapply(c, function(x) {x[2, 3]})
-   dat <- data.frame(d = c(d.s, d.b), 
-         n = c(1:length(d.s)+1, 1:length(d.s)+1),
-         g = c(rep(1, length(d.s)), rep(2, length(d.s))))
+   d.p <- sapply(c, function(x) {x[nrow(x), 3]})
+   dat <- data.frame(d = c(d.s, d.b, d.p), 
+         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s))))
    p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 

### 2025-07-18 Functions/distinction.new.R

@@ -35,7 +35,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
          C <- components(x.d)$membership
          names(C) <- V(x)$name[-as.numeric(i)]
          s.a <- rep(0, length(C))
-         for 2(k in unique(C)) {
+         for (k in unique(C)) {
             sub.g <- subgraph(x.d, names(which(C == k)))
             if (vcount(sub.g) > 1) {
                s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
@@ -49,12 +49,11 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
          } #end second else
       u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
       d[i] <- s[i] - u[i] #i's distinction centrality
-          } #end i for loop
+      } #end i for loop
    d[is.na(d)] <- 0
    u[is.na(u)] <- 0
    scalar <- mean(u)/mean(s)
    sd <- (s*scalar) - u
-   source("diss.status.R")
    dat <- data.frame(d = d, sd = sd, s = s, u = u, scalar = scalar)
    dat <- round(dat, 4)
    dat <- data.frame(n = names, dat)

### 2025-07-18 Functions/make.broker.trees.R

@@ -1,0 +1,30 @@
+   make.broker.trees <- function(n = 10) {
+      g <- make_empty_graph(9, directed = FALSE)
+      g <- g + edge(1,2)
+      g <- g + edge(1,3)
+      g <- g + edge(2,4)
+      g <- g + edge(2,5)
+      g <- g + edge(2,6)
+      g <- g + edge(3,7)
+      g <- g + edge(3,8)
+      g <- g + edge(3,9)
+      el <- vector(mode = "list", length = n)
+      el[[1]] <- g
+      a <- 10
+      b <- 11
+      c <- 12
+      d <- 13
+      for (i in 2:n) {
+         g <- add_vertices(g, 4)
+         g <- g + edge(1,a)
+         g <- g + edge(a,b)
+         g <- g + edge(a,c)
+         g <- g + edge(a,d)
+         el[[i]] <- g
+         a <- a + 4
+         b <- b + 4
+         c <- c + 4
+         d <- d + 4
+      }
+   return(el)
+   }

### 2025-07-18 analysis.qmd
do it

@@
 
+## Toy Networks
+
 ```{r Toy Examples}
@@
     g4 <- g3 + edge(2,7) # inter-connected clusters
-    tab.cent(distinction(g1), name = "star", label = "tab:star")
-    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
-    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
-    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
-```
-
-```{r}
-   source(here("Functions", "distinction.new.R"))
-   distinction.new(g2, norm = TRUE)
+    g5 <- make_ring(7) #circle graph
 ```
@@
    dev.off()
+   png(here("Plots", "circle.png"))
+   plot.graph.norm(g5)
+   dev.off()
 ```
 
-```{r Medici Distinction Plots}
+```{r Toy Network Distinction Tables}
+    tab.cent(distinction(g1), name = "star", label = "tab:star")
+    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
+    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
+    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
+    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
+```
+
+## Medici
+
+```{r Loading Medici Data}
    medici1 <- as.matrix(read.csv(here("Data", "MediciEdgeList.csv")))
@@
    nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
+```
+
+```{r Medici Distintion Plots}
    png(here("Plots", "medici.png"), height = 600, width = 1000)
@@
    dev.off()
+```
 
-```
+## Search
 
@@
 
+## Broker Computatinal Experiements
+
 ```{r}
-
-   b <- make.broker.graphs(30)
+   b <- make.broker.trees(30)
    c <- lapply(b, distinction.new, norm = FALSE)
@@
    library(patchwork)
-   library(ggplotify)
    library(ggraph)
-   gg <- function(x) {
+   gg <- function(x, lay.o = "kk") {
       n <- vcount(x)
       V(x)$name <- 1:n
-      w <- ggraph(x, layout = "kk") + 
+      w <- ggraph(x, layout = lay.o) + 
       geom_edge_link(color = "steelblue") + theme_graph() +
-      geom_node_point(size = 5, color = c("blue", rep("tan2", n - 1))) + 
+      geom_node_point(size = 5, color = c("blue", rep("tan2", n-1))) + 
       geom_node_text(aes(label = name), color = "white", size = 3) +
@@
          g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
-         rep(3, length(d.s))))
+         rep(3, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c("Star", "Gatekeeper", "Peripheral")))
    p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
@@
    p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
-   #p <- p + ylim(-0.1, 1)
+   p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
    p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 12),
-                  axis.title = element_text(size = 14, face = "bold"),
+   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 16, face = "bold"),
                   legend.title = element_blank(),
-                  legend.position = "none"
+                  legend.position = "top"
                   )
-   p <- p + ggtitle("Scalar Distinction of Star versus Gatekeeper Node")
    p
-   ggsave(here("Plots", "star-v-gate-by-nbranches.png"), width = 7, height = 7, units = "in")
+   ggsave(here("Plots", "broker-tree-roles-by-nbranches.png"), width = 7, height = 7, units = "in")
 ```
@@
 ```{r}
-   d <- sapply(c, function(x) {x[1, 3]})
-   dat <- data.frame(d = d, n = 1:length(d)) |> 
-      mutate(n = n + 1)
-   p <- ggplot(dat, aes(n, d, group = 1)) 
-   p <- p + geom_point(size = 3, color = "blue")
-   p <- p + geom_line(linewidth = 0.75, color = "blue")
-   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
-   p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
-   #p <- p + ylim(-0.1, 1)
-   p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 12),
-                  axis.title = element_text(size = 14, face = "bold"))
-   p <- p + ggtitle("Scalar Distinction of Star Node")
-   p
-   ggsave(here("Plots", "star-by-nbranches.png"), width = 7, height = 7, units = "in")
+   make.broker.cliques <- function(n = 10) {
+      g1 <- make_full_graph(4, directed = FALSE)
+      g2 <- make_full_graph(4, directed = FALSE)
+      g3 <- g1 + g2
+      g3 <- add_vertices(g3, 1)
+      g3 <- g3 + edge(9,4)
+      g3 <- g3 + edge(9,5)
+      el <- vector(mode = "list", length = n)
+      el[[1]] <- g3
+      a <- 10
+      for (i in 2:n) {
+         g3 <- g3 + make_full_graph(4, directed = FALSE)
+         g3 <- g3 + edge(9,a)
+         el[[i]] <- g3
+         a <- a + 4
+         }
+   return(el)
+   }
+   b <- make.broker.cliques(30)
+   c <- lapply(b, distinction.new, norm = FALSE)
 ```
@@
 ```{r}
-   d <- sapply(c, function(x) {x[2, 3]})
-   dat <- data.frame(d = d, n = 1:length(d)) |> 
-      mutate(n = n + 1)
-   p <- ggplot(dat, aes(n, d, group = 1)) 
-   p <- p + geom_point(size = 3, color = "blue")
-   p <- p + geom_line(linewidth = 0.75, color = "blue")
-   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
-   p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
-   #p <- p + ylim(-0.1, 1)
-   p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 12),
-                  axis.title = element_text(size = 14, face = "bold"))
-   p <- p + ggtitle("Scalar Distinction of Gatekeeper Node")
-   p
-   ggsave(here("Plots", "gatekeeper-by-nbranches.png"), width = 7, height = 7, units = "in")
+   gg2 <- function(x, lay.o = "kk") {
+      n <- vcount(x)
+      V(x)$name <- 1:n
+      c <- c(rep("tan2", n))
+      c[9] <- "blue"
+      w <- ggraph(x, layout = lay.o) + 
+      geom_edge_link(color = "steelblue") + theme_graph() +
+      geom_node_point(size = 5, color = c) + 
+      geom_node_text(aes(label = name), color = "white", size = 3) +
+      ylim(-4,4) + xlim(-4,4) 
+      return(w)
+      }
+   p.list <- lapply(b, gg2)
+   for (i in 1:length(p.list)) {
+      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
+         theme(plot.title = element_text(size = 11))
+      }
+   wrap_plots(p.list[c(1:6)], nrow = 2)
+   ggsave(here("Plots", "clique-examples.png"), width = 10, height = 7, units = "in")
 ```
@@
 ```{r}
-   d <- sapply(c, function(x) {x[nrow(x), 3]})
-   dat <- data.frame(d = d, n = 1:length(d)) |> 
-      mutate(n = n + 1)
-   p <- ggplot(dat, aes(n, d, group = 1)) 
-   p <- p + geom_point(size = 3, color = "blue")
-   p <- p + geom_line(linewidth = 0.75, color = "blue")
-   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
+   d.s <- sapply(c, function(x) {x[9, 3]})
+   d.b <- sapply(c, function(x) {x[4, 3]})
+   d.p <- sapply(c, function(x) {x[1, 3]})
+   dat <- data.frame(d = c(d.s, d.b, d.p), 
+         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c("Star", "Gatekeeper", "Peripheral")))
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
    p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
+   p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
    p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 12),
-                  axis.title = element_text(size = 14, face = "bold"))
-   p <- p + ggtitle("Scalar Distinction of Peripheral Node")
+   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 16, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "top"
+                  )
    p
-   ggsave(here("Plots", "pendant-by-nbranches.png"), width = 7, height = 7, units = "in")
+   ggsave(here("Plots", "broker-cliques-roles-by-nbranches.png"), width = 7, height = 7, units = "in")
 ```
@@
 ```{r}
-   d <- sapply(c, function(x) {x[nrow(x), 6]})
-   dat <- data.frame(d = d, n = 1:length(d)) |> 
-      mutate(n = n + 1)
-   p <- ggplot(dat, aes(n, d, group = 1)) 
-   p <- p + geom_point(size = 3, color = "blue")
-   p <- p + geom_line(linewidth = 0.75, color = "blue")
-   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
-   p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
-   p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 12),
-                  axis.title = element_text(size = 14, face = "bold"))
-   p <- p + ggtitle("Scalar Trajectory")
-   p
-   ggsave(here("Plots", "scalar-by-nbranches.png"), width = 7, height = 7, units = "in")
+   g <- make_ring(10)
 ```

### 2025-07-18 manuscript.tex
Updates from Overleaf

@@
 \usepackage{subcaption}
+\usepackage{listings}
+\usepackage{courier}
+\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
+\lstset{framextopmargin=50pt,frame=bottomline}
 \usepackage[hidelinks]{hyperref}
@@
 In this last respect, the more encompassing notion of \textit{social} distinction, implying an actor's embeddedness in a relational field \citep{erikson2013formalist-400, fuhse2021social-9cb}, is often measured as the shadow counterpart of cultural distinction or collapsed into the concept of status more generally \citep{podolny2010status-1a6}.
-This approach overlooks questions of how network constraints impact the capacity of actors to be distinct.
+This approach overlooks questions of how network constraints produced by other agents impact the capacity of actors to be distinct.
 A generalized, measured ordering of social distinction that is derivative from a network of concrete social relations would give Bourdieu's generalized conception of distinction a broader methodological base from which to conduct empirical analysis.
@@
 
-The second aspect of social distinction is \textit{autonomy}, which is the absence of network constraint.
+The second aspect of social distinction is \textit{autonomy}, which is the absence of network constraint \citep{burt1980autonomy}.
 Being structurally unique minimizes the social constraints placed on an individual.
@@
 The question of structural uniqueness and autonomy is the same underlying consideration as captured by measures of path centrality.
-The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt92}.
-\citet[1263-4]{padgett_ansell94} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions.
+The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt1995structural-5e8}.
+
+\citet[1263-4]{padgett1993robust} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions.
 Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because strong actions favoring one side would upset the other side.
@@
 \section{A Generalized Measure of Network Distinction}
-Below, we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and indicate the availability of an R program to facilitate easy implementation of the measure in further wok.
+Below, we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and indicate the availability of an R program to facilitate easy implementation of the measure in further work.
 
@@
 The first term captures the status of a given actor.
-Let \textit{x} be the eigenvector centrality \citep{bonacich72} of the designated individual.
+Let \textit{x} be the eigenvector centrality of the designated individual.
 Let S be a scalar that adjusts the social value placed on status relative to constraint, as discussed below.
-The second terms captures the element of autonomy.
+The second term captures the element of autonomy.
 Removing individual \textit{i} from the network, compute the eigenvectors of the remaining individuals and sum those that are connected to individual \textit{i}, taking the average eigenvector of neighbors \textit{j} as the constraint confronting node \textit{i} in the network.
-This is substantively the same mechanism as conducted in a jackknife resampling procedure, except that rather than forming a sampling distribution, we are measuring local constraint.
-Finally, subtract the status of the average neighbor connected to \textit{i} from \textit{i}’s scalar adjusted eigenvector centrality in the whole network.
+This is substantively the same mechanism as conducted in a jackknife resampling procedure, except that rather than forming a sampling distribution, we are measuring local constraints.
+Finally, subtract the status of the average neighbor connected to \textit{i} from \textit{i}’s scalar-adjusted eigenvector centrality in the whole network.
 
-If a node is an isolate, its eigenvector centrality should be set at 0.
-In the case of a network with no connections (such as a star graph), it can be accidentally calculated as 1.00 in programs.
-However, given that it is still a network with no connections, setting isolates at 0.00 is theoretically appropriate, considering that status is a reflection of connections.
-It would be inappropriate for an isolate to have the same status as the highest status node in a large network.
-Additionally, given the second step of subtraction, it is only theoretically meaningful if set as 0 in the case of distinction centrality.
+When a node is an isolate, we set its eigenvector centrality to $x_i =0$.
+In the case of a network with no connections (such as an empty graph), some routines calculate it as $x_i =1.0$.
+However, given that it is still a network with no connections, setting isolates at $x_i =0$ is theoretically appropriate, considering that status is a reflection of connections.
+It would be inappropriate for an isolate to have the same status as the highest-status node in a large network.
+Additionally, given the second step of subtraction, it is only theoretically meaningful if set as $x_i =0$ in the case of distinction centrality.
 
@@
 Status with a weak constraint means a weaker compulsion of deference.
-The structure of constraint redounds into the impact of status on social distinction beyond its contribution.
+The structure of constraint has a reverberative impact on social distinction beyond its contribution.
 
@@
 
-\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
-Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
-Compared to the structural fold, connections 3-2 and 6-7 have been removed.
-Measurement results are in Table 3.
-Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
-The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
-
-\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
-This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
-The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
-In fact, all nodes except 3 and 6 have higher distinction in such a case.
-This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
-
-\subsection{Implementation}
-To conduct the analyses below, we use a custom function written for the \textit{R} statistical computing environment \citep{R} software.\footnote{The function can be found here \href{https://github.com/olizardo/Jilbert-Distinction-Centrality/blob/main/distinction.R}{https://github.com/olizardo/Jilbert-Distinction-Centrality/blob/main/distinction.R}}
-
 \begin{figure}
@@
 \input{Tabs/interclust}
+
+\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
+Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
+Compared to the structural fold, connections 3-2 and 6-7 have been removed.
+Measurement results are in Table 3.
+Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
+The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
+
+\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
+This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+In fact, all nodes except 3 and 6 have higher distinction in such a case.
+This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
+increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
+
+\subsection{Distinction with Structural Holes vs. Structural Folds}
+
+%Clique addition experiment
+
+%Add cliques to star graph and see what happens
+
+%See what happens with the caveman
+
+%Placehold graphs
+%\begin{figure}
+%   \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+%    \centering
+%     \begin{subfigure}[b]{0.45\textwidth}
+%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
+%            \caption{Star Graph}
+%            \label{fig:Placehold}
+%    \end{subfigure}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
+%            \caption{Structural Fold}
+%            \label{fig:Placehold}
+%    \end{subfigure}
+%    \caption{Structural Holes with more added subgraphs.}
+%    \label{fig:toys}
+%\end{figure}
+
+\subsection{Long Ties and Hierarchy}
+This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs.
+While a star graph clearly creates a hierarchy, when additional weight is added to the broker's alters, the hierarchy can be flipped, especially when they form denser subgraphs.
+This is in keeping with the observed structural holes above.
+
+Graph (b) is the same as graph (a),but with Nodes 12, 13, and 14 combined into a clique with Node 9.
+Graph (c) is the same as graph (b) with the addition of Nodes 21, 22, and 23 as personal connections of Nodes 12, 13, and 14.
+Finally, graph (d) is the same as graph (c) with the addition of three long ties across subgraphs connecting only Nodes 17 with 23 and 11 with 18.
+
+As Figure 5 graph (d) demonstrates, when those subgroups become connected redundantly not through the central figure, but through the sparse interconnection of the other members, then Node 9's position of distinction becomes highly elevated.
+
+Thus, there is a U shaped pattern where at low levels of interconnection between sparse subgroups, mediated by a central node, the distinction level of the broker is high.
+However, as those subgraphs become more densely connected within themselves, the position of the central node is weakened as status accrues more heavily in those local subgraphs.
+However, when sparse long connections then form to connect the subgraphs, Node 9 achieves a high level of distinction again because the overall constraint in the network increases with the added ties between the subgraphs.
+The resulting decrease in the scalar works to stratify the distinction distance between Node 9 and other high status competitors, while simultaneously decreasing the constraint forced upon Node 9
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/political1.png}
+            \caption{High Subgraph Density, Low Graph Density}
+            \label{fig:Placehold}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/political2.png}
+            \caption{Broker Given Independent Foundations}
+            \label{fig:Placehold}
+    \end{subfigure}
+         \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/political3.png}
+            \caption{Increased Independent Foundations}
+            \label{fig:Placehold}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/political4.png}
+            \caption{All Subgraphs Connected by Long Ties}
+            \label{fig:Placehold}
+    \end{subfigure}
+    \caption{Increasingly connected graphs with central broker.}
+    \label{fig:Evolving Political Network}
+\end{figure}
+
+\input{Tabs/political.tex}
+
+\subsection{Implementation}
+To conduct the analyses below, we use a custom function written for the \textit{R} statistical computing environment \citep{R} software.
+The function code is reproduced in the \hyperref[sec:appendix]{the Appendix}.
 
@@
 The paper was an early application of an algorithm to predict the lines along which the group would divide.
-The original Ford-Fulkerson Labeling algorithm was a network flow model which sought to use the length between nodes to detect community membership (1977:454).
-However, in the algorithm, Node 9 was mis-assigned to the Officer’s network using the original algorithm, whereas empirically Node 9 joined the network of the karate teacher, Mr.
+The original Ford-Fulkerson Labeling algorithm was a network flow model that sought to use the length between nodes to detect community membership (1977:454).
+However, in the original algorithm, Node 9 was misclassified to the Officer’s network, whereas empirically Node 9 joined the network of the karate teacher, Mr.
 Hi.
@@
 If Node 9 was similarly affiliating with advanced students who only attended the dojo, then this would likely influence the decision regarding distinction at the field level.
-Failure to completely capture the positions in the appropriately defined field can create measures that fail to capture empirical outcomes.
+Failure to completely capture the positions in the appropriately defined field can result in measures that fail to accurately capture empirical outcomes.
 
@@
 
-\section{Distinction with Structural Holes vs. Structural Folds}
+Given the value that eigenvector-style centrality measures have had in underpinning the logic of internet search algorithms \citep{kleinberg99, brin_page98, langville2005survey-572}, the application of distinction centrality in the case of a reference network is briefly considered.
+As the social logic of distinction centrality involves jointly considering the interaction of status and constraint, so in a reference network, the distinction measure will give greater priority to the uniqueness of a node's flow of affiliations.
+
+A toy reference network is presented in Figure 3.
+The network was designed to contrast status versus distinction within a graph, featuring a clear cluster of nodes with an elevated level of density and tenuously connected to a node with a high degree of popularity external to the main, denser cluster.
+Such a graph is supposed to represent a contrast between an orthodox set of mutual endorsements and the emergence of a heterodox set of connections.
+
+The resulting distinction measures are presented in Table 6.
+The results are ranked in order of highest to lowest scaled distinction centrality.
+Node 8 measures highest in both scaled distinction and status, but immediately after Node 9 and Node 6 switch places in their ordering.
+Node 6 has the second highest status, but the third highest scaled distinction, while Node 9 goes from third in status to second in scaled distinction.
+The measure rewards the independent connections Node 9 has with Nodes 13 and 14 over the heavier constraints imposed on Node 6.
+\footnote{In the absence of Node 8's and its constraint effect on Node 6, Node 6 would become the most distinct and highest status.} Node 10's relative position in the social hierarchy is consistent at fourth in both the status and scaled distinction measures.
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/search.png}
+            \caption{Reference Network Example}
+            \label{fig:search}
+    \end{subfigure}
+    \caption{Example of a non-directed network of references, e.g. citation network, internet links, etc.}
+    \label{fig:search}
+\end{figure}
+
+\input{Tabs/search}
+
+The heterodoxy of Node 5 is elevated into the fifth position of the scaled distinction hierarchy compared to the sixth position it has in the status hierarchy.
+Node 7 correspondingly falls into the sixth position of the scaled distinction hierarchy from the fifth position in terms of status.
+However, scaled distinction centrality also elevates Nodes 1, 2, 3, and 4 which buttress 5's popularity.
+These nodes have the lowest status, yet leap over the hanger's on to the core members of the main orthodox cluster.
+They are greatly penalized for their high level of constraint, whereas Node's 1, 2, 3, and 4 are empowered by 5's own lower status position.
+If the goal is to elevate uniqueness, this makes sense as Nodes 11 through 16 are likely to conform to their higher status, and high distinction, connections.
+Nodes 7, 8, 9, and 10 already implicitly represent their contributions.
+Additionally, the application of the scalar is important in the final results.
+Without the scalar, Node 5 would actually be the third ranked node in terms of distinction, leaping Node 6.
+Such a result may be desirable in technical applications where uniqueness should be privileged over social hierarchy.
+On the whole, the scaled distinction centrality measure thus works to elevate the uniqueness of a node in search applications.
 
@@
 While the above exploration of how network shape changes diversity in cultural distinction practices is at least informative about how understanding the network of positions structures the cultural markers of distinction.
+
+%College as inherently distinction based institution makes liberals a thing, rather than if you only draw from caves
 
@@
 
+\newpage
+\section*{Appendix: Distinction
+Centrality Function} \label{sec:appendix}
+\begin{lstlisting}[language=R]
+distinction <- function(x) { 
+   library(igraph) #calling igraph
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE) #checking for vertex labels
+   V <- vcount(x)
+   if (has.labels == 0) {
+      V(x)$name <- 1:V
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
+      V(x)$name <- 1:V
+      }
+   s <- eigen_centrality(x)$vector
+   d <- rep(V, 0) #initializing distinction vector
+   u <- rep(V, 0) #initializing constraint vector
+   for (i in as.character(V(x)$name)) {
+      j <- names(neighbors(x, i))
+      x.d <- delete_vertices(x, i)
+      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
+      e <- as.numeric(ecount(x.d) == 0) #checking for empty
+      if (c == 1 & e == 0) { #connected non-empty graph
+         s.a <- eigen_centrality(x.d)$vector[j]
+         } #end if
+      else if (c == 0 & e == 1) { #empty graph
+         s.a <- 0
+         } #end first else 
+      else if (c == 0 & e == 0) { #disconnected non-empty graph
+         C <- components(x.d)$membership
+         names(C) <- V(x)$name[-as.numeric(i)]
+         s.a <- rep(0, length(C))
+         for (k in unique(C)) {
+            sub.g <- subgraph(x.d, names(which(C == k)))
+            if (vcount(sub.g) > 1) {
+               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
+               }
+            }
+         names(s.a) <- names(C)
+         s.a <- s.a[j]
+         } #end second else
+      u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
+      d[i] <- s[i] - u[i] #i's distinction centrality
+   } #end i for loop
+   d[is.na(d)] <- 0
+   u[is.na(u)] <- 0
+   scalar <- mean(u)/mean(s)
+   sd <- (s*scalar) - u
+   dat <- data.frame(d = d, sd = sd, s = s, u = u, scalar = scalar)
+   dat <- round(dat, 4)
+   dat <- data.frame(n = names, dat)
+   rownames(dat) <- 1:nrow(dat)
+   return(dat)
+} #end function
+\end{lstlisting}
+
 \end{document}

### 2025-07-18 analysis.qmd
new graphs who dis

@@
    g5 <- make_ring(7) #circle graph
+   g6 <- add_vertices(g5, 1)
+   g6 <- g6 + edge(8,1) #circle graph wit pendant
 ```
@@
    png(here("Plots", "circle.png"))
-   plot.graph.norm(g5)
+   plot.graph.norm(g5, l = "circle")
+   dev.off()
+   png(here("Plots", "circle-plus-one.png"))
+   plot.graph.norm(g6, l = "circle")
    dev.off()
@@
     tab.cent(distinction(g5), name = "circle", label = "tab:circle")
+    tab.cent(distinction(g6), name = "circleplus", label = "tab:circleplus")
+
 ```
@@
    library(ggraph)
-   gg <- function(x, lay.o = "kk") {
+   gg <- function(x, lay.o = "kk", star = 1) {
       n <- vcount(x)
       V(x)$name <- 1:n
+      c <- c(rep("tan2", n))
+      c[star] <- "blue"
+      gk <- which(degree(x) == 4)
+      gk <- gk[gk != star]
+      c[gk] <- "red"
       w <- ggraph(x, layout = lay.o) + 
       geom_edge_link(color = "steelblue") + theme_graph() +
-      geom_node_point(size = 5, color = c("blue", rep("tan2", n-1))) + 
+      geom_node_point(size = 5, color = c) + 
       geom_node_text(aes(label = name), color = "white", size = 3) +
-      ylim(-4,4) + xlim(-4,4) 
+      ylim(-4, 3.5) + xlim(-4, 3.25) 
       return(w)
@@
    wrap_plots(p.list[c(1:6)], nrow = 2)
-   ggsave(here("Plots", "tree-examples.png"), width = 10, height = 7, units = "in")
+   ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
 ```
@@
    p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
+   p <- p + scale_color_manual(values = c("red", "blue", "tan2"))
    p <- p + theme_minimal()
@@
    b <- make.broker.cliques(30)
+   b.r <- lapply(b, function(x) {rewire(x, each_edge(p = .05, loops = FALSE, multiple = FALSE))})
    c <- lapply(b, distinction.new, norm = FALSE)
@@
 ```{r}
-   gg2 <- function(x, lay.o = "kk") {
-      n <- vcount(x)
-      V(x)$name <- 1:n
-      c <- c(rep("tan2", n))
-      c[9] <- "blue"
-      w <- ggraph(x, layout = lay.o) + 
-      geom_edge_link(color = "steelblue") + theme_graph() +
-      geom_node_point(size = 5, color = c) + 
-      geom_node_text(aes(label = name), color = "white", size = 3) +
-      ylim(-4,4) + xlim(-4,4) 
-      return(w)
-      }
-   p.list <- lapply(b, gg2)
+   p.list <- lapply(b, gg, star = 9)
    for (i in 1:length(p.list)) {
@@
    wrap_plots(p.list[c(1:6)], nrow = 2)
-   ggsave(here("Plots", "clique-examples.png"), width = 10, height = 7, units = "in")
+   ggsave(here("Plots", "clique-examples.png"), width = 12, height = 8, units = "in")
 ```
@@
 ```{r}
-   g <- make_ring(10)
+
 ```

### 2025-07-18 Functions/plot.graph.norm.R

@@ -1,10 +1,12 @@
 plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
   library(ggraph)
-  d <- distinction(x)[,3]
+  d <- distinction(x)[, 3]
   nc <- rep("", length(d))
-  nc[which(d < -0.05)] <- "red"
+  nc[which(d < -0.05)] <- "tan2"
   nc[which(d > 0.05)] <- "blue"
   nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
+  nc[which(d == max(d))] <- "red"
+
   if (is.null(V(x)$name) == TRUE) {
       n <- 1:vcount(x)
       tc <- "white"

### 2025-07-18 analysis.qmd
new lays

@@
    png(here("Plots", "star.png"))
-   plot.graph.norm(g1)
+   plot.graph.norm(g1, l = "auto")
    dev.off()
    png(here("Plots", "sf.png"))
-   plot.graph.norm(g2)
+   plot.graph.norm(g2, l = "auto")
    dev.off()
    png(here("Plots", "intra.png"))
-   plot.graph.norm(g3)
+   plot.graph.norm(g3, l = "auto")
    dev.off()
    png(here("Plots", "inter.png"))
-   plot.graph.norm(g4)
+   plot.graph.norm(g4, l = "auto")
    dev.off()

### 2025-07-18 analysis.qmd
kite

--- 2025-07-18 analysis.qmd
@@
    g6 <- g6 + edge(8,1) #circle graph wit pendant
+   g7 <- make_full_graph(4, directed = FALSE)
+   g7 <- add_vertices(g7, 1)
+   g7 <- g7 + edge(1,5)
+   plot(g7)
 ```
@@
    png(here("Plots", "star.png"))
-   plot.graph.norm(g1)
+   plot.graph.norm(g1, l = "kk")
    dev.off()
    png(here("Plots", "sf.png"))
-   plot.graph.norm(g2)
+   plot.graph.norm(g2, l = "kk")
    dev.off()
    png(here("Plots", "intra.png"))
-   plot.graph.norm(g3)
+   plot.graph.norm(g3, l = "auto")
    dev.off()
    png(here("Plots", "inter.png"))
-   plot.graph.norm(g4)
+   plot.graph.norm(g4, l = "auto")
    dev.off()
@@
    plot.graph.norm(g6, l = "circle")
+   dev.off()
+   png(here("Plots", "kite.png"))
+   plot.graph.norm(g7, l = "kk")
    dev.off()
@@
     tab.cent(distinction(g6), name = "circleplus", label = "tab:circleplus")
-
+    tab.cent(distinction(g6), name = "kite", label = "tab:kite")
 ```

### 2025-07-18 manuscript.tex
Updates from Overleaf

@@
     \centering
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/star.png}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/sf.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/intra.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/inter.png}
@@
     \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/circle.png}
+            \caption{Circle Graph}
+            \label{fig:inter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-one.png}
+            \caption{Circle Graph with Pendant Node}
+            \label{fig:inter}
+    \end{subfigure}
     \caption{Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in blue, nodes with the lowest distinction are shown in red, and nodes with distinction scores close to zero are shown in purple.}
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
     \label{fig:toys}
@@
 \input{Tabs/interclust}
+\input{Tabs/circle}
 

### 2025-07-18 Functions/plot.graph.norm.R
big node

@@ -1,4 +1,4 @@
-plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
+plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   library(ggraph)
   d <- distinction(x)[, 3]
   nc <- rep("", length(d))

### 2025-07-18 analysis.qmd
clique

@@
    g6 <- add_vertices(g5, 1)
-   g6 <- g6 + edge(8,1) #circle graph wit pendant
-   g7 <- make_full_graph(4, directed = FALSE)
+   g6 <- g6 + edge(8,1) # circle graph plus pendant
+   g7 <- make_full_graph(6, directed = FALSE)
    g7 <- add_vertices(g7, 1)
-   g7 <- g7 + edge(1,5)
-   plot(g7)
+   g7 <- g7 + edge(1,7) # clique plus pendant
+   g8 <- make_full_graph(7, directed = FALSE) # clique
 ```
@@
    plot.graph.norm(g7, l = "kk")
+   dev.off()
+   png(here("Plots", "clique.png"))
+   plot.graph.norm(g8, l = "circle")
    dev.off()

### 2025-07-19 analysis.qmd
caveman

@@
    library(ggpubr)
+   library(patchwork)
    source(here("Functions", "distinction.R"))
@@
    source(here("Functions", "make.broker.trees.R"))
+   source(here("Functions", "make.broker.cliques.R"))
    source(here("Functions", "plot.graph.norm.R"))
@@
 
-## Broker Computatinal Experiements
+## Connected Caves Computational Experiments
+```{r}
+   source(here("Functions", "connect.caves.R"))
+   set.seed(12345)
+   b <- connect.caves(c = 4, nc = 4, n = 20)
+   c <- lapply(b, distinction.new, norm = FALSE)
+   gg2 <- function(x, lay.o = "kk") {
+      n <- vcount(x)
+      V(x)$name <- 1:n
+      c <- c(rep("tan2", n))
+      w <- ggraph(x, layout = lay.o) + 
+      geom_edge_link(color = "steelblue") + theme_graph() +
+      geom_node_point(size = 5, color = c) + 
+      geom_node_text(aes(label = name), color = "white", size = 3) 
+      #ylim(-4, 3.5) + xlim(-4, 3.25) 
+      return(w)
+      }
+   p.list <- lapply(b, gg2, lay.o = "auto")
+   for (i in 1:length(p.list)) {
+      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
+         theme(plot.title = element_text(size = 11))
+      }
+   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
+   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
+```
+
+## Broker Computational Experiements
 
@@
    library(ggraph)
-   gg <- function(x, lay.o = "kk", star = 1) {
-      n <- vcount(x)
-      V(x)$name <- 1:n
-      c <- c(rep("tan2", n))
-      c[star] <- "blue"
-      gk <- which(degree(x) == 4)
-      gk <- gk[gk != star]
-      c[gk] <- "red"
-      w <- ggraph(x, layout = lay.o) + 
-      geom_edge_link(color = "steelblue") + theme_graph() +
-      geom_node_point(size = 5, color = c) + 
-      geom_node_text(aes(label = name), color = "white", size = 3) +
-      ylim(-4, 3.5) + xlim(-4, 3.25) 
-      return(w)
-      }
    p.list <- lapply(b, gg)
@@
    ggsave(here("Plots", "broker-tree-roles-by-nbranches.png"), width = 7, height = 7, units = "in")
-```
-
-```{r}
-   make.broker.cliques <- function(n = 10) {
-      g1 <- make_full_graph(4, directed = FALSE)
-      g2 <- make_full_graph(4, directed = FALSE)
-      g3 <- g1 + g2
-      g3 <- add_vertices(g3, 1)
-      g3 <- g3 + edge(9,4)
-      g3 <- g3 + edge(9,5)
-      el <- vector(mode = "list", length = n)
-      el[[1]] <- g3
-      a <- 10
-      for (i in 2:n) {
-         g3 <- g3 + make_full_graph(4, directed = FALSE)
-         g3 <- g3 + edge(9,a)
-         el[[i]] <- g3
-         a <- a + 4
-         }
-   return(el)
-   }
-   b <- make.broker.cliques(30)
-   b.r <- lapply(b, function(x) {rewire(x, each_edge(p = .05, loops = FALSE, multiple = FALSE))})
-   c <- lapply(b, distinction.new, norm = FALSE)
 ```
@@
 ```
-
-```{r}
-
-```

### 2025-07-19 Functions/connect.caves.R

@@ -1,0 +1,31 @@
+connect.caves <- function(c = 4, nc = 4, n = 12) {
+    make.cave.list <- function(c) {
+      caves <- list() 
+      i <- 1
+      for (k in 1:nc) {
+        j <- i + (c - 1)
+        caves[[k]] <- c(i:j)
+        i <- i + c
+      }
+    return(caves)
+    } # end make.cave.list
+    caves <- make.cave.list(c)
+    make.caves <- function(c, nc) {
+      g <- make_full_graph(c, directed = FALSE)
+      for (k in 2:nc) {
+        g <- g + make_full_graph(c, directed = FALSE)
+        }
+      return(g) 
+      } # end make.caves
+    gl <- vector(mode = "list", length = n)
+    g <- make.caves(c, nc)
+    gl[[1]] <- g
+    for (k in 2:n) {
+      ca <- sample(1:c, 2)
+      ca1 <- caves[[ca[1]]]
+      ca2 <- caves[[ca[2]]]
+      g <- add_edges(g, c(sample(ca1, 1), sample(ca2, 1)))
+      gl[[k]] <- g
+      }
+    return(gl)
+}

### 2025-07-19 Functions/gg.R

@@ -1,0 +1,15 @@
+gg <- function(x, lay.o = "kk", star = 1) {
+   n <- vcount(x)
+   V(x)$name <- 1:n
+   c <- c(rep("tan2", n))
+   c[star] <- "blue"
+   gk <- which(degree(x) == 4)
+   gk <- gk[gk != star]
+   c[gk] <- "red"
+   w <- ggraph(x, layout = lay.o) + 
+   geom_edge_link(color = "steelblue") + theme_graph() +
+   geom_node_point(size = 5, color = c) + 
+   geom_node_text(aes(label = name), color = "white", size = 3) +
+   ylim(-4, 3.5) + xlim(-4, 3.25) 
+   return(w)
+   }

### 2025-07-19 Functions/make.broker.cliques.R

@@ -1,0 +1,18 @@
+make.broker.cliques <- function(n = 10) {
+   g1 <- make_full_graph(4, directed = FALSE)
+   g2 <- make_full_graph(4, directed = FALSE)
+   g3 <- g1 + g2
+   g3 <- add_vertices(g3, 1)
+   g3 <- g3 + edge(9,4)
+   g3 <- g3 + edge(9,5)
+   gl <- vector(mode = "list", length = n)
+   gl[[1]] <- g3
+   a <- 10
+   for (i in 2:n) {
+      g3 <- g3 + make_full_graph(4, directed = FALSE)
+      g3 <- g3 + edge(9,a)
+      gl[[i]] <- g3
+      a <- a + 4
+      }
+return(gl)
+}

### 2025-07-19 Functions/make.broker.trees.R

@@ -8,8 +8,8 @@
       g <- g + edge(3,7)
       g <- g + edge(3,8)
       g <- g + edge(3,9)
-      el <- vector(mode = "list", length = n)
-      el[[1]] <- g
+      gl <- vector(mode = "list", length = n)
+      gl[[1]] <- g
       a <- 10
       b <- 11
       c <- 12
@@ -20,11 +20,11 @@
          g <- g + edge(a,b)
          g <- g + edge(a,c)
          g <- g + edge(a,d)
-         el[[i]] <- g
+         gl[[i]] <- g
          a <- a + 4
          b <- b + 4
          c <- c + 4
          d <- d + 4
       }
-   return(el)
+   return(gl)
    }

### 2025-07-19 analysis.qmd
circle

@@
    g5 <- make_ring(7) #circle graph
-   g6 <- add_vertices(g5, 1)
-   g6 <- g6 + edge(8,1) # circle graph plus pendant
-   g7 <- make_full_graph(6, directed = FALSE)
-   g7 <- add_vertices(g7, 1)
-   g7 <- g7 + edge(1,7) # clique plus pendant
-   g8 <- make_full_graph(7, directed = FALSE) # clique
+   g6 <- g5 + edge(6,1) # circle graph plus triangle
+   g7 <- g5 + edge(7,4) # circle graph plus long tie
+   g8 <- make_full_graph(6, directed = FALSE)
+   g8 <- add_vertices(g7, 1)
+   g8 <- g8 + edge(1,7) # clique plus pendant
+   g9 <- make_full_graph(7, directed = FALSE) # clique
 ```
@@
    dev.off()
-   png(here("Plots", "circle-plus-one.png"))
+   png(here("Plots", "circle-plus-triangle.png"))
    plot.graph.norm(g6, l = "circle")
    dev.off()
+   png(here("Plots", "circle-plus-long.png"))
+   plot.graph.norm(g7, l = "circle")
+   dev.off()
    png(here("Plots", "kite.png"))
-   plot.graph.norm(g7, l = "kk")
+   plot.graph.norm(g8, l = "kk")
    dev.off()
    png(here("Plots", "clique.png"))
-   plot.graph.norm(g8, l = "circle")
+   plot.graph.norm(g9, l = "circle")
    dev.off()

### 2025-07-19 manuscript.tex
Updates from Overleaf

@@
 In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
-With a scalar adjustment, the stratification increases, giving Node 1 a bit more privilege, but also demonstrating the extent to which Node 1's distinction is eroded.
+With a scalar adjustment, the stratification increases, giving Node 1 a slight advantage, but also highlighting the extent to which Node 1's distinction is eroded.
 In a maximally connected graph, the distinction of each node would also go to 0.00, as there is no network differentiation among nodes.
@@
     \centering
-     \begin{subfigure}[b]{0.35\textwidth}
+     \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/star.png}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.35\textwidth}
+     \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/sf.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/intra.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/inter.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/circle.png}
             \caption{Circle Graph}
-            \label{fig:inter}
+            \label{fig:circle}
     \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/circle-plus-one.png}
-            \caption{Circle Graph with Pendant Node}
-            \label{fig:inter}
+            \caption{Circle with Pendant}
+            \label{fig:circleplus}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/clique.png}
+            \caption{Clique Graph}
+            \label{fig:clique}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/kite.png}
+            \caption{Kite Graph}
+            \label{fig:kite}
     \end{subfigure}
@@
 
+NOTES FROM 7|19|25 Meeting
+***Triadic closure as distinction maximization*** 
+Strogatz is random, preferential attachment of closure
+Status homophilous (enh) attachment vs preferential vs random 
+I wonder how much of balance theory is really just distinction maximization?
+Non psychological theory polarity
+
+3 versions
+-Psychology
+-Polarity 
+-Status distinction
+
+*Tie that cuts the longest shortest path Science, 
+https://www.science.org/doi/full/10.1126/science.aau9735
+Distinction homophily, chicken or egg of
+
 \section{Conclusion}

### 2025-07-19 analysis.qmd
new toys

--- 2025-07-19 analysis.qmd
@@
    g5 <- make_ring(7) #circle graph
-   g6 <- add_vertices(g5, 1)
-   g6 <- g6 + edge(8,1) # circle graph plus pendant
-   g7 <- make_full_graph(6, directed = FALSE)
-   g7 <- add_vertices(g7, 1)
-   g7 <- g7 + edge(1,7) # clique plus pendant
+   g6 <- g5 + edge(6,1) # circle graph plus triangle
+   g7 <- g5 + edge(7,4) # circle graph plus long tie
    g8 <- make_full_graph(7, directed = FALSE) # clique
+   g9 <- make_full_graph(6, directed = FALSE)
+   g9 <- add_vertices(g9, 1)
+   g9 <- g9 + edge(1,7) # kite
+
 ```
@@
    dev.off()
-   png(here("Plots", "circle-plus-one.png"))
+   png(here("Plots", "circle-plus-triangle.png"))
    plot.graph.norm(g6, l = "circle")
    dev.off()
-   png(here("Plots", "kite.png"))
-   plot.graph.norm(g7, l = "kk")
+   png(here("Plots", "circle-plus-long.png"))
+   plot.graph.norm(g7, l = "circle")
    dev.off()
    png(here("Plots", "clique.png"))
-   plot.graph.norm(g8, l = "circle")
+   plot.graph.norm(g8, l = "kk")
+   dev.off()
+   png(here("Plots", "kite.png"))
+   plot.graph.norm(g9, l = "kk")
    dev.off()

### 2025-07-19 manuscript.tex

@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-one.png}
-            \caption{Circle with Pendant}
+        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-triangle.png}
+            \caption{Circle Graph with Closure}
+            \label{fig:circleplus}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-long.png}
+            \caption{Circle Graph with Long Tie}
             \label{fig:circleplus}
@@
 
-NOTES FROM 7|19|25 Meeting
-***Triadic closure as distinction maximization*** 
-Strogatz is random, preferential attachment of closure
-Status homophilous (enh) attachment vs preferential vs random 
-I wonder how much of balance theory is really just distinction maximization?
-Non psychological theory polarity
+%NOTES FROM 7|19|25 Meeting
+%***Triadic closure as distinction maximization*** 
+%Strogatz is random, preferential attachment of closure
+%Status homophilous (enh) attachment vs preferential vs random 
+%I wonder how much of balance theory is really just distinction maximization?
+%Non psychological theory polarity
 
-3 versions
--Psychology
--Polarity 
--Status distinction
+%3 versions
+%-Psychology
+%-Polarity, valenced ties 
+%-Status distinction
 
-*Tie that cuts the longest shortest path Science, 
-https://www.science.org/doi/full/10.1126/science.aau9735
-Distinction homophily, chicken or egg of
+%*Tie that cuts the longest shortest path Science, 
+%https://www.science.org/doi/full/10.1126/science.aau9735
+%Distinction homophily, chicken or egg of
 

### 2025-07-19 analysis.qmd
wheel

--- 2025-07-19 analysis.qmd
@@
    g5 <- make_ring(7) #circle graph
-   g6 <- add_vertices(g5, 1)
-   g6 <- g6 + edge(8,1) # circle graph plus pendant
-   g7 <- make_full_graph(6, directed = FALSE)
-   g7 <- add_vertices(g7, 1)
-   g7 <- g7 + edge(1,7) # clique plus pendant
+   g6 <- g5 + edge(6,1) # circle graph plus triangle
+   g7 <- g5 + edge(7,4) # circle graph plus long tie
    g8 <- make_full_graph(7, directed = FALSE) # clique
+   g9 <- make_full_graph(6, directed = FALSE)
+   g9 <- add_vertices(g9, 1)
+   g9 <- g9 + edge(1,7) # kite
+   g10 <- union(make_ring(7), make_star(7, center = 1, mode = "undirected"))
+   g10 <- g10 + edge(2,7)
+   plot(g10)
+
 ```
@@
    dev.off()
-   png(here("Plots", "circle-plus-one.png"))
+   png(here("Plots", "circle-plus-triangle.png"))
    plot.graph.norm(g6, l = "circle")
    dev.off()
-   png(here("Plots", "kite.png"))
-   plot.graph.norm(g7, l = "kk")
+   png(here("Plots", "circle-plus-long.png"))
+   plot.graph.norm(g7, l = "circle")
    dev.off()
    png(here("Plots", "clique.png"))
-   plot.graph.norm(g8, l = "circle")
+   plot.graph.norm(g8, l = "kk")
+   dev.off()
+   png(here("Plots", "kite.png"))
+   plot.graph.norm(g9, l = "kk")
+   dev.off()
+   png(here("Plots", "wheel.png"))
+   plot.graph.norm(g10, l = "kk")
    dev.off()

### 2025-07-20 analysis.qmd
new v old

@@
    g10 <- g10 + edge(2,7)
-   plot(g10)
-
 ```
@@
    b <- connect.caves(c = 4, nc = 4, n = 20)
+```
+
+```{r}
+   source(here("Functions", "distinction.new.R"))
+   distinction(g1)
+   distinction.new(g1, norm = TRUE)
+```
+
+```{r}
    c <- lapply(b, distinction.new, norm = FALSE)
+```
+
+```{r}
    gg2 <- function(x, lay.o = "kk") {

### 2025-07-20 Functions/distinction.R

@@ -1,43 +1,53 @@
-distinction <- function(x) { 
+distinction <- function(x, norm = FALSE) { #distinction centrality function
    library(igraph)
-   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
    V <- vcount(x)
-   if (has.labels == 0) {
+   no.labels <- is.null(V(x)$name)
+   if (no.labels == TRUE) {
       V(x)$name <- 1:V
       names <- V(x)$name 
       }
-   if (has.labels == 1) {
+   if (no.labels == FALSE) {
       names <- V(x)$name 
       V(x)$name <- 1:V
       }
-   s <- eigen_centrality(x)$vector
-   d <- rep(V, 0)
-   u <- rep(V, 0)
+   norm.max <- function(x) {return(x/max(x))}
+   A <- as.matrix(as_adjacency_matrix(x))
+   nc <- components(x)$no
+   if (nc > 1) {
+      s <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
+      }
+   else if (nc == 1) {
+      s <- abs(eigen(A)$vectors[, 1])
+      }
+   if (norm == TRUE) {s <- norm.max(s)}
+   names(s) <- V(x)$name
+   d <- rep(V, 0) # initializing distinction vector
+   u <- rep(V, 0) # initializing constraint vector
+   labs <- V(x)$name
    for (i in as.character(V(x)$name)) {
       j <- names(neighbors(x, i))
       x.d <- delete_vertices(x, i)
-      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
-      e <- as.numeric(ecount(x.d) == 0) #checking for empty
-      if (c == 1 & e == 0) { #connected non-empty graph
-         s.a <- eigen_centrality(x.d)$vector[j]
-         } #end if
-      else if (c == 0 & e == 1) { #empty graph
+      c <- is_connected(x.d) #checking for connectedness of node-deleted subgraph
+      e <- ecount(x.d) == 0 #checking for emptiness of node-deleted subgraph
+      if (c == TRUE & e == FALSE) { #connected non-empty node-deleted graph
+         A <- as.matrix(as_adjacency_matrix(x.d))
+         s.a <- abs(eigen(A)$vectors[, 1])
+         names(s.a) <- labs[-which(labs == i)]
+         if (norm == TRUE) {s.a <- norm.max(s.a)}
+         s.a <- s.a[j]
+         } #end main if
[…]

### 2025-07-20 Functions/distinction.old.R

@@ -1,4 +1,4 @@
-distinction.new <- function(x, norm = TRUE) { #distinction centrality function
+distinction.old <- function(x) { 
    library(igraph)
    has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
    V <- vcount(x)
@@ -11,10 +11,6 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
       V(x)$name <- 1:V
       }
    s <- eigen_centrality(x)$vector
-  if (norm == FALSE) {
-      s <- abs(eigen(as.matrix(as_adjacency_matrix(x)))$vectors[, 1])
-      names(s) <- V(x)$name
-      }
    d <- rep(V, 0)
    u <- rep(V, 0)
    for (i in as.character(V(x)$name)) {
@@ -24,10 +20,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
       e <- as.numeric(ecount(x.d) == 0) #checking for empty
       if (c == 1 & e == 0) { #connected non-empty graph
          s.a <- eigen_centrality(x.d)$vector[j]
-         if (norm == FALSE) {
-            s.a <- abs(eigen(as.matrix(as_adjacency_matrix(x.d)))$vectors[, 1])
-            } #end sub if
-         } #end main if
+         } #end if
       else if (c == 0 & e == 1) { #empty graph
          s.a <- 0
          } #end first else 
@@ -39,10 +32,7 @@ distinction.new <- function(x, norm = TRUE) { #distinction centrality function
             sub.g <- subgraph(x.d, names(which(C == k)))
             if (vcount(sub.g) > 1) {
                s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
-               if (norm == FALSE) {
-                  s.a[which(C == k)] <- abs(eigen(as.matrix(as_adjacency_matrix(sub.g)))$vectors[, 1])
-                  } #end sub if
-               } #end main if
+               }
             }
          names(s.a) <- names(C)
          s.a <- s.a[j]

### 2025-07-20 Functions/plot.graph.norm.R

@@ -1,6 +1,6 @@
 plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   library(ggraph)
-  d <- distinction(x)[, 3]
+  d <- distinction.new(x)[, 3]
   nc <- rep("", length(d))
   nc[which(d < -0.05)] <- "tan2"
   nc[which(d > 0.05)] <- "blue"

### 2025-07-20 analysis.qmd
new stuff

@@
    source(here("Functions", "distinction.R"))
-   source(here("Functions", "distinction.new.R"))
    source(here("Functions", "make.broker.trees.R"))
@@
 ```{r Toy Networks Plots}
-   png(here("Plots", "star.png"))
+   png(here("Plots", "Toys", "star.png"))
    plot.graph.norm(g1, l = "kk")
    dev.off()
-   png(here("Plots", "sf.png"))
+   png(here("Plots", "Toys", "sf.png"))
    plot.graph.norm(g2, l = "kk")
    dev.off()
-   png(here("Plots", "intra.png"))
+   png(here("Plots", "Toys", "intra.png"))
    plot.graph.norm(g3, l = "auto")
    dev.off()
-   png(here("Plots", "inter.png"))
+   png(here("Plots", "Toys", "inter.png"))
    plot.graph.norm(g4, l = "auto")
    dev.off()
-   png(here("Plots", "circle.png"))
+   png(here("Plots", "Toys", "circle.png"))
    plot.graph.norm(g5, l = "circle")
    dev.off()
-   png(here("Plots", "circle-plus-triangle.png"))
+   png(here("Plots", "Toys", "circle-plus-triangle.png"))
    plot.graph.norm(g6, l = "circle")
    dev.off()
-   png(here("Plots", "circle-plus-long.png"))
+   png(here("Plots", "Toys", "circle-plus-long.png"))
    plot.graph.norm(g7, l = "circle")
    dev.off()
-   png(here("Plots", "clique.png"))
+   png(here("Plots", "Toys", "clique.png"))
    plot.graph.norm(g8, l = "kk")
    dev.off()
-   png(here("Plots", "kite.png"))
+   png(here("Plots", "Toys", "kite.png"))
    plot.graph.norm(g9, l = "kk")
    dev.off()
-   png(here("Plots", "wheel.png"))
+   png(here("Plots", "Toys", "wheel.png"))
    plot.graph.norm(g10, l = "kk")
@@
     tab.cent(distinction(g5), name = "circle", label = "tab:circle")
-    tab.cent(distinction(g6), name = "circleplus", label = "tab:circleplus")
-    tab.cent(distinction(g6), name = "kite", label = "tab:kite")
+    tab.cent(distinction(g6), name = "circletriangle", label = "tab:circletriangle")
+    tab.cent(distinction(g7), name = "circlelong", label = "tab:circlelong")
+    tab.cent(distinction(g8), name = "clique", label = "tab:clique")
+    tab.cent(distinction(g9), name = "kite", label = "tab:kite")
+    tab.cent(distinction(g10), name = "wheel", label = "tab:wheel")
 ```
@@
    source(here("Functions", "connect.caves.R"))
-   set.seed(12345)
-   b <- connect.caves(c = 4, nc = 4, n = 20)
-```
-
-```{r}
-   source(here("Functions", "distinction.new.R"))
-   distinction(g1)
-   distinction.new(g1, norm = TRUE)
-```
-
-```{r}
-   c <- lapply(b, distinction.new, norm = FALSE)
-```
-
-```{r}
+   set.seed(456)
+   b <- connect.caves(c = 4, nc = 4, n = 24)
    gg2 <- function(x, lay.o = "kk") {
@@
       V(x)$name <- 1:n
-      c <- c(rep("tan2", n))
+      d <- distinction(x)[, 3]
+      c <-  vector(mode = "character", length = length(d))
+      c[which(d < -0.05)] <- "tan2"
+      c[which(d > 0.05)] <- "blue"
+      c[which(d >=-0.05 & d <= 0.05)] <- "purple"
+      c[which(d == max(d))] <- "red"
       w <- ggraph(x, layout = lay.o) + 
@@
       geom_node_text(aes(label = name), color = "white", size = 3) 
-      #ylim(-4, 3.5) + xlim(-4, 3.25) 
       return(w)
@@
       }
-   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
-   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
+   wrap_plots(p.list[c(1:4)], nrow = 2)
+   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
+   wrap_plots(p.list[c(5:8)], nrow = 2)
+   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
+   wrap_plots(p.list[c(9:12)], nrow = 2)
+   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
+   wrap_plots(p.list[c(13:16)], nrow = 2)
+   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
 ```

### 2025-07-20 Functions/connect.caves.R

@@ -1,27 +1,27 @@
 connect.caves <- function(c = 4, nc = 4, n = 12) {
-    make.cave.list <- function(c) {
+    make.cave.list <- function(a, b) {
       caves <- list() 
       i <- 1
-      for (k in 1:nc) {
-        j <- i + (c - 1)
+      for (k in 1:b) {
+        j <- i + (a - 1)
         caves[[k]] <- c(i:j)
-        i <- i + c
+        i <- i + a
       }
     return(caves)
     } # end make.cave.list
-    caves <- make.cave.list(c)
-    make.caves <- function(c, nc) {
-      g <- make_full_graph(c, directed = FALSE)
-      for (k in 2:nc) {
-        g <- g + make_full_graph(c, directed = FALSE)
+    caves <- make.cave.list(c, nc)
+    make.caves <- function(a, b) {
+      g <- make_full_graph(a, directed = FALSE)
+      for (k in 2:b) {
+        g <- g + make_full_graph(a, directed = FALSE)
         }
       return(g) 
       } # end make.caves
-    gl <- vector(mode = "list", length = n)
     g <- make.caves(c, nc)
+    gl <- vector(mode = "list", length = n)
     gl[[1]] <- g
     for (k in 2:n) {
-      ca <- sample(1:c, 2)
+      ca <- sample(1:nc, 2)
       ca1 <- caves[[ca[1]]]
       ca2 <- caves[[ca[2]]]
       g <- add_edges(g, c(sample(ca1, 1), sample(ca2, 1)))

### 2025-07-20 Functions/distinction.R

@@ -1,4 +1,4 @@
-distinction <- function(x, norm = FALSE) { #distinction centrality function
+distinction <- function(x, norm = FALSE) { 
    library(igraph)
    V <- vcount(x)
    no.labels <- is.null(V(x)$name)
@@ -10,16 +10,16 @@ distinction <- function(x, norm = FALSE) { #distinction centrality function
       names <- V(x)$name 
       V(x)$name <- 1:V
       }
-   norm.max <- function(x) {return(x/max(x))}
+   norm.max <- function(x) {return(x/max(x))} #normalizing function
    A <- as.matrix(as_adjacency_matrix(x))
-   nc <- components(x)$no
+   nc <- components(x)$no #checking for disconnected graph
    if (nc > 1) {
       s <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
       }
    else if (nc == 1) {
       s <- abs(eigen(A)$vectors[, 1])
       }
-   if (norm == TRUE) {s <- norm.max(s)}
+   if (norm == TRUE) {s <- norm.max(s)} #normalizing by maximum
    names(s) <- V(x)$name
    d <- rep(V, 0) # initializing distinction vector
    u <- rep(V, 0) # initializing constraint vector
@@ -33,7 +33,7 @@ distinction <- function(x, norm = FALSE) { #distinction centrality function
          A <- as.matrix(as_adjacency_matrix(x.d))
          s.a <- abs(eigen(A)$vectors[, 1])
          names(s.a) <- labs[-which(labs == i)]
-         if (norm == TRUE) {s.a <- norm.max(s.a)}
+         if (norm == TRUE) {s.a <- norm.max(s.a)} #normalizing by maximum
          s.a <- s.a[j]
          } #end main if
       else if (c == FALSE & e == TRUE) { #empty node-deleted graph
@@ -44,7 +44,7 @@ distinction <- function(x, norm = FALSE) { #distinction centrality function
          nc <- components(x.d)$no         
          s.a <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
          names(s.a) <- labs[-which(labs == i)]
-         if (norm == TRUE) {s.a <- norm.max(s.a)}
+         if (norm == TRUE) {s.a <- norm.max(s.a)} #normalizing by maximum
          s.a <- s.a[j]
          } #end second else
       u[i] <- mean(s.a) #i's average neighbor eigenvector centrality in node deleted subgraph

### 2025-07-20 Functions/plot.graph.norm.R

@@ -1,6 +1,6 @@
 plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   library(ggraph)
-  d <- distinction.new(x)[, 3]
+  d <- distinction(x)[, 3]
   nc <- rep("", length(d))
   nc[which(d < -0.05)] <- "tan2"
   nc[which(d > 0.05)] <- "blue"

### 2025-07-20 manuscript.tex
Updates from Overleaf

@@
 \subsection{Distinction Centrality's Measurement Parameters}
+Below we present a variety of toy model to explore the relationship between network shape and density and the calculated measure of network distinction.
+
+\subsubsection{Distinction and Brokerage: Structural Holes vs. Structural Folds}
 In Figure 1, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors.
@@
     \centering
-     \begin{subfigure}[b]{0.3\textwidth}
+     \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/star.png}
@@
             \label{fig:star}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.3\textwidth}
+    \end{subfigure} \\
+     \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/sf.png}
@@
     \end{subfigure} 
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/intra.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/inter.png}
@@
     \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/wheel.png}
+            \caption{Wheel Graph}
+            \label{fig:wheel}
+    \end{subfigure}
+
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+    \label{fig:toys}
+\end{figure}
+
+\input{Tabs/star}
+\input{Tabs/structfold.tex}
+\input{Tabs/intraclust}
+\input{Tabs/interclust}
+\input{Tabs/circle}
+
+\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
+Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
+Compared to the structural fold, connections 3-2 and 6-7 have been removed.
+Measurement results are in Table 3.
+Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
+The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
+
+\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
+This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+In fact, all nodes except 3 and 6 have higher distinction in such a case.
+This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
+increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
+
+\subsubsection{Circle Graphs and Triadic Closure Incentives}
+Here be dragons.
+
+%Strogatz is random, preferential attachment of closure
+%Status homophilous (enh) attachment vs preferential vs random
+
+%***Triadic closure as distinction maximization*** 
+%Triadic closure 3 versions
+%-Psychology
+%-Balance version response triadic closure, Polarity, valenced ties  balance was the reason 
+%-Status distinction 
+%I wonder how much of balance theory is really just distinction maximization?
+%Knights of the Round table, why equality conditions are fragile
+%kite graph-outsider breaks mechanical solidarity
+%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
+Try to get inequality in an organic solidarity system but that's unstable?
+(might have written that down wrong).
+%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
+%actually anthropologists ruined everything in the villages
+%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
+%theory of subgraph cliques rather than full graph as clique
+%*Tie that cuts the longest shortest path Science, 
+%https://www.science.org/doi/full/10.1126/science.aau9735
+%Distinction homophily, chicken or egg of
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
     \begin{subfigure}[b]{0.3\textwidth}
@@
 
-\input{Tabs/star}
-\input{Tabs/structfold.tex}
-\input{Tabs/intraclust}
-\input{Tabs/interclust}
-\input{Tabs/circle}
-
-\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
-Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
-Compared to the structural fold, connections 3-2 and 6-7 have been removed.
-Measurement results are in Table 3.
-Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
-The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
-
-\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
-This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
-The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
-In fact, all nodes except 3 and 6 have higher distinction in such a case.
-This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
-increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
-
-\subsection{Distinction with Structural Holes vs. Structural Folds}
-
-%Clique addition experiment
-
-%Add cliques to star graph and see what happens
-
-%See what happens with the caveman
-
-%Placehold graphs
-%\begin{figure}
-%   \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-%    \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
-%            \caption{Star Graph}
-%            \label{fig:Placehold}
-%    \end{subfigure}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
-%            \caption{Structural Fold}
-%            \label{fig:Placehold}
-%    \end{subfigure}
-%    \caption{Structural Holes with more added subgraphs.}
-%    \label{fig:toys}
-%\end{figure}
-
-\subsection{Long Ties and Hierarchy}
+\subsubsection{Long Ties and Hierarchy}
 This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs.
@@
 
-%NOTES FROM 7|19|25 Meeting
-%***Triadic closure as distinction maximization*** 
-%Strogatz is random, preferential attachment of closure
-%Status homophilous (enh) attachment vs preferential vs random 
-%I wonder how much of balance theory is really just distinction maximization?
-%Non psychological theory polarity
-
-%3 versions
-%-Psychology
-%-Polarity, valenced ties 
-%-Status distinction
-
-%*Tie that cuts the longest shortest path Science, 
-%https://www.science.org/doi/full/10.1126/science.aau9735
-%Distinction homophily, chicken or egg of
-
 \section{Conclusion}

### 2025-07-20 analysis.qmd
new tabs

@@
 ```{r Toy Network Distinction Tables}
-    tab.cent(distinction(g1), name = "star", label = "tab:star")
-    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
-    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
-    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
-    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
-    tab.cent(distinction(g6), name = "circletriangle", label = "tab:circletriangle")
-    tab.cent(distinction(g7), name = "circlelong", label = "tab:circlelong")
-    tab.cent(distinction(g8), name = "clique", label = "tab:clique")
-    tab.cent(distinction(g9), name = "kite", label = "tab:kite")
-    tab.cent(distinction(g10), name = "wheel", label = "tab:wheel")
+   source(here("Functions", "tab.cent.R"))
+   tab.cent(distinction(g1), name = "star", 
+   label = "tab:star", rownames = c("1", "2, 3, 4, 5, 6, 7"))
+   tab.cent(distinction(g2), name = "structfold", 
+   label = "tab:sf", rownames = c("1", "2, 3, 4, 5, 6, 7"))
+   tab.cent(distinction(g3), name = "intraclust", 
+   label = "tab:intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"))
+   tab.cent(distinction(g4), name = "interclust", 
+   label = "tab:inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"))
+   tab.cent(distinction(g5), name = "circle", 
+   label = "tab:circle", rownames = c("1, 2, 3, 4, 5, 6, 7"))
+   tab.cent(distinction(g6), name = "circletriangle", 
+   label = "tab:circletriangle", 
+   rownames = c("1, 6", "2, 5", "3, 4", "7"))
+   tab.cent(distinction(g7), name = "circlelong", 
+   label = "tab:circlelong", 
+   rownames = c("1, 3", "2", "4, 7", "5, 6"))
+   tab.cent(distinction(g8), name = "clique", 
+   label = "tab:clique", rownames = c("1, 2, 3, 4, 5, 6, 7"))
+   tab.cent(distinction(g9), name = "kite", 
+   label = "tab:kite", rownames = c("1", "2, 3, 4, 5, 6", "7"))
+   tab.cent(distinction(g10), name = "wheel", 
+   label = "tab:wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"))
+
 ```

### 2025-07-20 Functions/tab.cent.R

@@ -1,11 +1,19 @@
-tab.cent <- function(x, d = 3, name = "name", caption = "", label = "label") { #table function
+tab.cent <- function(x, 
+      d = 3, 
+      name = "name", 
+      caption = "", 
+      label = "label",
+      rownames) { 
 library(kableExtra)
+library(dplyr)
+x <- distinct(x[, 2:6])
+x <- cbind(rownames, x)
 t <- kbl(x, 
       format = "latex", booktabs = TRUE, linesep = "",
       digits = d, row.names = FALSE,
-      col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
+      col.names = c("Nodes", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
       caption = caption, label = label
       ) %>% 
       kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
       save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))
-      }
+}

### 2025-07-20 analysis.qmd
captions

--- 2025-07-20 analysis.qmd
@@
 ```{r Toy Network Distinction Tables}
-    tab.cent(distinction(g1), name = "star", label = "tab:star")
-    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
-    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
-    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
-    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
-    tab.cent(distinction(g6), name = "circletriangle", label = "tab:circletriangle")
-    tab.cent(distinction(g7), name = "circlelong", label = "tab:circlelong")
-    tab.cent(distinction(g8), name = "clique", label = "tab:clique")
-    tab.cent(distinction(g9), name = "kite", label = "tab:kite")
-    tab.cent(distinction(g10), name = "wheel", label = "tab:wheel")
+   source(here("Functions", "tab.cent.R"))
+   tab.cent(distinction(g1), name = "star", 
+   label = "tab:star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for star graph.")
+   tab.cent(distinction(g2), name = "structfold", 
+   label = "tab:sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for structural fold graph.")
+   tab.cent(distinction(g3), name = "intraclust", 
+   label = "tab:intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
+   caption = "Distinction centrality scores for intra-connected clusters graph.")
+   tab.cent(distinction(g4), name = "interclust", 
+   label = "tab:inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
+   caption = "Distinction centrality scores for inter-connected clusters graph.")
+   tab.cent(distinction(g5), name = "circle", 
+   label = "tab:circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for circle graph.")
+   tab.cent(distinction(g6), name = "circletriangle", 
+   label = "tab:circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
+   caption = "Distinction centrality scores for circle graph with triangle.")
+   tab.cent(distinction(g7), name = "circlelong", 
+   label = "tab:circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
+   caption = "Distinction centrality scores for circle graph with long tie.")
+   tab.cent(distinction(g8), name = "clique", 
+   label = "tab:clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for clique graph.")
+   tab.cent(distinction(g9), name = "kite", 
+   label = "tab:kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
+   caption = "Distinction centrality scores for kite graph.")
+   tab.cent(distinction(g10), name = "wheel", 
+   label = "tab:wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for wheel graph.")
+
 ```

### 2025-07-20 Functions/plot.graph.norm.R

@@ -1,12 +1,11 @@
 plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   library(ggraph)
   d <- distinction(x)[, 3]
-  nc <- rep("", length(d))
+  nc <- vector(mode = "character", length = length(d))
   nc[which(d < -0.05)] <- "tan2"
   nc[which(d > 0.05)] <- "blue"
-  nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
+  nc[which(d >=-0.05 & d <= 0.05)] <- "purple"
   nc[which(d == max(d))] <- "red"
-
   if (is.null(V(x)$name) == TRUE) {
       n <- 1:vcount(x)
       tc <- "white"

### 2025-07-20 analysis.qmd
new wheel who dis

@@
    library(patchwork)
+   library(dplyr)
    source(here("Functions", "distinction.R"))
@@
    g9 <- g9 + edge(1,7) # kite
-   g10 <- union(make_ring(7), make_star(7, center = 1, mode = "undirected"))
-   g10 <- g10 + edge(2,7)
+   g10 <- g1 + edge(2,3)
+   g10 <- g10 + edge(3,4)
+   g10 <- g10 + edge(4,5)
+   g10 <- g10 + edge(5,6)
+   g10 <- g10 + edge(6,7)
+   g10 <- g10 + edge(7,2) #wheel graph
 ```
@@
 ```{r Toy Networks Plots}
+   source(here("Functions", "plot.graph.norm.R"))
    png(here("Plots", "Toys", "star.png"))

### 2025-07-20 Functions/plot.graph.norm.R

@@ -5,7 +5,7 @@ plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   nc[which(d < -0.05)] <- "tan2"
   nc[which(d > 0.05)] <- "blue"
   nc[which(d >=-0.05 & d <= 0.05)] <- "purple"
-  nc[which(d == max(d))] <- "red"
+  nc[which(d == max(d) & d >= 0.05)] <- "red"
   if (is.null(V(x)$name) == TRUE) {
       n <- 1:vcount(x)
       tc <- "white"

### 2025-07-20 analysis.qmd
new graphs who dis

@@
    b <- make.broker.trees(30)
-   c <- lapply(b, distinction.new, norm = FALSE)
-```
-
-```{r}
-   library(patchwork)
-   library(ggraph)
+   source(here("Functions", "gg.R"))
    p.list <- lapply(b, gg)

### 2025-07-20 Functions/gg.R

@@ -2,10 +2,10 @@ gg <- function(x, lay.o = "kk", star = 1) {
    n <- vcount(x)
    V(x)$name <- 1:n
    c <- c(rep("tan2", n))
-   c[star] <- "blue"
+   c[star] <- "red"
    gk <- which(degree(x) == 4)
    gk <- gk[gk != star]
-   c[gk] <- "red"
+   c[gk] <- "blue"
    w <- ggraph(x, layout = lay.o) + 
    geom_edge_link(color = "steelblue") + theme_graph() +
    geom_node_point(size = 5, color = c) + 

### 2025-07-20 Functions/tab.cent.R

@@ -11,7 +11,7 @@ x <- cbind(rownames, x)
 t <- kbl(x, 
       format = "latex", booktabs = TRUE, linesep = "",
       digits = d, row.names = FALSE,
-      col.names = c("Nodes", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
+      col.names = c("Nodes", "Distinction", "S-Distinction", "Status", "Constraint", "Scalar"),
       caption = caption, label = label
       ) %>% 
       kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 

### 2025-07-20 manuscript.tex
Updates from Overleaf

--- 2025-07-19 manuscript.tex
@@
     \centering
-     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/star.png}
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/star.png}
             \caption{Star Graph}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
             \caption{Structural Fold}
             \label{fig:sf}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/intra.png}
+    \end{subfigure} \\
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
             \caption{2-Connected Subgraphs}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/inter.png}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
             \caption{2-Connected Subgraphs with Long Tie}
@@
     \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
+            \caption{Wheel Graph}
+            \label{fig:wheel}
+    \end{subfigure}
+
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+    \label{fig:toys}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/circle.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle.png}
             \caption{Circle Graph}
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-triangle.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-triangle.png}
             \caption{Circle Graph with Closure}
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-long.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-long.png}
             \caption{Circle Graph with Long Tie}
@@
     \end{subfigure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/clique.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
             \caption{Clique Graph}
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/kite.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
             \caption{Kite Graph}
@@
 \input{Tabs/circle}
+\input{Tabs/kite}
+\input{Tabs/clique.tex}
+\input{Tabs/wheel}
+\input{Tabs/circletriangle}
+\input{Tabs/circlelong}
 
@@
 %\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+    \begin{subfigure}[b]{0.9\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/tree-examples.png}
+            \caption{Example of tree graphs with different numbers of branches for the star node.}
+            \label{fig:tree-examples}
+    \end{subfigure} \\
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/broker-tree-roles-by-nbranches.png}
+            \caption{Evolution of distinction scores by number of branches for the star node.}
+            \label{fig:broker-tree-roles}
+    \end{subfigure}
+    \caption{.}
+    \label{fig:toys}
+\end{figure}
 
@@
 
-%3 versions
+%Triadic closure 3 versions
 %-Psychology
@@
 
+%Knights of the Round table, why equality conditions are fragile
+%kite graph-outsider breaks mechanical solidarity
+%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
+Try to get inequality in an organic solidarity system but that's unstable?
+(might have written that down wrong).
+%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
+%actually anthropologists ruined everything in the villages
+%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
+%theory of subgraph cliques rather than full graph as clique
 %*Tie that cuts the longest shortest path Science, 
@@
 %Distinction homophily, chicken or egg of
+
+%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
+%folds vs circles
+%college caves, BYU vs Notre Dame vs regulars
 

### 2025-07-20 analysis.qmd
gg

@@
    source(here("Functions", "connect.caves.R"))
+   source(here("Functions", "gg2.R"))
    set.seed(456)
    b <- connect.caves(c = 4, nc = 4, n = 24)
-   gg2 <- function(x, lay.o = "kk") {
-      n <- vcount(x)
-      V(x)$name <- 1:n
-      d <- distinction(x)[, 3]
-      c <-  vector(mode = "character", length = length(d))
-      c[which(d < -0.05)] <- "tan2"
-      c[which(d > 0.05)] <- "blue"
-      c[which(d >=-0.05 & d <= 0.05)] <- "purple"
-      c[which(d == max(d))] <- "red"
-      w <- ggraph(x, layout = lay.o) + 
-      geom_edge_link(color = "steelblue") + theme_graph() +
-      geom_node_point(size = 5, color = c) + 
-      geom_node_text(aes(label = name), color = "white", size = 3) 
-      return(w)
-      }
    p.list <- lapply(b, gg2, lay.o = "auto")

### 2025-07-20 Functions/gg2.R

@@ -1,0 +1,15 @@
+gg2 <- function(x, lay.o = "kk") {
+   n <- vcount(x)
+   V(x)$name <- 1:n
+   d <- distinction(x)[, 3]
+   c <-  vector(mode = "character", length = length(d))
+   c[which(d < -0.05)] <- "tan2"
+   c[which(d > 0.05)] <- "blue"
+   c[which(d >=-0.05 & d <= 0.05)] <- "purple"
+   c[which(d == max(d))] <- "red"
+   w <- ggraph(x, layout = lay.o) + 
+   geom_edge_link(color = "steelblue") + theme_graph() +
+   geom_node_point(size = 5, color = c) + 
+   geom_node_text(aes(label = name), color = "white", size = 3) 
+   return(w)
+   }

### 2025-07-20 manuscript.tex
do it

@@
 \subsection{Distinction Centrality's Measurement Parameters}
-In Figure 1, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors.
+Below, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors.
+
+\subsubsection{Structural Holes vs Structural Folds}
  In each model, there are seven nodes, and node 1 is the best-connected node in the network.
@@
 
+\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
+Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
+Compared to the structural fold, connections 3-2 and 6-7 have been removed.
+Measurement results are in Table 3.
+Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
+The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
+
+\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
+This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+In fact, all nodes except 3 and 6 have higher distinction in such a case.
+This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
+increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
+
+\subsubsection{Circle Graphs and Triadic Closure}
+%NOTES FROM 7|19|25 Meeting
+%***Triadic closure as distinction maximization*** 
+%Strogatz is random, preferential attachment of closure
+%Status homophilous (enh) attachment vs preferential vs random 
+%I wonder how much of balance theory is really just distinction maximization?
+%Non psychological theory polarity
+
+%Triadic closure 3 versions
+Psychology
+Polarity, valenced ties 
+Status distinction
+
+%Knights of the Round table, why equality conditions are fragile
+%kite graph-outsider breaks mechanical solidarity
+%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
+Try to get inequality in an organic solidarity system but that's unstable?
+(might have written that down wrong).
+%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
+%actually anthropologists ruined everything in the villages
+%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
+%theory of subgraph cliques rather than full graph as clique
+%*Tie that cuts the longest shortest path Science, 
+%https://www.science.org/doi/full/10.1126/science.aau9735
+%Distinction homophily, chicken or egg of
+
+%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
+%folds vs circles
+%college caves, BYU vs Notre Dame vs regulars
+
 \begin{figure}
@@
 
-\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
-Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
-Compared to the structural fold, connections 3-2 and 6-7 have been removed.
-Measurement results are in Table 3.
-Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
-The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
-
-\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
-This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
-The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
-In fact, all nodes except 3 and 6 have higher distinction in such a case.
-This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
-increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
-
-\subsection{Distinction with Structural Holes vs. Structural Folds}
-
 %Clique addition experiment
@@
 %See what happens with the caveman
-
-%Placehold graphs
-%\begin{figure}
-%   \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-%    \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
-%            \caption{Star Graph}
-%            \label{fig:Placehold}
-%    \end{subfigure}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
-%            \caption{Structural Fold}
-%            \label{fig:Placehold}
-%    \end{subfigure}
-%    \caption{Structural Holes with more added subgraphs.}
-%    \label{fig:toys}
-%\end{figure}
 
@@
 
-\subsection{Long Ties and Hierarchy}
+\subsubsection{Long Ties and Hierarchy}
 This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs.
@@
 
-%NOTES FROM 7|19|25 Meeting
-%***Triadic closure as distinction maximization*** 
-%Strogatz is random, preferential attachment of closure
-%Status homophilous (enh) attachment vs preferential vs random 
-%I wonder how much of balance theory is really just distinction maximization?
-%Non psychological theory polarity
-
-%Triadic closure 3 versions
-%-Psychology
-%-Polarity, valenced ties 
-%-Status distinction
-
-%Knights of the Round table, why equality conditions are fragile
-%kite graph-outsider breaks mechanical solidarity
-%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
-Try to get inequality in an organic solidarity system but that's unstable?
-(might have written that down wrong).
-%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
-%actually anthropologists ruined everything in the villages
-%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
-%theory of subgraph cliques rather than full graph as clique
-%*Tie that cuts the longest shortest path Science, 
-%https://www.science.org/doi/full/10.1126/science.aau9735
-%Distinction homophily, chicken or egg of
-
-%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
-%folds vs circles
-%college caves, BYU vs Notre Dame vs regulars
-
 \section{Conclusion}

### 2025-07-20 analysis.qmd
updated analysis

@@
    source(here("Functions", "distinction.R"))
-   source(here("Functions", "make.broker.trees.R"))
-   source(here("Functions", "make.broker.cliques.R"))
    source(here("Functions", "plot.graph.norm.R"))
@@
 ```{r}
+   source(here("Functions", "make.broker.trees.R"))
+   source(here("Functions", "gg.R"))
    b <- make.broker.trees(30)
-   source(here("Functions", "gg.R"))
    p.list <- lapply(b, gg)
@@
 ```{r}
+   source(here("Functions", "make.broker.cliques.R"))
+   source(here("Functions", "gg.R"))
+   b <- make.broker.cliques(30)
    p.list <- lapply(b, gg, star = 9)

### 2025-07-20 manuscript.tex

@@
 In the case of politics, status refers to the ability to access those who themselves have higher levels of access, with those most central to the access network having the authority to make decisions.
-This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972norms}.
+This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972factoring-03e}.
 Status is higher for actors when the people they are connected to are themselves influential, and accessibility is merely a political reframe of the context.
-The internal stratification of individuals is determined by who has greater connections to those with even greater connections, with those having few connections to other important people being at the bottom of the hierarchy \citep{bonacich1972norms}.
+The internal stratification of individuals is determined by who has greater connections to those with even greater connections, with those having few connections to other important people being at the bottom of the hierarchy \citep{bonacich1972factoring-03e}.
 
@@
 \section{A Generalized Measure of Network Distinction}
-Below, we present a measure of distinction centrality, determine the appropriate application of a scalar factor, and indicate the availability of an R program to facilitate easy implementation of the measure in further work.
+In this section, we present our measure of distinction centrality, which incorporates a scalar adjustment factor to mitigate arbitrary scaling issues.
+We also indicate the availability of an \textit{R} custom function to facilitate the easy implementation of the measure in further work.
 
@@
 
-A formalization of this interaction between status and uniqueness allows for a measure of network distinction.
+Formalizing the interaction between status and uniqueness allows for a measure of network distinction.
 Distinction as a theoretical concept is composed of status mediated by autonomy.
-A distinction measure can reflect this by considering an actor's status and then discounting their status by the status of their neighbors, independent of the actor.
-The more reliant an actor's neighbors are on the actor for their status, the lower the actor's ability to exert their influence, and thus the lower their distinction.
-In other words, autonomy is determined by how much one's neighbors rely on you to maintain their position in the network.
+A distinction measure can reflect this by considering an actor's status and then discounting it by the counterfactual status of their neighbors when the focal actor is absent from the network.
+The more reliant an actor's neighbors are on the actor for their status, the lower the focal actor's ability to exert influence over them, and thus the lower their distinction.
+In other words, autonomy is determined by how much one's neighbors rely on you to maintain their advantageous position in the network.
 
-Distinction centrality can be measured using the following expression:
+Accordingly, we propose the following as a measure of distinction:
+
 \begin{equation}
-\beta_i=Sx_i-{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}} 
+\beta_i= \alpha s_i - \kappa_i
+\label{eq:distinction}
 \end{equation}
 
-Let $\beta_i$ be the distinction centrality of a given individual \textit{i}.
-The first term captures the status of a given actor.
-Let \textit{x} be the eigenvector centrality of the designated individual.
-Let S be a scalar that adjusts the social value placed on status relative to constraint, as discussed below.
-The second term captures the element of autonomy.
-Removing individual \textit{i} from the network, compute the eigenvectors of the remaining individuals and sum those that are connected to individual \textit{i}, taking the average eigenvector of neighbors \textit{j} as the constraint confronting node \textit{i} in the network.
-This is substantively the same mechanism as conducted in a jackknife resampling procedure, except that rather than forming a sampling distribution, we are measuring local constraints.
-Finally, subtract the status of the average neighbor connected to \textit{i} from \textit{i}’s scalar-adjusted eigenvector centrality in the whole network.
+Where $\beta_i$ is the distinction centrality score of actor \textit{i}, $s_i$ is actor $i$'s status, $\kappa_i$ is actor $i$'s network constraint (the obverse of autonomy), and $\alpha$ is a scalar adjustment factor to be discussed below.
+Each individual's status score $s_i$ is obtained from the vector $\mathbf{s}$ obtained from solving the standard linear eigenvector equation:
 
-When a node is an isolate, we set its eigenvector centrality to $x_i =0$.
-In the case of a network with no connections (such as an empty graph), some routines calculate it as $x_i =1.0$.
-However, given that it is still a network with no connections, setting isolates at $x_i =0$ is theoretically appropriate, considering that status is a reflection of connections.
-It would be inappropriate for an isolate to have the same status as the highest-status node in a large network.
-Additionally, given the second step of subtraction, it is only theoretically meaningful if set as $x_i =0$ in the case of distinction centrality.
+\begin{equation}
+\lambda\mathbf{s}= \mathbf{A}\mathbf{s}
+\label{eq:eigen}
+\end{equation}
 
-\subsection{Scalar Adjustment}
-First, a scalar is required because the relative value of status and autonomy is not inherently fixed in a social system.
-We might imagine situations where one desires more status at the expense of autonomy if the rewards to status are higher, or values autonomy more highly if the rewards to status are low.
-There cannot be an assumed unadjusted equivalence between the resulting eigenvectors of the two terms for this theoretical level.
+Where $\mathbf{A}$ is the network's adjacency matrix and $\mathbf{s}$ is the right dominant eigenvector of the matrix; status, therefore, is given by the usual eigenvector centrality score \citep{bonacich1972factoring-03e}, taken as the absolute value of each individual's score on the first eigenvector of the adjacency matrix.
+When a node is an isolate, either in the larger graph or in the node-deleted subgraph used to compute constraint scores, we set its status score to $s_i =0$.\footnote{In the case of a network with no connections (such as an empty graph), some routines calculate it as $s_i =1.0$.
+However, given that it is still a network with no connections, setting isolates at $s_i =0$ is theoretically appropriate, considering that status is a reflection of connections.
+It would be inappropriate for an isolate to have the same status as the highest-status node in a large network.}
 
-Additionally, due to the hierarchical nature of networks, the average constraint in the network is greater than the average status.
-The high average constraint of their neighbors is often much larger than the impact of status.
-The result is that, at the level of the entire network, those who are deeply embedded among the most elite, without a basis of supporters, are very indistinct when considering the high constraints placed on them by their high-status alters.
-Thus, the calculated results without a scalar may fail to capture the appropriate value of status compared to the constraint.
+The second term $\kappa_i$ in equation~\ref{eq:distinction} is a \textbf{localized induced centrality} score \citep{borgatti2020oxford-fa6}.
+It is given by the average status (eigenvector centrality) of $i$'s neighbors in the \textit{node-deleted subgraph} of the focal graph $G$ that excludes $i$:
 
-While an arbitrary scalar is possible, it can yield erroneous results when applied to empirical networks.
-However, a scalar can be derived from the network itself due to the field positional interplay between status and constraint.
-Imagining two actors of equal status and personal constraint, one in an averagely more constrained system and the other in a less averagely constrained system, with average status otherwise equal.
-In such a case, the status of an actor in the more constrained system has a greater impact on their social distinction than in the less constrained system.
-With high constraint, status takes on greater importance in determining social distinction because it compels deference.
-In other words, it is the difference between a hierarchical system with and without constraints.
-Status with a weak constraint means a weaker compulsion of deference.
-The structure of constraint has a reverberative impact on social distinction beyond its contribution.
+\begin{equation}
+    \kappa_i = \frac{\sum_{j \in N(i)}s_j^{G-i}}{|N(i)|}
+\end{equation}
 
-With this social understanding of how constraint interacts with the transmission of status, an endogenous scalar can be derived from the network.
-The average constraint of actors within the network divided by the average status of actors in the network creates a scalar that reflects the relationship between status and constraint.
+Where $|N(i)|$ is the cardinality of node $i$'s neighbor set (node $i$'s degree), and $s_j^{G-i}$ is the status of node $j$ in the graph that excludes node $i$.\footnote{The $\kappa$ term is meant to capture the element of autonomy.
+This is substantively the same mechanism as conducted in a jackknife resampling procedure, except that rather than forming a sampling distribution, we are measuring local constraints.} Thus the $\kappa_i$ component of equation~\ref{eq:distinction} is larger for nodes whose neighbors would gain a lot in status (on average) if they were to be removed from the network.
 
-\[S=\frac{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}}{\overline{x_i}} \]
+Understanding that both $s_i$ and $k_i$ are given in the (arbitrary) scaling produced by the eigenvector scoring procedure, it is desirable to re-scale the distinction centrality measure so that it has a natural zero point.
+As equation~\ref{eq:distinction} shows, we do this by multiplying each actor's status score by a scaling factor, which is given by:
 
-Under conditions of high average constraint and low average status, the scalar is large, indicating the significant role of status in determining social distinction.
-Under conditions where the average constraint is low and the average status is high, the scalar is weaker, reflecting a system in which status is less important in determining social distinction.
-Under very large-scale conditions, the averages of status and constraint should trend towards 1, weakening the necessity of the scalar.
-However, under constrained conditions, particularly in elite networks with missing data on the social scaffolding that created the network elites, the scalar is more important for explaining action because the range of eigenvector network measures is otherwise artificially expanded due to the missing data.
+\begin{equation}
+    \alpha = \frac{\bar{\mathbf{\kappa}}}{\bar{\mathbf{s}}}
+\end{equation}
 
-Without a scalar, networks with any degree of hierarchy see the average constraint overwhelm the average status because many low-status nodes are tied to high-status nodes.
-The advantage of this scalar is to ensure that the average scalar status in the network equals the average constraint in the network.
-Thus, total status is equal to total constraint, and from there it becomes a matter of distribution among members.
-From there, however, it enables comparability between networks that would otherwise be impossible.
-With the understanding that we have, through the scalar, adjusted for a network where one's combination of status and constraint is better or worse, networks can be compared so long as the unobserved social context within the network remains stable.
+Where $\bar{\mathbf{\kappa}}$ is the mean of the vector of $\kappa_i$ constraint scores for each actor in the network, and $\bar{\mathbf{\kappa}}$ is the mean of the vector of $s_i$ status scores for each actor in the network.
+As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:tab:circle} and~\ref{tab:clique}).
 
@@
 \input{Tabs/kite}
-\input{Tabs/clique.tex}
+\input{Tabs/clique}
 \input{Tabs/wheel}

### 2025-07-20 old-scalar-verbiage.tex

\subsection{Scalar Adjustment}
First, a scalar is required because the relative value of status and autonomy is not inherently fixed in a social system. We might imagine situations where one desires more status at the expense of autonomy if the rewards to status are higher, or values autonomy more highly if the rewards to status are low. There cannot be an assumed unadjusted equivalence between the resulting eigenvectors of the two terms for this theoretical level.

Additionally, due to the hierarchical nature of networks, the average constraint in the network is greater than the average status. The high average constraint of their neighbors is often much larger than the impact of status. The result is that, at the level of the entire network, those who are deeply embedded among the most elite, without a basis of supporters, are very indistinct when considering the high constraints placed on them by their high-status alters. Thus, the calculated results without a scalar may fail to capture the appropriate value of status compared to the constraint.

While an arbitrary scalar is possible, it can yield erroneous results when applied to empirical networks. However, a scalar can be derived from the network itself due to the field positional interplay between status and constraint. Imagining two actors of equal status and personal constraint, one in an averagely more constrained system and the other in a less averagely constrained system, with average status otherwise equal. In such a case, the status of an actor in the more constrained system has a greater impact on their social distinction than in the less constrained system. With high constraint, status takes on greater importance in determining social distinction because it compels deference. In other words, it is the difference between a hierarchical system with and without constraints. Status with a weak constraint means a weaker compulsion of deference. The structure of constraint has a reverberative impact on social distinction beyond its contribution.

With this social understanding of how constraint interacts with the transmission of status, an endogenous scalar can be derived from the network. The average constraint of actors within the network divided by the average status of actors in the network creates a scalar that reflects the relationship between status and constraint.

\[S=\frac{\frac{1}{n_{j=i}}\sum_{{j}\in{A},i\neq{j}}x_{j}}{\overline{x_i}} \]

Under conditions of high average constraint and low average status, the scalar is large, indicating the significant role of status in determining social distinction. Under conditions where the average constraint is low and the average status is high, the scalar is weaker, reflecting a system in which status is less important in determining social distinction. Under very large-scale conditions, the averages of status and constraint should trend towards 1, weakening the necessity of the scalar. However, under constrained conditions, particularly in elite networks with missing data on the social scaffolding that created the network elites, the scalar is more important for explaining action because the range of eigenvector network measures is otherwise artificially expanded due to the missing data.

Without a scalar, networks with any degree of hierarchy see the average constraint overwhelm the average status because many low-status nodes are tied to high-status nodes. The advantage of this scalar is to ensure that the average scalar status in the network equals the average constraint in the network. Thus, total status is equal to total constraint, and from there it becomes a matter of distribution among members. From there, however, it enables comparability between networks that would otherwise be impossible. With the understanding that we have, through the scalar, adjusted for a network where one's combination of status and constraint is better or worse, networks can be compared so long as the unobserved social context within the network remains stable.

### 2025-07-20 analysis.qmd
new stuff

@@
    tab.cent(distinction(g1), name = "star", 
-   label = "tab:star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   label = "star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
    caption = "Distinction centrality scores for star graph.")
    tab.cent(distinction(g2), name = "structfold", 
-   label = "tab:sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   label = "sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
    caption = "Distinction centrality scores for structural fold graph.")
    tab.cent(distinction(g3), name = "intraclust", 
-   label = "tab:intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
+   label = "intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
    caption = "Distinction centrality scores for intra-connected clusters graph.")
    tab.cent(distinction(g4), name = "interclust", 
-   label = "tab:inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
+   label = "inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
    caption = "Distinction centrality scores for inter-connected clusters graph.")
    tab.cent(distinction(g5), name = "circle", 
-   label = "tab:circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   label = "circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
    caption = "Distinction centrality scores for circle graph.")
    tab.cent(distinction(g6), name = "circletriangle", 
-   label = "tab:circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
+   label = "circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
    caption = "Distinction centrality scores for circle graph with triangle.")
    tab.cent(distinction(g7), name = "circlelong", 
-   label = "tab:circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
+   label = "circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
    caption = "Distinction centrality scores for circle graph with long tie.")
    tab.cent(distinction(g8), name = "clique", 
-   label = "tab:clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   label = "clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
    caption = "Distinction centrality scores for clique graph.")
    tab.cent(distinction(g9), name = "kite", 
-   label = "tab:kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
+   label = "kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
    caption = "Distinction centrality scores for kite graph.")
    tab.cent(distinction(g10), name = "wheel", 
-   label = "tab:wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   label = "wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
    caption = "Distinction centrality scores for wheel graph.")

### 2025-07-20 manuscript.tex
Updates from Overleaf

@@
 Where $\bar{\mathbf{\kappa}}$ is the mean of the vector of $\kappa_i$ constraint scores for each actor in the network, and $\bar{\mathbf{\kappa}}$ is the mean of the vector of $s_i$ status scores for each actor in the network.
-As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:tab:circle} and~\ref{tab:clique}).
+As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:circle} and~\ref{tab:clique}).
 

### 2025-07-20 analysis.qmd
just do it

@@
 
+## Star Graph Computational Experiments
+
+```{r}
+   make.stars <- function(n = 30) {
+      gl <- vector(mode = "list", length = n)
+      gl[[1]] <- make_star(3, mode = "undirected") 
+      for (k in 2:n) {
+         gl[[k]] <- make_star(k+2, mode = "undirected") 
+         }
+      return(gl)
+      }
+   b <- make.stars(33)
+   c <- lapply(b, distinction)
+   ds.s <- sapply(c, function(x) {x[1, 3]})
+   ds.p <- sapply(c, function(x) {x[2, 3]})
+   d.s <- sapply(c, function(x) {x[1, 2]})
+   d.p <- sapply(c, function(x) {x[2, 2]})
+   dat <- data.frame(d = c(ds.s, ds.p, d.s, d.p), 
+         n = c(1:length(d.s), 1:length(d.s), 1:length(d.s), 1:length(d.s)),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s)), rep(4, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c(
+                           "Scaled Distinction (Star)", 
+                           "Scaled Distinction (Peripheral)", 
+                           "Non-scaled Distinction (Star)",
+                           "Non-scaled Distinction (Peripheral)"))) |> 
+         mutate(n = n + 2)
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "", x = "Star Size")
+   p <- p + scale_x_continuous(breaks = seq(3, length(d.s), by = 3))
+   p <- p + scale_color_manual(values = c("red", "blue", "tan2", "purple"))
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 16, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "top"
+                  )
+   p <- p + guides(color = guide_legend(nrow = 2))
+   p
+   ggsave(here("Plots", "star-roles-by-size.png"), width = 7, height = 7, units = "in")
+```
 ## Connected Caves Computational Experiments
@@
 
-## Broker Computational Experiements
+## Broker Computational Experiments
 

### 2025-07-20 manuscript.tex

@@
 Where $\bar{\mathbf{\kappa}}$ is the mean of the vector of $\kappa_i$ constraint scores for each actor in the network, and $\bar{\mathbf{\kappa}}$ is the mean of the vector of $s_i$ status scores for each actor in the network.
-As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:circle} and~\ref{tab:clique}).
+As hinted earlier, a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:circle} and~\ref{tab:clique}).
 

### 2025-07-20 manuscript.tex
new edits

@@
 As hinted earlier, a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:circle} and~\ref{tab:clique}).
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{Plots/star-roles-by-size.png}
+    \caption{Enter Caption}
+    \label{fig:star-scaling}
+\end{figure}
+
+Another advantage of rescaling the $s_i$ component of equation~\ref{eq:distinction} is that it makes the distinction score of key nodes in the graph sensitive to network scaling, so that it increases when peripheral actors are added to the network.
+For instance, Figure~\ref{fig:star-scaling} illustrates the centrality score for star and peripheral nodes in star graphs of varying sizes.
+As we can see, when distinction is calculated simply as $\beta^*_i = s_i - \kappa_i$, the distinction score is a constant for the star nodes across graphs of different sizes, demonstrating insensitivity to network scaling.
+By way of contrast, when distinction is calculated as in Equation~\ref{eq:distinction}, then we observe that the distinction score of the star node increases logarithmically with network size, which is precisely what we want, as a star mediating between many peripheral nodes should be more distinct that a star mediating between just a few peripheral nodes.
 

### 2025-07-21 analysis.qmd
new plot

--- 2025-07-20 analysis.qmd
@@
 
+```{r}
+   g <- make_graph(c(1,2, 2,3, 3,4, 4,5, 5,6, 6,7, 7,8, 8,9, 9,10), directed = FALSE)
+   distinction(g)
+```
+
+## Star Graph Computational Experiments
+
+```{r}
+   make.stars <- function(n = 30) {
+      gl <- vector(mode = "list", length = n)
+      gl[[1]] <- make_star(3, mode = "undirected") 
+      for (k in 2:n) {
+         gl[[k]] <- make_star(k+2, mode = "undirected") 
+         }
+      return(gl)
+      }
+   b <- make.stars(33)
+   c <- lapply(b, distinction)
+   ds.s <- sapply(c, function(x) {x[1, 3]})
+   ds.p <- sapply(c, function(x) {x[2, 3]})
+   d.s <- sapply(c, function(x) {x[1, 2]})
+   d.p <- sapply(c, function(x) {x[2, 2]})
+   dat <- data.frame(d = c(ds.s, ds.p, d.s, d.p), 
+         n = c(1:length(d.s), 1:length(d.s), 1:length(d.s), 1:length(d.s)),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s)), rep(4, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c(
+                           "Scaled Distinction (Central Node)", 
+                           "Scaled Distinction (Peripheral Nodes)", 
+                           "Non-scaled Distinction (Central Node)",
+                           "Non-scaled Distinction (Peripheral Nodes)"))) |> 
+         mutate(n = n + 2)
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "", x = "Star Size")
+   p <- p + scale_x_continuous(breaks = seq(3, length(d.s), by = 3))
+   p <- p + scale_color_manual(values = c("red", "blue", "tan2", "purple"))
+   p <- p + theme_minimal()
+   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 12, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "bottom"
+                  )
+   p <- p + guides(color = guide_legend(nrow = 4))
+   p
+   ggsave(here("Plots", "star-roles-by-size.png"), width = 7, height = 8, units = "in")
+```
 ## Connected Caves Computational Experiments

### 2025-07-21 Functions/distinction.R

@@ -39,7 +39,7 @@ distinction <- function(x, norm = FALSE) {
       else if (c == FALSE & e == TRUE) { #empty node-deleted graph
          s.a <- 0
          } #end first else 
-      else if (c == FALSE & e == FALSE) { #disconnected non-empty graph
+      else if (c == FALSE & e == FALSE) { #disconnected non-empty node-deleted graph
          A <- as.matrix(as_adjacency_matrix(x.d))
          nc <- components(x.d)$no         
          s.a <- rowSums(abs(eigen(A)$vectors[, 1:nc]))

### 2025-07-21 manuscript.tex

@@
 
-The second term $\kappa_i$ in equation~\ref{eq:distinction} is a \textbf{localized induced centrality} score \citep{borgatti2020oxford-fa6}.
-It is given by the average status (eigenvector centrality) of $i$'s neighbors in the \textit{node-deleted subgraph} of the focal graph $G$ that excludes $i$:
+The second term $\kappa_i$ in equation~\ref{eq:distinction} is a \textit{localized} induced centrality score in the sense of \citet{borgatti2020oxford-fa6}.
+According to \citet{everett2010induced-817}, an induced centrality is obtained whenever we calculate the difference that removing a node in the graph makes to some global property of the graph (a graph invariant).
+\citet{everett2010induced-817} suggest taking the sum of the centralities scores of the nodes in the node-deleted subgraph produced by removing a given node as that node's contribution to the centralities of other nodes in the graph, as a measure of that node's centrality.
+They propose examples extending this idea to the classical centrality measures like degree, closeness, and betweenness \citep{freeman79}.
+
+Here we extend the induced centrality approach in two ways and incorporate it into our measurement of distinction.
+First, we use the induced centrality perspective in context of ``spectral ranking'' \citep{boldi_vigna14}; secondly, we look not at the difference that removing a node in the graph makes for a global property of the graph (e.g., the sum of the centralities of \textit{all} other nodes), but by restricting it to its local consenquences, namely, the difference it makes for the sum of the centralities of its \textit{neighbors}.
+
+Accordingly, the $\kappa$ term in Equation~\ref{eq:distinction} is given by the average status (eigenvector centrality) of $i$'s neighbors in the \textit{node-deleted subgraph} of the focal graph $G$ that excludes $i$:
 
@@
     \includegraphics[width=0.6\linewidth]{Plots/star-roles-by-size.png}
-    \caption{Enter Caption}
+    \caption{Scaled and non-scaled distinction centralities for the two node roles in the star graph.}
     \label{fig:star-scaling}
@@
 As we can see, when distinction is calculated simply as $\beta^*_i = s_i - \kappa_i$, the distinction score is a constant for the star nodes across graphs of different sizes, demonstrating insensitivity to network scaling.
-By way of contrast, when distinction is calculated as in Equation~\ref{eq:distinction}, then we observe that the distinction score of the star node increases logarithmically with network size, which is precisely what we want, as a star mediating between many peripheral nodes should be more distinct that a star mediating between just a few peripheral nodes.
+By way of contrast, when distinction is calculated as in Equation~\ref{eq:distinction}, then we observe that the distinction score of the star node increases logarithmically with network size, which is precisely what we want, as a star mediating between many peripheral nodes should be more distinct that a star mediating between just a few peripheral nodes (we elaborate on the mathematical reasons for this below).
 
@@
 
-\subsubsection{Structural Holes vs Structural Folds}
 In each model, there are seven nodes, and node 1 is the best-connected node in the network.
@@
 
-\textit{Model (a)} is a star graph where node 1 is completely connected to all other nodes, yet the other nodes share no connections.
-Under such conditions, node 1's eigenvector centrality is 1.00.
-Yet, node 1's constraint is 0.00 because, when node 1 is removed from the network, all of node 1's neighbors have no connections and thus an eigenvector centrality of 0.00.
-Table 1 displays the various measurements for each node.
+\subsubsection{Distinction in the Star Graph}
+Figure~\ref{fig:star} shows a star graph of order seven where node 1 is the central node connected to six peripheral nodes, who themselves have no other connections.
+This hub-spoke system is the simplest for exploring the linkages between distinction, status, and constraint.
+The reason for that is that, for the star node 1, $\kappa_i$ is always equal to zero.
+In other words, the star node has a minimum network constraint, given that the node-deleted subgraph obtained by removing the central node from the star graph is a disconnected, empty graph, where the status of the peripheral nodes collapses to zero, meaning that the star node's distinction score reduces to:
+
+\begin{equation}
+    \beta_1 = \alpha s_1
+    \label{eq:distinction-star1}
+\end{equation}
+
+In a star graph, $s_1$ is a constant regardless of the order of the graph (e.g., number of peripheral nodes).
+This means that differences in the distinction of the central nodes across star graphs of different orders are wholly driven by $\alpha$.
+Note also that if we forgo scaling and set $\alpha = 1$ in Equation~\ref{eq:distinction}, then distinction reduces to status ($\beta_1 = s_1$) and therefore the distinction of the star node fails to scale with increasing network size (see Figure~\ref{fig:star-scaling}).
+
+Further note that the average constraint of the star graph is also a constant, equal to $\left(s_1-\frac{s_1}{N}\right)$, where $N$ is the number of nodes in the graph.
+Substituting this expression for $\alpha$ in Equation~\ref{eq:distinction-star1}, gives us the distinction score for the central node in the star graph:
+
+\begin{equation}
+    \beta_1 =\frac{s_1^2-\frac{s_1^2}{N}}{\bar{\mathbf{s}}}
+    \label{eq:distinction-star1}
+\end{equation}
+
+This means that in the star graph, the central node's distinction is proportional to the square of its status score minus the same score divided by the network size, divided by the average status in the network, which declines (at a decreasing rate) as network size increases, as shown in Figure~\ref{fig:star-scaling}.
+Thus, the distinction of the star node increases at a decreasing rate governed by the size of the graph $N$, as also shown in Figure~\ref{fig:star-scaling}.
+
+Similarly, for every peripheral node $j$, the constraint is also a constant and is equal to the status score of the central node $s_1$.
+Thus, for the peripheral nodes in a star graph, Equation~\ref{eq:distinction} becomes:
+
+\begin{equation}
+    \beta_j = \alpha s_j - s_1
+    \label{eq:distinction-star}
+\end{equation}
+
+However, as we noted, the average constraint of the star graph is a function of the status of the central node and the size of the graph, which means that the above becomes:
+
+\begin{equation}
+    \beta_j = \left[\frac{\left(1-\frac{1}{N}\right)s_1}{\bar{\mathbf{s}}}\right]s_j-s_1 = \left[\frac{s_1 - \frac{s_1}{N}}{\bar{\mathbf{s}}}\right]s_j - s_1 = \left[\frac{s_1 s_j - \frac{s_1 s_j}{N}}{\bar{\mathbf{s}}} \right] - s_1
+    \label{eq:distinction-star}
+\end{equation}
+
 The hub of a star graph thus has the maximum possible distance between status and constraint.
 However, with additional spokes added to a star graph, the scalar adjusted distinction measure increases.
-The hub of a star graph with seven spokes is more distinct than a hub with six, allowing a degree of comparability across networks.
-A network composed of a dyad would have a scalar adjusted distinction of 0.00 because the average constraint is 0.
-Distinction becomes a meaningful phenomenon only in networks of three or more nodes.
+The hub of a star graph with seven spokes is more distinct than a hub with six, allowing a degree of comparability across networks.\footnote{A network composed of a dyad would have a scalar adjusted distinction of 0.00 because the average constraint is 0.
+Distinction becomes a meaningful phenomenon only in networks of three or more nodes.}
 

### 2025-07-21 manuscript.tex
new

@@
 
-Another advantage of rescaling the $s_i$ component of equation~\ref{eq:distinction} is that it makes the distinction score of key nodes in the graph sensitive to network scaling, so that it increases when peripheral actors are added to the network.
-For instance, Figure~\ref{fig:star-scaling} illustrates the centrality score for star and peripheral nodes in star graphs of varying sizes.
+Another advantage of rescaling the $s_i$ component of equation~\ref{eq:distinction} is that it makes the distinction score of key nodes in the graph sensitive to network size, so that it increases for the most distinct (central) node when peripheral actors are added to the network.
+For instance, Figure~\ref{fig:star-scaling} illustrates the centrality score for central and peripheral nodes in star graphs of varying sizes.
 As we can see, when distinction is calculated simply as $\beta^*_i = s_i - \kappa_i$, the distinction score is a constant for the star nodes across graphs of different sizes, demonstrating insensitivity to network scaling.
@@
     \beta_1 =\frac{s_1^2-\frac{s_1^2}{N}}{\bar{\mathbf{s}}}
-    \label{eq:distinction-star1}
+    \label{eq:distinction-star2}
 \end{equation}
@@
 Thus, the distinction of the star node increases at a decreasing rate governed by the size of the graph $N$, as also shown in Figure~\ref{fig:star-scaling}.
+
+The hub of a star graph thus has the maximum possible distance between status and constraint.
+However, with additional spokes added to a star graph, the scalar adjusted distinction measure increases.
+The hub of a star graph with seven spokes is more distinct than a hub with six, allowing a degree of comparability across networks.\footnote{Nodes in a graph composed of a single dyad would have a scalar adjusted distinction of 0.00 because the average constraint is 0.
+Distinction becomes a meaningful phenomenon only in networks of three or more nodes.}
+
+\input{Tabs/star}
 
@@
     \beta_j = \alpha s_j - s_1
-    \label{eq:distinction-star}
+    \label{eq:distinction-star3}
 \end{equation}
 
-However, as we noted, the average constraint of the star graph is a function of the status of the central node and the size of the graph, which means that the above becomes:
+Substituting Equation~\ref{eq:distinction-star1} into Equation~\ref{eq:distinction-star3} we obtain:
 
 \begin{equation}
-    \beta_j = \left[\frac{\left(1-\frac{1}{N}\right)s_1}{\bar{\mathbf{s}}}\right]s_j-s_1 = \left[\frac{s_1 - \frac{s_1}{N}}{\bar{\mathbf{s}}}\right]s_j - s_1 = \left[\frac{s_1 s_j - \frac{s_1 s_j}{N}}{\bar{\mathbf{s}}} \right] - s_1
-    \label{eq:distinction-star}
+    \beta_j = \alpha s_j - \frac{\beta_1}{\alpha}
+    \label{eq:distinction-star4}
 \end{equation}
 
-The hub of a star graph thus has the maximum possible distance between status and constraint.
-However, with additional spokes added to a star graph, the scalar adjusted distinction measure increases.
-The hub of a star graph with seven spokes is more distinct than a hub with six, allowing a degree of comparability across networks.\footnote{A network composed of a dyad would have a scalar adjusted distinction of 0.00 because the average constraint is 0.
-Distinction becomes a meaningful phenomenon only in networks of three or more nodes.}
+Which tells us that the distinction of the peripheral node in the star graph is proportional to its own (scale) status, discounted by the distinction of the star node divided by the same scaling factor.
+
+\begin{figure}[ht!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/star.png}
+            \caption{Star Graph}
+            \label{fig:star}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle.png}
+            \caption{Circle Graph}
+            \label{fig:circle}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
+            \caption{Clique Graph}
+            \label{fig:clique}
+    \end{subfigure}
+    \label{fig:star-circle-clique}
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+\end{figure}
+
+\input{Tabs/circle}
+
+\subsubsection{Distinction in the Circle and Clique Graphs}
+
+If the star graph is the ideal-typical representation of maximum inequality (and thus distinction), the circle and clique graphs (see Figures~\ref{fig:circle} and~\ref{fig:clique}) represent the obverse case; a representation of maximum equality and thus \textit{lack} of distinction.
+In that respect, distinction should be at its theoretical minimum of zero for all nodes in these cases.
+As we can see in Tables~\ref{tab:circle} and~\ref{tab:clique} this is precisely what we observe.
+
+In the case of the circle graph, status scores be equivalent across all nodes ($s_i = 0.38$ for the circle graph of order seven shown in Figure~\ref{fig:circle}.
+Also note that whenever we remove a node from the circle graph a path graph of order $N-1$, where $N$ is the number of nodes in the original circle graph is obtained.
+The previous neighbors of the removed node become the end nodes in the node-deleted path graph.
+These two nodes will by necessity have the same status score.
+This means that the $\kappa$ component of Equation~\ref{eq:distinction} will be the same constant across all nodes, and that the average status and average constraint will also be equal to a constant, in which case Equation~\ref{eq:distinction} becomes:
+
+\begin{equation}
+    \beta_i = \left(\frac{\kappa_i}{s_i}s_i-\kappa_i\right)= (\kappa_i - \kappa_i) =0
+    \label{eq:distinction-circle}
+\end{equation}
+
+Thus, distinction is zero for all nodes in the circle graph.
+The same reasoning applies to the clique graph in which nodes have the same constant status scores as in the circle graph.
+The difference is that in this case the $\kappa$ component of Equation~\ref{eq:distinction} is obtained from the status scores of each actor in the node-deleted subgraph excluding the focal node, which is just a clique of size $N-1$ where $N$ is the number of nodes in the original clique.
+Just like in the circle graph case, however, both the $s$ and $\kappa$ components are constant across nodes, which means that the status scores cancel out by division and the constraint scores by subtraction, leaving everyone with a scaled distinction score of zero.\footnote{Because of the local nature of the $\kappa$ component in Equation~\ref{eq:distinction}, in a regular $(n, k)$ graph of order $n$ with prescribed degree $k$ across nodes, we should not expect scaled distinction to be exactly zero, since the focal nodes previous neighbors will have different status scores than the other nodes in the graph in the focal-node-deleted subgraph.
+However, we should not expect their status to be wildly different, since their degree is now only $k-1$.
+Instead, we should expect scaled distinction to fluctuate \textit{around} the zero value across nodes.
+Nevertheless, these should cancel out across nodes, and therefore we should also expect the \textit{average} distinction across nodes in a regular $(n, k)$ graph to be zero.}
+
+\input{Tabs/clique}
 
@@
      \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/star.png}
-            \caption{Star Graph}
-            \label{fig:star}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.35\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
@@
             \label{fig:sf}
-    \end{subfigure} \\
+    \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
@@
     \end{subfigure}
-
+    \label{fig:struct-folds}
     \caption{Distinction Centrality in toy graphs.
 Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-    \label{fig:toys}
 \end{figure}
@@
     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle.png}
-            \caption{Circle Graph}
-            \label{fig:circle}
-    \end{subfigure}
+
     \begin{subfigure}[b]{0.3\textwidth}
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
-            \caption{Clique Graph}
-            \label{fig:clique}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
@@
 
-\input{Tabs/star}
 \input{Tabs/structfold.tex}
@@
 \input{Tabs/interclust}
-\input{Tabs/circle}
 \input{Tabs/kite}
 \input{Tabs/clique}
-\input{Tabs/wheel}
 \input{Tabs/circletriangle}

### 2025-07-21 analysis.qmd
new tabs

@@
    g10 <- g10 + edge(7,2) #wheel graph
+   g11 <- make_ring(8) #circle graph
+   g11 <- delete_vertices(g11, 8) #path graph
 ```
@@
    dev.off()
+   png(here("Plots", "Toys", "path.png"))
+   plot.graph.norm(g11, l = "kk")
+   dev.off()
 ```
@@
    label = "star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for star graph.")
+   caption = "Distinction centrality scores for the star graph.")
    tab.cent(distinction(g2), name = "structfold", 
    label = "sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for structural fold graph.")
+   caption = "Distinction centrality scores for the structural fold graph.")
    tab.cent(distinction(g3), name = "intraclust", 
    label = "intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
-   caption = "Distinction centrality scores for intra-connected clusters graph.")
+   caption = "Distinction centrality scores for the intra-connected clusters graph.")
    tab.cent(distinction(g4), name = "interclust", 
    label = "inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
-   caption = "Distinction centrality scores for inter-connected clusters graph.")
+   caption = "Distinction centrality scores for the inter-connected clusters graph.")
    tab.cent(distinction(g5), name = "circle", 
    label = "circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for circle graph.")
+   caption = "Distinction centrality scores for the circle graph.")
    tab.cent(distinction(g6), name = "circletriangle", 
    label = "circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
-   caption = "Distinction centrality scores for circle graph with triangle.")
+   caption = "Distinction centrality scores for the circle graph with triangle.")
    tab.cent(distinction(g7), name = "circlelong", 
    label = "circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
-   caption = "Distinction centrality scores for circle graph with long tie.")
+   caption = "Distinction centrality scores for the circle graph with long tie.")
    tab.cent(distinction(g8), name = "clique", 
    label = "clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for clique graph.")
+   caption = "Distinction centrality scores for the clique graph.")
    tab.cent(distinction(g9), name = "kite", 
    label = "kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
-   caption = "Distinction centrality scores for kite graph.")
+   caption = "Distinction centrality scores for the kite graph.")
    tab.cent(distinction(g10), name = "wheel", 
    label = "wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for wheel graph.")
-
+   caption = "Distinction centrality scores for the wheel graph.")
+   tab.cent(distinction(g11), name = "path", 
+   label = "path", rownames = c("1, 7", "2, 6", "3, 5", "4"),
+   caption = "Distinction centrality scores for the path graph.")
 ```

### 2025-07-21 analysis.qmd
ooof

@@
    source(here("Functions", "plot.graph.norm.R"))
-   source(here("Functions", "tab.cent.R"))
 ```

### 2025-07-21 Functions/tab.cent.R

@@ -6,12 +6,12 @@ tab.cent <- function(x,
       rownames) { 
 library(kableExtra)
 library(dplyr)
-x <- distinct(x[, 2:6])
+x <- distinct(x[, 3:6])
 x <- cbind(rownames, x)
 t <- kbl(x, 
       format = "latex", booktabs = TRUE, linesep = "",
       digits = d, row.names = FALSE,
-      col.names = c("Nodes", "Distinction", "S-Distinction", "Status", "Constraint", "Scalar"),
+      col.names = c("Nodes", "$\\beta_i$", "$s_i$", "$\\kappa_i$", "$\\alpha$"),
       caption = caption, label = label
       ) %>% 
       kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 

### 2025-07-21 Functions/tab.cent.R
now we are talking

@@ -12,7 +12,7 @@ t <- kbl(x,
       format = "latex", booktabs = TRUE, linesep = "",
       digits = d, row.names = FALSE,
       col.names = c("Nodes", "$\\beta_i$", "$s_i$", "$\\kappa_i$", "$\\alpha$"),
-      caption = caption, label = label
+      caption = caption, label = label, escape = FALSE
       ) %>% 
       kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
       save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))

### 2025-07-26 manuscript.tex
Updates from Overleaf

@@
 
-Thus, distinction is zero for all nodes in the circle graph.
+Thus, the distinction is zero for all nodes in the circle graph.
 The same reasoning applies to the clique graph in which nodes have the same constant status scores as in the circle graph.
-The difference is that in this case the $\kappa$ component of Equation~\ref{eq:distinction} is obtained from the status scores of each actor in the node-deleted subgraph excluding the focal node, which is just a clique of size $N-1$ where $N$ is the number of nodes in the original clique.
+The difference is that in this case the $\kappa$ component of Equation~\ref{eq:distinction} is obtained from the status scores of each actor in the node-deleted subgraph, excluding the focal node, which is just a clique of size $N-1$ where $N$ is the number of nodes in the original clique.
 Just like in the circle graph case, however, both the $s$ and $\kappa$ components are constant across nodes, which means that the status scores cancel out by division and the constraint scores by subtraction, leaving everyone with a scaled distinction score of zero.\footnote{Because of the local nature of the $\kappa$ component in Equation~\ref{eq:distinction}, in a regular $(n, k)$ graph of order $n$ with prescribed degree $k$ across nodes, we should not expect scaled distinction to be exactly zero, since the focal nodes previous neighbors will have different status scores than the other nodes in the graph in the focal-node-deleted subgraph.
@@
 This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also
-increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
 
@@
 %Triadic closure 3 versions
+\textit Triadic closure is an observed regularity in which a connection is likely to form between two actors who, although not originally connected, are first connected to a common alter (Simmel 1908).
+In essence, friends of friends have an increased likelihood of also becoming friends.
+The causes of this regularity, and the reasons for its occasional failure, are largely based on consideration of valence.
+Positive or negative affect drive the resulting triadic relations.
+The original consideration was for the cognitive balance of the individual, or the psychological congruity of affect by an individual for two objects that they see as causally connected.
+As such, the valenced relationship of any three actors are brought into combined consideration because any two are considered affectively combined through their joint combination as "the parts of a causal unit (Heider 1946:107)."
+
+\citep{huang2018will}
+\citep{yoon2013exchange}
+\citep{mollenhorst2011shared} 
+\citep{feld1981focused}
+\citep{feld1982social}
+
 Psychology

### 2025-07-26 manuscript.tex
Updates from Overleaf

@@
 \begin{abstract}	
-This paper introduces the concept of \textit{distinction centrality}, developing a network metric designed to capture it.
+This paper introduces the concept of network \textit{distinction} and develops a relational metric that captures it.
 The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, where other actors and their actions provide opportunities and constraints to maximize social positioning.
@@
 Still, such a correlation is not guaranteed at the individual level, even if it is relevant at the field level.
-
 While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}.
@@
 In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}.
-Translated to network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle is reflective of the constraints neighbors put on an actor.
+Translated into network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle reflects the constraints that neighbors impose on an actor.
 An actor with high influence is well-connected to others who can be mobilized for effective action.
@@
 In developing a broader understanding and measure of social distinction, actor-level incentives and structural impediments to action become apparent.
-When we understand the underlying motivation actors have to proactively reshape their network connections so as to achieve more distinct positions, historical patterns of network change can be better accounted for and sometimes even properly forecasted.
+When we understand the underlying motivation that actors have to proactively reshape their network connections to achieve more distinct positions, historical patterns of network change can be better accounted for and, in some cases, even properly forecasted.
 
 \subsection{Position as the Relational Basis for a Distinction Measure}
-Bourdieu's separation of distinction into habitus and position is not a sociological problem at all, but rather creates the analytical problem of how an actor's network position generates dispositions and how these dispositions create opportunities for network mobility.
+Bourdieu's separation of distinction into habitus and position is not a sociological problem in itself, but rather creates the analytical challenge of how an actor's network position generates dispositions and how these dispositions, in turn, create opportunities for network mobility.
 Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when creating a network measure of distinction, only the relational basis of position can be considered.
@@
 
-Which tells us that the distinction of the peripheral node in the star graph is proportional to its own (scale) status, discounted by the distinction of the star node divided by the same scaling factor.
+Which tells us that the distinction of the peripheral node in the star graph is proportional to its own (scaled) status, discounted by the distinction of the star node divided by the same scaling factor.
 
@@
 \input{Tabs/clique}
+%Clique addition experiment
+%Add cliques to star graph and see what happens
+%See what happens with the caveman
+
+\subsubsection{Distinction in Triadic Closure and Formation}
+
+Triadic closure is an observed regularity in which a connection is likely to form between two actors who, although not originally connected, are first connected to a common alter (Simmel 1908).
+In essence, friends of friends have an increased likelihood of also becoming friends.
+The causes of this regularity, and the reasons for its occasional failure, are largely based on consideration of valence.
+Positive or negative affect drive the resulting triadic relations.
+The original consideration was for the cognitive balance of the individual, or the psychological congruity of affect by an individual for two objects that they see as causally connected.
+As such, the valenced relationship of any three actors are brought into combined consideration because any two are considered affectively combined through their joint combination as "the parts of a causal unit (Heider 1946:107)."
+
+Beyond the cognitive congruence account of triadic closure, there is an accounting of triadic closure based on the strains new positive network connections may or may not create in existing relationships.
+Networks are sets of triads that are either actualized in connection, either positive or negative, or left unactuated.
+Actualization is largely predicated on propinquity, and the valence of theoretically possible ties never rises to the concern of a social question \citep{feld1981focused, feld1982social, mollenhorst2011shared}.
+However, in a contested context where ties are either positive or negative, triadic closure becomes a matter of not betraying one's friends by associating with one of their enemies, and of solidifying social alliances (Bearman 1993).
+However, triadic closure with a friend's friend signals commitment.
+The endorsement effect of triadic balance, that betrayal creates two relational problems rather than one, reinforces the surety of the actors \citep{yoon2013exchange}.
+
+In addition to these explanations, the distinction measure also reveals the utility of a distinction based theory of triadic closure.
+Figure 3 \textit{Model (a)} and Table 4 present a graph and corresponding measures of near-neighbor triadic closure.
+The distinction of nodes 1 and 6 increases to .106, compared to 0 in the circle graph, while all other nodes fall below 0 due to the reverberating effects of the new connection.
+Notably, node 7 increases in eigenvector status from the combination, but overall decrease in scaled distinction due to the tie.
+While both eigenvector centrality and scaled distinction would predict tie formation in this simplified social structure, the scaled distinction measure would find that Node 7 would actually lose out in some ways from this arrangement.
+This matches with findings that initial connections do weaken when triadic closure occurs \citep{huang2018will}, consistent with a reaction to the increased constraint placed on the closure broker.
+This example demonstrates the fragility of the circle graph as an equality condition in a distinction-based theoretical framework, as there are opportunities for mutual increases in distinction through triadic closure.
+Beyond questions of balancing valence as is the current framework for understanding triadic closure, a distinction-based theoretical framework can explain the propensity towards triadic closure, but also its failure to form depending on the initial patterning of relationships.
+
+Figure 3 \textit{Model (b)} and Table 5 present a graph and corresponding measures of a long tie formation spanning the circle graph.
+The connected nodes 4 and 7 both have distinction maximizing incentives to form a tie, but notably their scaled distinction increases more when they close triadically with a near neighbor.
+Thus, under sparse network conditions, the gains in status from local consolidation outweigh the distinction gains from increased autonomy.
+
+%actually creates hierarchy, you only one tie to create 4 levels of hierarchy
+%the pyramid is the natural form of organization
+%agents form ties with maximization, then you grow transitivty 
+%two conditions, inital local ties matter more, with density, long ties matter more
+
+%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
+%folds vs circles
+
+%kite graph-outsider breaks mechanical solidarity
+%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
+Try to get inequality in an organic solidarity system but that's unstable?
+(might have written that down wrong).
+%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
+%actually anthropologists ruined everything in the villages
+%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
+%theory of subgraph cliques rather than full graph as clique
+
+%gets close to 0 negative, with non-normalized eigenvectors
+%if you normalize then it all works as expected
+% in the normalized kite graph, 1.0, the other get close, decreases the scalar, evs don't mean anything
+
+%college caves, BYU vs Notre Dame vs regulars
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-triangle.png}
+            \caption{Circle Graph with Closure}
+            \label{fig:circleplus}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-long.png}
+            \caption{Circle Graph with Long Tie}
+            \label{fig:circleplus}
+    \end{subfigure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
+            \caption{Kite Graph}
+            \label{fig:kite}
+    \end{subfigure}
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+    \label{fig:toys}
+\end{figure}
+
+\input{Tabs/circletriangle}
+\input{Tabs/circlelong}
+\input{Tabs/kite}
+
+\input{Tabs/structfold.tex}
+\input{Tabs/intraclust}
+\input{Tabs/interclust}
+\input{Tabs/clique}
+
+\subsubsection{Distinction and Brokerage}
 
@@
 
-\subsubsection{Circle Graphs and Triadic Closure}
-%NOTES FROM 7|19|25 Meeting
-%***Triadic closure as distinction maximization*** 
+\subsubsection{Long Ties and Hierarchy}
+
 %Strogatz is random, preferential attachment of closure
 %Status homophilous (enh) attachment vs preferential vs random 
-%I wonder how much of balance theory is really just distinction maximization?
-%Non psychological theory polarity
-
-%Triadic closure 3 versions
-\textit Triadic closure is an observed regularity in which a connection is likely to form between two actors who, although not originally connected, are first connected to a common alter (Simmel 1908).
-In essence, friends of friends have an increased likelihood of also becoming friends.
-The causes of this regularity, and the reasons for its occasional failure, are largely based on consideration of valence.
-Positive or negative affect drive the resulting triadic relations.
-The original consideration was for the cognitive balance of the individual, or the psychological congruity of affect by an individual for two objects that they see as causally connected.
-As such, the valenced relationship of any three actors are brought into combined consideration because any two are considered affectively combined through their joint combination as "the parts of a causal unit (Heider 1946:107)."
-
-\citep{huang2018will}
-\citep{yoon2013exchange}
-\citep{mollenhorst2011shared} 
-\citep{feld1981focused}
-\citep{feld1982social}
-
-Psychology
-Polarity, valenced ties 
-Status distinction
-
-%Knights of the Round table, why equality conditions are fragile
-%kite graph-outsider breaks mechanical solidarity
-%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
-Try to get inequality in an organic solidarity system but that's unstable?
-(might have written that down wrong).
-%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
-%actually anthropologists ruined everything in the villages
-%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
-%theory of subgraph cliques rather than full graph as clique
 %*Tie that cuts the longest shortest path Science, 
@@
 
-%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
-%folds vs circles
-%college caves, BYU vs Notre Dame vs regulars
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-triangle.png}
-            \caption{Circle Graph with Closure}
-            \label{fig:circleplus}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-long.png}
-            \caption{Circle Graph with Long Tie}
-            \label{fig:circleplus}
-    \end{subfigure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
-            \caption{Kite Graph}
-            \label{fig:kite}
-    \end{subfigure}
-    \caption{Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-    \label{fig:toys}
-\end{figure}
-
-\input{Tabs/structfold.tex}
-\input{Tabs/intraclust}
-\input{Tabs/interclust}
-\input{Tabs/kite}
-\input{Tabs/clique}
-\input{Tabs/circletriangle}
-\input{Tabs/circlelong}
-
-%Clique addition experiment
-
-%Add cliques to star graph and see what happens
-
-%See what happens with the caveman
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.9\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/tree-examples.png}
-            \caption{Example of tree graphs with different numbers of branches for the star node.}
-            \label{fig:tree-examples}
-    \end{subfigure} \\
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/broker-tree-roles-by-nbranches.png}
-            \caption{Evolution of distinction scores by number of branches for the star node.}
-            \label{fig:broker-tree-roles}
-    \end{subfigure}
-    \caption{.}
-    \label{fig:toys}
-\end{figure}
-
-\subsubsection{Long Ties and Hierarchy}
 This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs.
@@
     \label{fig:Evolving Political Network}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+    \begin{subfigure}[b]{0.9\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/tree-examples.png}
+            \caption{Example of tree graphs with different numbers of branches for the star node.}
+            \label{fig:tree-examples}
+    \end{subfigure} \\
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/broker-tree-roles-by-nbranches.png}
+            \caption{Evolution of distinction scores by number of branches for the star node.}
+            \label{fig:broker-tree-roles}
+    \end{subfigure}
+    \caption{.}
+    \label{fig:toys}
 \end{figure}

### 2025-07-27 manuscript.tex
Updates from Overleaf

@@
 
-\subsubsection{Distinction in Triadic Closure and Formation}
+\subsubsection{Distinction in Triadic Closure}
 
@@
 This example demonstrates the fragility of the circle graph as an equality condition in a distinction-based theoretical framework, as there are opportunities for mutual increases in distinction through triadic closure.
+Additionally, the  example of triadic closure shows that only mild additions to network ties can very quickly create stratification.
+The addition of a single connection between node 1 and 6 in Figure 3 \textit{Model (a)} stratified a network from equality into four levels of hierarchy with a single additional connection.
+
 Beyond questions of balancing valence as is the current framework for understanding triadic closure, a distinction-based theoretical framework can explain the propensity towards triadic closure, but also its failure to form depending on the initial patterning of relationships.
@@
 The connected nodes 4 and 7 both have distinction maximizing incentives to form a tie, but notably their scaled distinction increases more when they close triadically with a near neighbor.
-Thus, under sparse network conditions, the gains in status from local consolidation outweigh the distinction gains from increased autonomy.
+Thus, under sparse overall network conditions, the gains in status from local consolidation outweigh the distinction gains from increased autonomy.
+Conversely, once dense local conditions prevail, long ties can become more valuable as the gain in autonomy outweighs the marginal gains in status.
+However, the unique topography of networks requires careful consideration in each case.
 
-%actually creates hierarchy, you only one tie to create 4 levels of hierarchy
-%the pyramid is the natural form of organization
-%agents form ties with maximization, then you grow transitivty 
-%two conditions, inital local ties matter more, with density, long ties matter more
-
-%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
-%folds vs circles
-
-%kite graph-outsider breaks mechanical solidarity
-%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
-Try to get inequality in an organic solidarity system but that's unstable?
-(might have written that down wrong).
-%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
-%actually anthropologists ruined everything in the villages
-%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
-%theory of subgraph cliques rather than full graph as clique
-
-%gets close to 0 negative, with non-normalized eigenvectors
-%if you normalize then it all works as expected
-% in the normalized kite graph, 1.0, the other get close, decreases the scalar, evs don't mean anything
-
-%college caves, BYU vs Notre Dame vs regulars
+What the difference between these two examples suggests is that, based on considerations for distinction, the initial spread of social organization occurs locally through the triadic balance of near neighbors.
+This would suggest that the natural form of organizational formation is the pyramid formed from combinations of local triads that are further connected by brokers or welds creating structural folds.
+However, the transitivity created by the initial triad formation would spread quickly throughout the network, making welding structural folds a highly advantageous strategy for members of triads who could facilitate that connection, which is further explored below.
 
@@
         \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-triangle.png}
-            \caption{Circle Graph with Closure}
+            \caption{Circle Graph with Near Neighbor Closure}
             \label{fig:circleplus}
@@
             \label{fig:circleplus}
-    \end{subfigure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
-            \caption{Kite Graph}
-            \label{fig:kite}
     \end{subfigure}
@@
 
+\subsubsection{Kite Graphs and Eigenvector Normalization}
+
+%gets close to 0 negative, with non-normalized eigenvectors
+%if you normalize then it all works as expected
+% in the normalized kite graph, 1.0, the other get close, decreases the scalar, evs don't mean anything
+%computtional experiment where you make kite less dense, or size of kite
+%kite graph-outsider breaks mechanical solidarity
+%mechanical solidarity is really an outcome of the network structure (Durkheim kind of %said that but Omar said it better).
+Try to get inequality in an organic solidarity system but that's unstable?
+(might have written that down wrong).
+%mechanical solidarity benefits from the stranger. more theoretical than empirical. 
+%actually anthropologists ruined everything in the villages
+%also somewhat the Marco Polo vibe, Shogun (the violation of markers of distinction, %didn't matter), The Last Samurai
+%theory of subgraph cliques rather than full graph as clique
+%hypothesis: size of the normalization gaps is causing the differences between normalized and unnormalized.
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
+            \caption{Kite Graph}
+            \label{fig:kite}
+    \end{subfigure}
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+    \label{fig:toys}
+\end{figure}
+
 \subsubsection{Distinction and Brokerage}
 
+%welds martin2009social
+%Structural holes vs folds (need to graph out the holes)
+
+%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
+%folds vs circles
 \textit{Model (b)} presents an idealized depiction of a structural fold \citep{vedres2010structural}.
@@
     \centering
+    \begin{subfigure}[b]{0.9\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/tree-examples.png}
+            \caption{Example of tree graphs with different numbers of branches for the star node.}
+            \label{fig:tree-examples}
+    \end{subfigure} \\
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/broker-tree-roles-by-nbranches.png}
+            \caption{Evolution of distinction scores by number of branches for the star node.}
+            \label{fig:broker-tree-roles}
+    \end{subfigure}
+    \caption{.}
+    \label{fig:toys}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
      \begin{subfigure}[b]{0.45\textwidth}
@@
     \label{fig:Evolving Political Network}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.9\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/tree-examples.png}
-            \caption{Example of tree graphs with different numbers of branches for the star node.}
-            \label{fig:tree-examples}
-    \end{subfigure} \\
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/broker-tree-roles-by-nbranches.png}
-            \caption{Evolution of distinction scores by number of branches for the star node.}
-            \label{fig:broker-tree-roles}
-    \end{subfigure}
-    \caption{.}
-    \label{fig:toys}
 \end{figure}
@@
 These cultural transformations were neither inherent in the students nor the institutions, but came out of the network structure that enabled the pursuit of cultural distinction to match the newly acquired network position.
+Thus, if "liberals" are those who espouse diversity and innovation in cultural forms, to the extent that universities draw from a variety of social bases, liberal dispositions will results.
+However, if the university draws from an isolated basis, as the common educational destination of a delimited community, then the structural opportunities for cultural distinction are absent, and the culture is inherited from the isolated community.
 
@@
 While the above exploration of how network shape changes diversity in cultural distinction practices is at least informative about how understanding the network of positions structures the cultural markers of distinction.
-
-%College as inherently distinction based institution makes liberals a thing, rather than if you only draw from caves
 

### 2025-07-30 analysis.qmd
new ex who dis

@@
    g11 <- make_ring(8) #circle graph
-   g11 <- delete_vertices(g11, 8) #path graph
+   g12 <- delete_vertices(g11, 8) #path graph
+```
+
+```{r Bonacich examples}
+   g13 <- make_empty_graph(10, directed = FALSE)
+   g13 <- g13 + edge(1,2)
+   g13 <- g13 + edge(1,3)
+   g13 <- g13 + edge(1,9)
+   g13 <- g13 + edge(2,3)
+   g13 <- g13 + edge(2,10)
+   g13 <- g13 + edge(3,4)
+   g13 <- g13 + edge(4,5)
+   g13 <- g13 + edge(4,6)
+   g13 <- g13 + edge(5,10)
+   g13 <- g13 + edge(5,6)
+   g13 <- g13 + edge(6,7)
+   g13 <- g13 + edge(7,8)
+   g13 <- g13 + edge(7,9)
+   g13 <- g13 + edge(8,10)
+   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
+   g14 <- make_empty_graph(12, directed = FALSE)
+   g14 <- g14 + edge(1,2)
+   g14 <- g14 + edge(1,6)
+   g14 <- g14 + edge(1,7)
+   g14 <- g14 + edge(2,3)
+   g14 <- g14 + edge(2,10)
+   g14 <- g14 + edge(3,4)
+   g14 <- g14 + edge(3,8)
+   g14 <- g14 + edge(4,5)
+   g14 <- g14 + edge(4,11)
+   g14 <- g14 + edge(5,6)
+   g14 <- g14 + edge(5,9)
+   g14 <- g14 + edge(6,12)
+   g14 <- g14 + edge(7,8)
+   g14 <- g14 + edge(7,9)
+   g14 <- g14 + edge(8,9)
+   g14 <- g14 + edge(10,11)
+   g14 <- g14 + edge(10,12)
+   g14 <- g14 + edge(11,12)
+   plot(g14)
+```
+
+```{r Estrada examples}
+   g15 <- make_empty_graph(8, directed = FALSE)
+   g15 <- g15 + edge(1,2)
+   g15 <- g15 + edge(1,5)
+   g15 <- g15 + edge(1,8)
+   g15 <- g15 + edge(2,3)
+   g15 <- g15 + edge(2,8)
+   g15 <- g15 + edge(3,4)
+   g15 <- g15 + edge(3,6)
+   g15 <- g15 + edge(4,5)
+   g15 <- g15 + edge(4,7)
+   g15 <- g15 + edge(5,6)
+   g15 <- g15 + edge(6,7)
+   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
+   distinction(g15, norm = TRUE)
+```
+
+```{r}
+   n <- 5
+   g9 <- make_full_graph(n, directed = FALSE)
+   g9 <- add_vertices(g9, 1)
+   g9 <- g9 + edge(n, n+1) # kite
+   distinction(g9, norm = FALSE)
 ```

### 2025-07-30 Functions/distinction.R

@@ -32,6 +32,9 @@ distinction <- function(x, norm = FALSE) {
       if (c == TRUE & e == FALSE) { #connected non-empty node-deleted graph
          A <- as.matrix(as_adjacency_matrix(x.d))
          s.a <- abs(eigen(A)$vectors[, 1])
+         if (vcount(x.d) == 1) {
+            s.a <- 0 
+            }
          names(s.a) <- labs[-which(labs == i)]
          if (norm == TRUE) {s.a <- norm.max(s.a)} #normalizing by maximum
          s.a <- s.a[j]

### 2025-07-30 manuscript.tex

@@
 Notably, node 7 increases in eigenvector status from the combination, but overall decrease in scaled distinction due to the tie.
+This example demonstrates the fragility of the circle graph as an equality condition in a distinction-based theoretical framework, as there are opportunities for mutual increases in distinction through triadic closure.
 While both eigenvector centrality and scaled distinction would predict tie formation in this simplified social structure, the scaled distinction measure would find that Node 7 would actually lose out in some ways from this arrangement.
-This matches with findings that initial connections do weaken when triadic closure occurs \citep{huang2018will}, consistent with a reaction to the increased constraint placed on the closure broker.
-This example demonstrates the fragility of the circle graph as an equality condition in a distinction-based theoretical framework, as there are opportunities for mutual increases in distinction through triadic closure.
-Additionally, the  example of triadic closure shows that only mild additions to network ties can very quickly create stratification.
-The addition of a single connection between node 1 and 6 in Figure 3 \textit{Model (a)} stratified a network from equality into four levels of hierarchy with a single additional connection.
-
+This matches with findings that often initial connections do weaken when triadic closure occurs \citep{huang2018will}, consistent with a reaction to the increased constraint placed on the closure broker.
+However, the actual incentives and consequences for each of the nodes in a triadic closure will be dependent on the overall existing network structure.
+Node 7 is worse off because of the structure of the circle graph, not necessarily because in all conditions Node 7 will be worse off.
+If Node 7 is actually highly central to the graph, near neighbor triadic closure can be distinction increasing.
 Beyond questions of balancing valence as is the current framework for understanding triadic closure, a distinction-based theoretical framework can explain the propensity towards triadic closure, but also its failure to form depending on the initial patterning of relationships.
@@
 However, the transitivity created by the initial triad formation would spread quickly throughout the network, making welding structural folds a highly advantageous strategy for members of triads who could facilitate that connection, which is further explored below.
+Additionally, the example of triadic closure shows that only mild additions to network ties can very quickly create stratification.
+The addition of a single connection between node 1 and 6 in Figure 3 \textit{Model (a)} stratified a network from equality into four levels of hierarchy with a single additional connection.
 

### 2025-07-31 analysis.qmd
a bucha

--- 2025-07-21 analysis.qmd
@@
 ```{r Toy Examples}
+   source(here("Functions", "distinction.R"))
    g1 <- make_star(7, mode = "undirected") # star graph
+   distinction(g5, norm = "eig")
    g2 <- g1 + edge(2,3)
@@
    g10 <- g10 + edge(7,2) #wheel graph
-   g11 <- make_ring(8) #circle graph
+   g11 <- make_ring(8) 
    g11 <- delete_vertices(g11, 8) #path graph
+   source(here("Functions", "distinction.R"))
+   all.dis <- function(x) {
+      distinct <- list()
+      distinct[[1]] <- distinction(x)
+      distinct[[2]] <- distinction(x, norm = "one")
+      distinct[[3]] <- distinction(x, norm = "eig")
+      return(distinct)
+      }
+   all.dis(g9)
+```
+
+```{r Bonacich examples}
+   g13 <- make_empty_graph(10, directed = FALSE)
+   g13 <- g13 + edge(1,2)
+   g13 <- g13 + edge(1,3)
+   g13 <- g13 + edge(1,9)
+   g13 <- g13 + edge(2,3)
+   g13 <- g13 + edge(2,10)
+   g13 <- g13 + edge(3,4)
+   g13 <- g13 + edge(4,5)
+   g13 <- g13 + edge(4,6)
+   g13 <- g13 + edge(5,10)
+   g13 <- g13 + edge(5,6)
+   g13 <- g13 + edge(6,7)
+   g13 <- g13 + edge(7,8)
+   g13 <- g13 + edge(7,9)
+   g13 <- g13 + edge(8,10)
+   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
+   g14 <- make_empty_graph(12, directed = FALSE)
+   g14 <- g14 + edge(1,2)
+   g14 <- g14 + edge(1,6)
+   g14 <- g14 + edge(1,7)
+   g14 <- g14 + edge(2,3)
+   g14 <- g14 + edge(2,10)
+   g14 <- g14 + edge(3,4)
+   g14 <- g14 + edge(3,8)
+   g14 <- g14 + edge(4,5)
+   g14 <- g14 + edge(4,11)
+   g14 <- g14 + edge(5,6)
+   g14 <- g14 + edge(5,9)
+   g14 <- g14 + edge(6,12)
+   g14 <- g14 + edge(7,8)
+   g14 <- g14 + edge(7,9)
+   g14 <- g14 + edge(8,9)
+   g14 <- g14 + edge(10,11)
+   g14 <- g14 + edge(10,12)
+   g14 <- g14 + edge(11,12)
+```
+
+```{r Estrada examples}
+   g15 <- make_empty_graph(8, directed = FALSE)
+   g15 <- g15 + edge(1,2)
+   g15 <- g15 + edge(1,5)
+   g15 <- g15 + edge(1,8)
+   g15 <- g15 + edge(2,3)
+   g15 <- g15 + edge(2,8)
+   g15 <- g15 + edge(3,4)
+   g15 <- g15 + edge(3,6)
+   g15 <- g15 + edge(4,5)
+   g15 <- g15 + edge(4,7)
+   g15 <- g15 + edge(5,6)
+   g15 <- g15 + edge(6,7)
+   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
+   g16 <- make_full_graph(9, directed = FALSE)
+   g16 <- g16 - edge("1|6")
+   g16 <- g16 - edge("1|5")
+   g16 <- g16 - edge("2|4")
+   g16 <- g16 - edge("2|9")
+   g16 <- g16 - edge("3|6")
+   g16 <- g16 - edge("3|8")
+   g16 <- g16 - edge("4|7")
+   g16 <- g16 - edge("5|8")
+   g16 <- g16 - edge("7|9") #Fig 1(b) https://doi.org/10.1103/PhysRevE.71.056103
 ```
@@
 ```{r Toy Networks Plots}
+   source(here("Functions", "distinction.R"))
    source(here("Functions", "plot.graph.norm.R"))
@@
    plot.graph.norm(g11, l = "kk")
+   dev.off()
+   source(here("Functions", "plot.graph.cat.R"))
+   png(here("Plots", "Toys", "bonacich1.png"))
+   plot.graph.cat(g13, l = "circle")
+   dev.off()
+   png(here("Plots", "Toys", "bonacich2.png"))
+   plot.graph.cat(g14, l = "circle")
+   dev.off()
+   png(here("Plots", "Toys", "estrada1.png"))
+   plot.graph.cat(g15, l = "circle")
+   dev.off()
+   png(here("Plots", "Toys", "estrada2.png"))
+   plot.graph.cat(g16, l = "circle")
    dev.off()

### 2025-07-31 Functions/distinction.R

@@ -1,65 +1,52 @@
-distinction <- function(x, norm = FALSE) { 
-   library(igraph)
-   V <- vcount(x)
-   no.labels <- is.null(V(x)$name)
-   if (no.labels == TRUE) {
-      V(x)$name <- 1:V
-      names <- V(x)$name 
-      }
-   if (no.labels == FALSE) {
-      names <- V(x)$name 
-      V(x)$name <- 1:V
-      }
-   norm.max <- function(x) {return(x/max(x))} #normalizing function
-   A <- as.matrix(as_adjacency_matrix(x))
-   nc <- components(x)$no #checking for disconnected graph
-   if (nc > 1) {
-      s <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
-      }
-   else if (nc == 1) {
-      s <- abs(eigen(A)$vectors[, 1])
-      }
-   if (norm == TRUE) {s <- norm.max(s)} #normalizing by maximum
-   names(s) <- V(x)$name
-   d <- rep(V, 0) # initializing distinction vector
-   u <- rep(V, 0) # initializing constraint vector
-   labs <- V(x)$name
-   for (i in as.character(V(x)$name)) {
-      j <- names(neighbors(x, i))
-      x.d <- delete_vertices(x, i)
-      c <- is_connected(x.d) #checking for connectedness of node-deleted subgraph
-      e <- ecount(x.d) == 0 #checking for emptiness of node-deleted subgraph
-      if (c == TRUE & e == FALSE) { #connected non-empty node-deleted graph
-         A <- as.matrix(as_adjacency_matrix(x.d))
-         s.a <- abs(eigen(A)$vectors[, 1])
-         if (vcount(x.d) == 1) {
-            s.a <- 0 
-            }
-         names(s.a) <- labs[-which(labs == i)]
-         if (norm == TRUE) {s.a <- norm.max(s.a)} #normalizing by maximum
-         s.a <- s.a[j]
-         } #end main if
-      else if (c == FALSE & e == TRUE) { #empty node-deleted graph
-         s.a <- 0
-         } #end first else 
-      else if (c == FALSE & e == FALSE) { #disconnected non-empty node-deleted graph
-         A <- as.matrix(as_adjacency_matrix(x.d))
-         nc <- components(x.d)$no         
-         s.a <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
[…]

### 2025-07-31 Functions/distinction.old.R

@@ -1,43 +1,56 @@
-distinction.old <- function(x) { 
+distinction <- function(x, norm = FALSE) { 
    library(igraph)
-   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
    V <- vcount(x)
-   if (has.labels == 0) {
+   no.labels <- is.null(V(x)$name)
+   if (no.labels == TRUE) {
       V(x)$name <- 1:V
       names <- V(x)$name 
       }
-   if (has.labels == 1) {
+   if (no.labels == FALSE) {
       names <- V(x)$name 
       V(x)$name <- 1:V
       }
-   s <- eigen_centrality(x)$vector
-   d <- rep(V, 0)
-   u <- rep(V, 0)
+   norm.max <- function(x) {return(x/max(x))} #normalizing function
+   A <- as.matrix(as_adjacency_matrix(x))
+   nc <- components(x)$no #checking for disconnected graph
+   if (nc > 1) {
+      s <- rowSums(abs(eigen(A)$vectors[, 1:nc]))
+      }
+   else if (nc == 1) {
+      s <- abs(eigen(A)$vectors[, 1])
+      }
+   if (norm == TRUE) {s <- norm.max(s)} #normalizing by maximum
+   names(s) <- V(x)$name
+   d <- rep(V, 0) # initializing distinction vector
+   u <- rep(V, 0) # initializing constraint vector
+   labs <- V(x)$name
    for (i in as.character(V(x)$name)) {
       j <- names(neighbors(x, i))
       x.d <- delete_vertices(x, i)
-      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
-      e <- as.numeric(ecount(x.d) == 0) #checking for empty
-      if (c == 1 & e == 0) { #connected non-empty graph
-         s.a <- eigen_centrality(x.d)$vector[j]
-         } #end if
-      else if (c == 0 & e == 1) { #empty graph
+      c <- is_connected(x.d) #checking for connectedness of node-deleted subgraph
+      e <- ecount(x.d) == 0 #checking for emptiness of node-deleted subgraph
+      if (c == TRUE & e == FALSE) { #connected non-empty node-deleted graph
+         A <- as.matrix(as_adjacency_matrix(x.d))
+         s.a <- abs(eigen(A)$vectors[, 1])
+         if (vcount(x.d) == 1) {
+            s.a <- 0 
+            }
+         names(s.a) <- labs[-which(labs == i)]
[…]

### 2025-07-31 Functions/distinction.vold.R

@@ -1,0 +1,52 @@
+distinction.old <- function(x) { 
+   library(igraph)
+   has.labels <- as.numeric(is.null(V(x)$name) == FALSE)
+   V <- vcount(x)
+   if (has.labels == 0) {
+      V(x)$name <- 1:V
+      names <- V(x)$name 
+      }
+   if (has.labels == 1) {
+      names <- V(x)$name 
+      V(x)$name <- 1:V
+      }
+   s <- eigen_centrality(x)$vector
+   d <- rep(V, 0)
+   u <- rep(V, 0)
+   for (i in as.character(V(x)$name)) {
+      j <- names(neighbors(x, i))
+      x.d <- delete_vertices(x, i)
+      c <- as.numeric(is_connected(x.d) == TRUE) #checking for connectedness
+      e <- as.numeric(ecount(x.d) == 0) #checking for empty
+      if (c == 1 & e == 0) { #connected non-empty graph
+         s.a <- eigen_centrality(x.d)$vector[j]
+         } #end if
+      else if (c == 0 & e == 1) { #empty graph
+         s.a <- 0
+         } #end first else 
+      else if (c == 0 & e == 0) { #disconnected non-empty graph
+         C <- components(x.d)$membership
+         names(C) <- V(x)$name[-as.numeric(i)]
+         s.a <- rep(0, length(C))
+         for (k in unique(C)) {
+            sub.g <- subgraph(x.d, names(which(C == k)))
+            if (vcount(sub.g) > 1) {
+               s.a[which(C == k)] <- eigen_centrality(sub.g)$vector
+               }
+            }
+         names(s.a) <- names(C)
+         s.a <- s.a[j]
+         } #end second else
+      u[i] <- sum(s.a)/length(s.a) #i's average neighbor centrality in node deleted subgraph
+      d[i] <- s[i] - u[i] #i's distinction centrality
+      } #end i for loop
+   d[is.na(d)] <- 0
+   u[is.na(u)] <- 0
+   scalar <- mean(u)/mean(s)
+   sd <- (s*scalar) - u
+   dat <- data.frame(d = d, sd = sd, s = s, u = u, scalar = scalar)
+   dat <- round(dat, 4)
+   dat <- data.frame(n = names, dat)
+   rownames(dat) <- 1:nrow(dat)
+   return(dat)
+} #end function

### 2025-07-31 Functions/plot.graph.cat.R

@@ -1,11 +1,8 @@
-plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8, c = 0.05) { #plotting function
+plot.graph.cat<- function(x, l = "kk", vs = 16, ts = 8) { #plotting function
   library(ggraph)
   d <- distinction(x)[, 3]
-  nc <- vector(mode = "character", length = length(d))
-  nc[which(d < -c)] <- "tan2"
-  nc[which(d > c)] <- "blue"
-  nc[which(d >=-c & d <= c)] <- "purple"
-  nc[which(d == max(d) & d >= c)] <- "red"
+  cols <- paletteer::paletteer_d("RColorBrewer::Set1")
+  nc <- factor(d, labels = cols[1:length(unique(d))])
   if (is.null(V(x)$name) == TRUE) {
       n <- 1:vcount(x)
       tc <- "white"

### 2025-07-31 analysis.qmd
fixed func

@@
    g1 <- make_star(7, mode = "undirected") # star graph
-   distinction(g5, norm = "eig")
    g2 <- g1 + edge(2,3)
@@
    g11 <- delete_vertices(g11, 8) #path graph
+```
+
+```{r}
    source(here("Functions", "distinction.R"))
-   all.dis <- function(x) {
-      distinct <- list()
-      distinct[[1]] <- distinction(x)
-      distinct[[2]] <- distinction(x, norm = "one")
-      distinct[[3]] <- distinction(x, norm = "eig")
-      return(distinct)
-      }
-   all.dis(g9)
+   distinction(g5, norm = "abs")
 ```
@@
    b <- make.stars(33)
-   c <- lapply(b, distinction)
+   c <- lapply(b, distinction, norm = "abm")
    ds.s <- sapply(c, function(x) {x[1, 3]})
@@
 ```{r}
+   c <- lapply(b, distinction, norm = "abm")
    d.s <- sapply(c, function(x) {x[1, 3]})

### 2025-07-31 Functions/distinction.R

@@ -1,43 +1,46 @@
 distinction <- function(x, norm = "max", digits  = 4) { 
   require(igraph) #need igraph
-  if (is.null(V(x)$name) == TRUE) {
-    V(x)$name <- 1:vcount(x)
+  n <- vcount(x)
+  if (is.null(V(x)$name) == 1) {
+    V(x)$name <- 1:n
     names <- V(x)$name 
     }
-  if (is.null(V(x)$name) == FALSE) {
+  if (is.null(V(x)$name) == 0) {
     names <- V(x)$name 
-    V(x)$name <- 1:vcount(x)
+    V(x)$name <- 1:n
     }
-  norm.max <- function(x) {return(x^2/max(x^2))} #max normalizing function
-  norm.one <- function(x) {return(x^2)}
-  norm.eig <- function(x, a) {return(x^2*a)}
+  norm.max <- function(x) {return(x^2/max(x^2))} #sum to one and max normalizing function
+  norm.one <- function(x) {return(x^2)} #sum to one normalizing function
+  norm.abm <- function(x) {return(abs(x)/max(abs(x)))} #max normalizing function
+  norm.abs <- function(x) {return(abs(x))} #absolute value normalizing function
   eig.x <- eigen(as_adjacency_matrix(x)) #eigenvector decomposition of adjacency matrix
   nc <- components(x)$no #number of components
-  if (nc == 1) {s <- eig.x$vectors[, 1]; l <- eig.x$values[1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1) {s <- rowSums(eig.x$vectors[, 1:nc]); l <- sum(eig.x$values[1:nc])} #collecting status scores from separate eigenvectors in disconnected graph
+  print(nc)
+  if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
+  if (nc > 1) {s <- rowSums(eig.x$vectors[, 1:nc])} #collecting status scores from separate eigenvectors in disconnected graph
   if (norm == "max") {s <- norm.max(s)} #normalizing so that maximum value is one
   if (norm == "one") {s <- norm.one(s)} #normalizing so that vector sums to one
-  if (norm == "eig") {s <- norm.eig(s, l)} #normalizing so that vector sums to first eigenvalue
[…]

### 2025-07-31 analysis.qmd
new and improved

@@
    source(here("Functions", "distinction.R"))
-   distinction(g5, norm = "abs")
+   distinction(g11, norm = "one")
 ```
@@
 
-```{r}
-   g <- make_graph(c(1,2, 2,3, 3,4, 4,5, 5,6, 6,7, 7,8, 8,9, 9,10), directed = FALSE)
-   distinction(g)
-```
-
 ## Star Graph Computational Experiments
@@
 ```{r}
+   source(here("Functions", "distinction.R"))
    make.stars <- function(n = 30) {
@@
    b <- make.stars(33)
-   c <- lapply(b, distinction, norm = "abm")
+   c <- lapply(b, distinction, norm = "max")
    ds.s <- sapply(c, function(x) {x[1, 3]})
@@
    ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
-```
-
-```{r}
    c <- lapply(b, distinction, norm = "abm")
@@
    ggsave(here("Plots", "clique-examples.png"), width = 12, height = 8, units = "in")
-```
 
-```{r}
    d.s <- sapply(c, function(x) {x[9, 3]})
@@
    p <- p + labs(y = "", x = "Number of Branches")
-   p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
+  # p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
    p <- p + scale_color_manual(values = c("red", "blue", "tan2"))

### 2025-07-31 Functions/distinction.R

@@ -9,15 +9,16 @@ distinction <- function(x, norm = "max", digits  = 4) {
     names <- V(x)$name 
     V(x)$name <- 1:n
     }
-  norm.max <- function(x) {return(x^2/max(x^2))} #sum to one and max normalizing function
-  norm.one <- function(x) {return(x^2)} #sum to one normalizing function
-  norm.abm <- function(x) {return(abs(x)/max(abs(x)))} #max normalizing function
-  norm.abs <- function(x) {return(abs(x))} #absolute value normalizing function
+  norm.max <- function(x) {x^2/max(x^2)} #sum to one and max one normalizing function
+  norm.one <- function(x) {x^2} #sum to one normalizing function
+  norm.abm <- function(x) {abs(x)/max(abs(x))} #max one normalizing function
+  norm.abs <- function(x) {abs(x)} #absolute value normalizing function
   eig.x <- eigen(as_adjacency_matrix(x)) #eigenvector decomposition of adjacency matrix
   nc <- components(x)$no #number of components
-  print(nc)
+  iso <- sum(components(g)$csize == 1) #checking for isolated components
   if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1) {s <- rowSums(eig.x$vectors[, 1:nc])} #collecting status scores from separate eigenvectors in disconnected graph
+  if (nc > 1 & iso > 0) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
+  if (nc > 1 & iso == 0) {s <- rowSums(eig.x$vectors[, 1:nc])} #collecting status scores from separate eigenvectors in disconnected graph
   if (norm == "max") {s <- norm.max(s)} #normalizing so that maximum value is one
   if (norm == "one") {s <- norm.one(s)} #normalizing so that vector sums to one
   if (norm == "abm") {s <- norm.abm(s)} #normalizing so that maximum value is one
@@ -25,29 +26,30 @@ distinction <- function(x, norm = "max", digits  = 4) {
   d <- rep(n, 0) # initializing distinction vector to all zeros
   u <- rep(n, 0) # initializing constraint vector to all zeros
   for (i in 1:n) { #start looping across nodes in the graph
[…]

### 2025-07-31 Functions/distinction.R
now new and improved

@@ -8,17 +8,20 @@ distinction <- function(x, norm = "max", digits  = 4) {
   if (is.null(V(x)$name) == 0) {
     names <- V(x)$name 
     V(x)$name <- 1:n
-    }
+    } 
   norm.max <- function(x) {x^2/max(x^2)} #sum to one and max one normalizing function
   norm.one <- function(x) {x^2} #sum to one normalizing function
   norm.abm <- function(x) {abs(x)/max(abs(x))} #max one normalizing function
   norm.abs <- function(x) {abs(x)} #absolute value normalizing function
   eig.x <- eigen(as_adjacency_matrix(x)) #eigenvector decomposition of adjacency matrix
-  nc <- components(x)$no #number of components
-  iso <- sum(components(g)$csize == 1) #checking for isolated components
+  nc <- components(x)$no #number of components in graph
+  if (nc > 1) {
+    nn <- sum(components(x)$csize != 1) #number of non-isolated components in graph
+    ci <- which(components(x)$csize != 1) #column indices for non-isolated components
+    }
   if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1 & iso > 0) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1 & iso == 0) {s <- rowSums(eig.x$vectors[, 1:nc])} #collecting status scores from separate eigenvectors in disconnected graph
+  if (nc > 1 & nn == 1) {s <- eig.x$vectors[, ci]} #collecting status scores from first eigenvector in disconnected graph with a single connected component
+  if (nc > 1 & nn > 1) {s <- rowSums(eig.x$vectors[, ci])}
   if (norm == "max") {s <- norm.max(s)} #normalizing so that maximum value is one
   if (norm == "one") {s <- norm.one(s)} #normalizing so that vector sums to one
   if (norm == "abm") {s <- norm.abm(s)} #normalizing so that maximum value is one
@@ -31,11 +34,14 @@ distinction <- function(x, norm = "max", digits  = 4) {
     ed <- ecount(xd) == 0 #checking for empty node-deleted subgraph
     nd <- vcount(xd) #number of nodes of node delete subgraph
     ncd <- components(xd)$no #number of components of node-deleted subgraph
[…]

### 2025-07-31 analysis.qmd
now new and improved
ok NOW it's the real deal

@@
    g11 <- delete_vertices(g11, 8) #path graph
-```
-
-```{r}
-   source(here("Functions", "distinction.R"))
-   distinction(g11, norm = "one")
+   distinction(g11)
 ```

### 2025-07-31 Functions/distinction.R

@@ -1,27 +1,27 @@
 distinction <- function(x, norm = "max", digits  = 4) { 
   require(igraph) #need igraph
-  n <- vcount(x)
-  if (is.null(V(x)$name) == 1) {
-    V(x)$name <- 1:n
-    names <- V(x)$name 
+  n <- vcount(x) #number of nodes in the graph
+  if (is.null(V(x)$name) == 1) { #checking for node labels
+    V(x)$name <- 1:n #labeling nodes with consecutive numbers
+    names <- V(x)$name #storing new labels in vector
     }
-  if (is.null(V(x)$name) == 0) {
-    names <- V(x)$name 
-    V(x)$name <- 1:n
+  if (is.null(V(x)$name) == 0) { #if the nodes already have labels
+    names <- V(x)$name #store old labels in vector
+    V(x)$name <- 1:n #label nodes with consecutive numbers
     } 
   norm.max <- function(x) {x^2/max(x^2)} #sum to one and max one normalizing function
   norm.one <- function(x) {x^2} #sum to one normalizing function
-  norm.abm <- function(x) {abs(x)/max(abs(x))} #max one normalizing function
+  norm.abm <- function(x) {abs(x)/max(abs(x))} #absolute value max one normalizing function
   norm.abs <- function(x) {abs(x)} #absolute value normalizing function
   eig.x <- eigen(as_adjacency_matrix(x)) #eigenvector decomposition of adjacency matrix
   nc <- components(x)$no #number of components in graph
-  if (nc > 1) {
-    nn <- sum(components(x)$csize != 1) #number of non-isolated components in graph
-    ci <- which(components(x)$csize != 1) #column indices for non-isolated components
-    }
+  nn <- sum(components(x)$csize != 1) #number of non-isolated components in graph
+  ni <- nc - nn #number of isolated components in the graph
+  ci <- which(components(x)$csize != 1) #column indices for non-isolated components
   if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1 & nn == 1) {s <- eig.x$vectors[, ci]} #collecting status scores from first eigenvector in disconnected graph with a single connected component
-  if (nc > 1 & nn > 1) {s <- rowSums(eig.x$vectors[, ci])}
[…]

### 2025-07-31 analysis.qmd
fixed mess

@@
    g11 <- delete_vertices(g11, 8) #path graph
+   distinction(g1)
+   distinction(g2)
+   distinction(g5)
+   distinction(g8)
+   distinction(g10)
    distinction(g11)

### 2025-07-31 Functions/distinction.R

@@ -19,8 +19,8 @@ distinction <- function(x, norm = "max", digits  = 4) {
   ni <- nc - nn #number of isolated components in the graph
   ci <- which(components(x)$csize != 1) #column indices for non-isolated components
   if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
-  if (nc > 1 & nn == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with isolated components
-  if (nc > 1 & ni == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with multiple isolates and a single connected component
+  if (nc > 1 & nn == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with a single connected component
+  if (nc > 1 & ni == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with a single isolate
   if (nc > 1 & nn > 1) {s <- rowSums(eig.x$vectors[, ci])} #collecting status scores from the sum of the first k eigenvectors in disconnected graph with multiple components and no isolates
   if (norm == "max") {s <- norm.max(s)} #normalizing so that maximum value is one
   if (norm == "one") {s <- norm.one(s)} #normalizing so that vector sums to one
@@ -40,7 +40,7 @@ distinction <- function(x, norm = "max", digits  = 4) {
     cid <- which(components(xd)$csize != 1) #column indices for non-isolated components
     if (ncd == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in connected subgraph
     if (ncd > 1 & nnd == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in disconnected subgraph with a single connected component
-    if (ncd > 1 & nid == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in disconnected subgraph with multiple isolates and a single connected component
+    if (ncd > 1 & nid == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in disconnected subgraph with a single isolate
[…]

### 2025-07-31 analysis.qmd
new graphs who dis

@@
    ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
-   c <- lapply(b, distinction, norm = "abm")
+   c <- lapply(b, distinction, norm = "max")
    d.s <- sapply(c, function(x) {x[1, 3]})
@@
    ggsave(here("Plots", "clique-examples.png"), width = 12, height = 8, units = "in")
-
+   c <- lapply(b, distinction, norm = "abm")
    d.s <- sapply(c, function(x) {x[9, 3]})

### 2025-07-31 analysis.qmd
oof

--- 2025-07-31 analysis.qmd
@@
    ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
+```
+
+```{r}
+   b <- make.broker.trees(30)
+   c <- lapply(b, distinction, norm = "max")
+   d.s <- sapply(c, function(x) {x[1, 3]})
+   d.b <- sapply(c, function(x) {x[2, 3]})
+   d.p <- sapply(c, function(x) {x[nrow(x), 3]})
+   dat <- data.frame(d = c(d.s, d.b, d.p), 
+         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c("Star", "Gatekeeper", "Peripheral")))
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
+   p <- p + scale_color_manual(values = c("red", "blue", "tan2"))
+   p <- p + theme_minimal()
+   p1 <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 16, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "top"
+                  ) + ggtitle("Abs. Value Norm")
    c <- lapply(b, distinction, norm = "abm")
@@
    d.p <- sapply(c, function(x) {x[nrow(x), 3]})
+   dat <- data.frame(d = c(d.s, d.b, d.p), 
+         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
+         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
+         rep(3, length(d.s)))) |> 
+         mutate(g = factor(g, labels = c("Star", "Gatekeeper", "Peripheral")))
+   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
+   p <- p + geom_point(size = 3)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
+   p <- p + labs(y = "", x = "Number of Branches")
+   p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
+   p <- p + scale_color_manual(values = c("red", "blue", "tan2"))
+   p <- p + theme_minimal()
+   p2 <- p + theme(axis.text = element_text(size = 14, face = "bold"),
+                  axis.title = element_text(size = 16, face = "bold"),
+                  legend.text = element_text(size = 16, face = "bold"),
+                  legend.title = element_blank(),
+                  legend.position = "top"
+                  ) + ggtitle("Squared Norm")
+   library(patchwork)
+   p1 + p2
+   ggsave(here("Plots", "broker-tree-roles-by-nbranches.png"), width = 10, height = 7, units = "in")
+```
+
+```{r}
+   source(here("Functions", "make.broker.cliques.R"))
+   source(here("Functions", "gg.R"))
+   b <- make.broker.cliques(30)
+   p.list <- lapply(b, gg, star = 9)
+   for (i in 1:length(p.list)) {
+      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
+         theme(plot.title = element_text(size = 11))
+      }
+   wrap_plots(p.list[c(1:6)], nrow = 2)
+   ggsave(here("Plots", "clique-examples.png"), width = 12, height = 8, units = "in")
+```
+
+```{r}
+   c <- lapply(b, distinction, norm = "abm")
+   d.s <- sapply(c, function(x) {x[9, 3]})
+   d.b <- sapply(c, function(x) {x[4, 3]})
+   d.p <- sapply(c, function(x) {x[1, 3]})
    dat <- data.frame(d = c(d.s, d.b, d.p), 
@@
    p
-   ggsave(here("Plots", "broker-tree-roles-by-nbranches.png"), width = 7, height = 7, units = "in")
-```
-
-```{r}
-   source(here("Functions", "make.broker.cliques.R"))
-   source(here("Functions", "gg.R"))
-   b <- make.broker.cliques(30)
-   p.list <- lapply(b, gg, star = 9)
-   for (i in 1:length(p.list)) {
-      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
-         theme(plot.title = element_text(size = 11))
-      }
-   wrap_plots(p.list[c(1:6)], nrow = 2)
-   ggsave(here("Plots", "clique-examples.png"), width = 12, height = 8, units = "in")
-
-   d.s <- sapply(c, function(x) {x[9, 3]})
-   d.b <- sapply(c, function(x) {x[4, 3]})
-   d.p <- sapply(c, function(x) {x[1, 3]})
-   dat <- data.frame(d = c(d.s, d.b, d.p), 
-         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
-         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
-         rep(3, length(d.s)))) |> 
-         mutate(g = factor(g, labels = c("Star", "Gatekeeper", "Peripheral")))
-   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
-   p <- p + geom_point(size = 3)
-   p <- p + geom_line(linewidth = 0.75)
-   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
-   p <- p + labs(y = "", x = "Number of Branches")
-  # p <- p + scale_x_continuous(breaks = seq(2, length(d.s), by = 2))
-   p <- p + scale_color_manual(values = c("red", "blue", "tan2"))
-   p <- p + theme_minimal()
-   p <- p + theme(axis.text = element_text(size = 14, face = "bold"),
-                  axis.title = element_text(size = 16, face = "bold"),
-                  legend.text = element_text(size = 16, face = "bold"),
-                  legend.title = element_blank(),
-                  legend.position = "top"
-                  )
-   p
    ggsave(here("Plots", "broker-cliques-roles-by-nbranches.png"), width = 7, height = 7, units = "in")

### 2025-07-31 Functions/distinction.R

@@ -14,10 +14,11 @@ distinction <- function(x, norm = "max", digits  = 4) {
   norm.abm <- function(x) {abs(x)/max(abs(x))} #absolute value max one normalizing function
   norm.abs <- function(x) {abs(x)} #absolute value normalizing function
   eig.x <- eigen(as_adjacency_matrix(x)) #eigenvector decomposition of adjacency matrix
-  nc <- components(x)$no #number of components in graph
-  nn <- sum(components(x)$csize != 1) #number of non-isolated components in graph
+  xc <- components(x) #graph component analysis
+  nc <- xc$no #number of components in graph
+  nn <- sum(xc$csize != 1) #number of non-isolated components in graph
   ni <- nc - nn #number of isolated components in the graph
-  ci <- which(components(x)$csize != 1) #column indices for non-isolated components
+  ci <- which(xc$csize != 1) #column indices for non-isolated components
   if (nc == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in connected graph
   if (nc > 1 & nn == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with a single connected component
   if (nc > 1 & ni == 1) {s <- eig.x$vectors[, 1]} #collecting status scores from first eigenvector in disconnected graph with a single isolate
@@ -35,7 +36,8 @@ distinction <- function(x, norm = "max", digits  = 4) {
     nd <- vcount(xd) #number of nodes of node delete subgraph
     ncd <- components(xd)$no #number of components of node-deleted subgraph
     eig.xd <- eigen(as_adjacency_matrix(xd)) #eigenvector decomposition of node-deleted subgraph
-    nnd <- sum(components(xd)$csize != 1) #number of non-isolated components in graph
+    xdc <- components(xd) #subgraph component analysis
+    nnd <- sum(xcd$csize != 1) #number of non-isolated components in graph
     nid <- ncd - nnd
     cid <- which(components(xd)$csize != 1) #column indices for non-isolated components
     if (ncd == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in connected subgraph

### 2025-08-02 analysis.qmd
new version

@@
    g11 <- delete_vertices(g11, 8) #path graph
-   distinction(g1)
-   distinction(g2)
-   distinction(g5)
-   distinction(g8)
-   distinction(g10)
-   distinction(g11)
 ```
@@
    b <- make.stars(33)
-   c <- lapply(b, distinction, norm = "max")
+   c <- lapply(b, distinction)
    ds.s <- sapply(c, function(x) {x[1, 3]})

### 2025-08-02 Functions/distinction.R

@@ -1,4 +1,4 @@
-distinction <- function(x, norm = "max", digits  = 4) { 
+distinction <- function(x, norm = "abm", digits  = 4) { 
   require(igraph) #need igraph
   n <- vcount(x) #number of nodes in the graph
   if (is.null(V(x)$name) == 1) { #checking for node labels
@@ -37,7 +37,7 @@ distinction <- function(x, norm = "max", digits  = 4) {
     ncd <- components(xd)$no #number of components of node-deleted subgraph
     eig.xd <- eigen(as_adjacency_matrix(xd)) #eigenvector decomposition of node-deleted subgraph
     xdc <- components(xd) #subgraph component analysis
-    nnd <- sum(xcd$csize != 1) #number of non-isolated components in graph
+    nnd <- sum(xdc$csize != 1) #number of non-isolated components in graph
     nid <- ncd - nnd
     cid <- which(components(xd)$csize != 1) #column indices for non-isolated components
     if (ncd == 1) {sd <- eig.xd$vectors[, 1]} #collecting status scores from first eigenvector in connected subgraph

### 2025-08-17 manuscript.tex
Updates from Overleaf

@@
 
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.6\linewidth]{Plots/star-roles-by-size.png}
-    \caption{Scaled and non-scaled distinction centralities for the two node roles in the star graph.}
-    \label{fig:star-scaling}
-\end{figure}
-
 Another advantage of rescaling the $s_i$ component of equation~\ref{eq:distinction} is that it makes the distinction score of key nodes in the graph sensitive to network size, so that it increases for the most distinct (central) node when peripheral actors are added to the network.
@@
 
-\subsubsection{Distinction in the Star Graph}
+\subsubsection{Maximum Inequality and Equality in Distinction}
 Figure~\ref{fig:star} shows a star graph of order seven where node 1 is the central node connected to six peripheral nodes, who themselves have no other connections.
@@
 
-\subsubsection{Distinction in the Circle and Clique Graphs}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{Plots/star-roles-by-size.png}
+    \caption{Scaled and non-scaled distinction centralities for the two node roles in the star graph.}
+    \label{fig:star-scaling}
+\end{figure}
 
@@
 
+%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103
+
 \begin{figure}
@@
 \input{Tabs/clique}
+
+\subsubsection{Distinction and Brokerage}
+
+%welds martin2009social
+%Structural holes vs folds (need to graph out the holes)
+
+%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
+%folds vs circles
+\textit{Model (b)} presents an idealized depiction of a structural fold \citep{vedres2010structural}.
+The resulting measurement scores are in Table 2.
+While node 1 maintains high eigenvector centrality, the eigenvector centrality of the other nodes increases, while their constraint decreases.
+It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their respective subgroups.
+This position of brokerage is more constrained than the star graph because the other actors are connected in subgroups.
+The actors in the subgroup are able to combine their interests to mitigate against the independence of Node 1 in the center.
+In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
+With a scalar adjustment, the stratification increases, giving Node 1 a slight advantage, but also highlighting the extent to which Node 1's distinction is eroded.
+In a maximally connected graph, the distinction of each node would also go to 0.00, as there is no network differentiation among nodes.
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
+            \caption{Inter-Group Brokerage}
+            \label{fig:sf}
+    \end{subfigure} 
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
+            \caption{Structural Fold}
+            \label{fig:sf}
+    \end{subfigure} 
+    \label{fig:classicbrokerage}
+    \caption{Comparison of betweenness brokerage and a structural fold goes here}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
+            \caption{Structural Fold}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
+            \caption{2-Connected Subgraphs}
+            \label{fig:intra}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
+            \caption{2-Connected Subgraphs with Long Tie}
+            \label{fig:inter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
+            \caption{Wheel Graph}
+            \label{fig:wheel}
+    \end{subfigure}
+    \label{fig:struct-folds}
+    \caption{Examples of varying parameters of mediator brokerage (Burt brokerage).
+Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
+            \caption{Structural Fold}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
+            \caption{2-Connected Subgraphs}
+            \label{fig:intra}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
+            \caption{2-Connected Subgraphs with Long Tie}
+            \label{fig:inter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
+            \caption{Wheel Graph}
+            \label{fig:wheel}
+    \end{subfigure}
+    \label{fig:struct-folds}
+    \caption{Examples of varying degrees of connectedness within welded subgraphs.
+Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+\end{figure}
+
+\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
+Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
+Compared to the structural fold, connections 3-2 and 6-7 have been removed.
+Measurement results are in Table 3.
+Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
+The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
+
+\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
+This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+In fact, all nodes except 3 and 6 have higher distinction in such a case.
+This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
+While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
 
@@
 \end{figure}
-
-\subsubsection{Distinction and Brokerage}
-
-%welds martin2009social
-%Structural holes vs folds (need to graph out the holes)
-
-%Circles as their own, pizza pie. at least get to 0 status. Wheel can emerge
-%folds vs circles
-\textit{Model (b)} presents an idealized depiction of a structural fold \citep{vedres2010structural}.
-The resulting measurement scores are in Table 2.
-While node 1 maintains high eigenvector centrality, the eigenvector centrality of the other nodes increases, while their constraint decreases.
-It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their respective subgroups.
-This position of brokerage is more constrained than the star graph because the other actors are connected in subgroups.
-The actors in the subgroup are able to combine their interests to mitigate against the independence of Node 1 in the center.
-In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
-With a scalar adjustment, the stratification increases, giving Node 1 a slight advantage, but also highlighting the extent to which Node 1's distinction is eroded.
-In a maximally connected graph, the distinction of each node would also go to 0.00, as there is no network differentiation among nodes.
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
-            \caption{Structural Fold}
-            \label{fig:sf}
-    \end{subfigure} 
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
-            \caption{2-Connected Subgraphs}
-            \label{fig:intra}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
-            \caption{2-Connected Subgraphs with Long Tie}
-            \label{fig:inter}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
-            \caption{Wheel Graph}
-            \label{fig:wheel}
-    \end{subfigure}
-    \label{fig:struct-folds}
-    \caption{Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-\end{figure}
-
-\textit{Model (c)} presents a graph that is 2-connected in the absence of node 1.
-Each subgraph is one connection short of forming complete subgraphs in the absence of Node 1.
-Compared to the structural fold, connections 3-2 and 6-7 have been removed.
-Measurement results are in Table 3.
-Of the demonstrative networks here, this is the one that most approximates a three-tiered ordered hierarchy.
-The resulting scalar adjusted distinction measures well reflect this stratification, with Node 1 retaining its distinction, Nodes 4 and 5 failing in the middle position, and Nodes 2, 3, 6, and 7 falling to the bottom.
-
-\textit{Model (d)} is the same 2-connected graph with the addition of a long tie connecting nodes 2 and 7.
-This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
-The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
-In fact, all nodes except 3 and 6 have higher distinction in such a case.
-This reflects the positional idea that distinction is a matter of stratification, and cohesion is at odds with creating stratification.
-While the status of Nodes 2 and 7 actually increases beyond that of Nodes 4 and 5 due to the long tie, the constraint also increases as they are now both further constrained by the influence of Node 1, their mutual neighbor.
 

### 2025-09-07 analysis.qmd
new toys

@@
    source(here("Functions", "plot.graph.norm.R"))
+   plot.toys <- function(x, n, l) {
+      ggsave(here("Plots", "Toys", n), 
+         plot = plot.graph.norm(x, l = l)
+         )
+      }
+   del.names <- function(x) {
+      return(delete_vertex_attr(x, "name"))
+      }
 ```
@@
 
-```{r Toy Examples}
-   source(here("Functions", "distinction.R"))
-   g1 <- make_star(7, mode = "undirected") # star graph
-   g2 <- g1 + edge(2,3)
-   g2 <- g2 + edge(2,4)
-   g2 <- g2 + edge(3,4)
-   g2 <- g2 + edge(5,6)
-   g2 <- g2 + edge(5,7)
-   g2 <- g2 + edge(6,7) # structural fold
-   g3 <- g1 + edge(2,4)
-   g3 <- g3 + edge(3,4)
-   g3 <- g3 + edge(5,6)
-   g3 <- g3 + edge(5,7) # intra-connected clusters
-   g4 <- g3 + edge(2,7) # inter-connected clusters
-   g5 <- make_ring(7) #circle graph
-   g6 <- g5 + edge(6,1) # circle graph plus triangle
-   g7 <- g5 + edge(7,4) # circle graph plus long tie
-   g8 <- make_full_graph(7, directed = FALSE) # clique
-   g9 <- make_full_graph(6, directed = FALSE)
-   g9 <- add_vertices(g9, 1)
-   g9 <- g9 + edge(1,7) # kite
-   g10 <- g1 + edge(2,3)
-   g10 <- g10 + edge(3,4)
-   g10 <- g10 + edge(4,5)
-   g10 <- g10 + edge(5,6)
-   g10 <- g10 + edge(6,7)
-   g10 <- g10 + edge(7,2) #wheel graph
-   g11 <- make_ring(8) 
-   g11 <- delete_vertices(g11, 8) #path graph
+```{r Building Blocks}
+   c3 <- make_full_graph(3, directed = FALSE) # triangle
+   c4 <- make_full_graph(4, directed = FALSE) # 4-clique
+   c5 <- make_full_graph(5, directed = FALSE) # 5-clique
+   t3 <- make_tree(n = 4, children = 3, mode = "undirected") # 3-tree
+   t2 <- make_tree(n = 3, children = 2, mode = "undirected") # 2-tree
 ```
 
-```{r Bonacich examples}
-   g13 <- make_empty_graph(10, directed = FALSE)
-   g13 <- g13 + edge(1,2)
-   g13 <- g13 + edge(1,3)
-   g13 <- g13 + edge(1,9)
-   g13 <- g13 + edge(2,3)
-   g13 <- g13 + edge(2,10)
-   g13 <- g13 + edge(3,4)
-   g13 <- g13 + edge(4,5)
-   g13 <- g13 + edge(4,6)
-   g13 <- g13 + edge(5,10)
-   g13 <- g13 + edge(5,6)
-   g13 <- g13 + edge(6,7)
-   g13 <- g13 + edge(7,8)
-   g13 <- g13 + edge(7,9)
-   g13 <- g13 + edge(8,10)
-   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
-   g14 <- make_empty_graph(12, directed = FALSE)
-   g14 <- g14 + edge(1,2)
-   g14 <- g14 + edge(1,6)
-   g14 <- g14 + edge(1,7)
-   g14 <- g14 + edge(2,3)
-   g14 <- g14 + edge(2,10)
-   g14 <- g14 + edge(3,4)
-   g14 <- g14 + edge(3,8)
-   g14 <- g14 + edge(4,5)
-   g14 <- g14 + edge(4,11)
-   g14 <- g14 + edge(5,6)
-   g14 <- g14 + edge(5,9)
-   g14 <- g14 + edge(6,12)
-   g14 <- g14 + edge(7,8)
-   g14 <- g14 + edge(7,9)
-   g14 <- g14 + edge(8,9)
-   g14 <- g14 + edge(10,11)
-   g14 <- g14 + edge(10,12)
-   g14 <- g14 + edge(11,12)
+```{r Basic Toy Graphs}
+   s7 <- make_star(7, mode = "undirected") # 7-star graph
+   plot.toys(s7, "star.png", "kk")
+   c7 <- make_full_graph(7, directed = FALSE) # 7-clique
+   plot.toys(c7, "clique.png", "circle")
+   r7 <- make_ring(7) # 7-circle graph
+   plot.toys(r7, "circle.png", "circle")
+   c6 <- make_full_graph(6, directed = FALSE) # 6-clique
+   k7 <- add_vertices(c6, 1) # 6-clique plus node
+   k7 <- k7 + edge(1,7) # 7-kite
+   plot.toys(k7, "kite.png", "kk")
+   r6 <- make_ring(6) # 6-circle graph
+   V(r6)$name <- as.character(2:7)
+   V(s7)$name <- as.character(1:7)
+   w7 <- s7 + r6 # 7-wheel-graph
+   r6 <- del.names(r6)
+   s7 <- del.names(s7)
+   w7 <- del.names(w7)
+   plot.toys(w7, "wheel.png", "kk")
+   r8 <- make_ring(8) # 8-circle graph
+   p7 <- delete_vertices(r8, 8) #path graph
+   plot.toys(p7, "path.png", "kk")
 ```
 
-```{r Estrada examples}
-   g15 <- make_empty_graph(8, directed = FALSE)
-   g15 <- g15 + edge(1,2)
-   g15 <- g15 + edge(1,5)
-   g15 <- g15 + edge(1,8)
-   g15 <- g15 + edge(2,3)
-   g15 <- g15 + edge(2,8)
-   g15 <- g15 + edge(3,4)
-   g15 <- g15 + edge(3,6)
-   g15 <- g15 + edge(4,5)
-   g15 <- g15 + edge(4,7)
-   g15 <- g15 + edge(5,6)
-   g15 <- g15 + edge(6,7)
-   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
-   g16 <- make_full_graph(9, directed = FALSE)
-   g16 <- g16 - edge("1|6")
-   g16 <- g16 - edge("1|5")
-   g16 <- g16 - edge("2|4")
-   g16 <- g16 - edge("2|9")
-   g16 <- g16 - edge("3|6")
-   g16 <- g16 - edge("3|8")
-   g16 <- g16 - edge("4|7")
-   g16 <- g16 - edge("5|8")
-   g16 <- g16 - edge("7|9") #Fig 1(b) https://doi.org/10.1103/PhysRevE.71.056103
+```{r Mediator versus Weld}
+   c1 <- c4
+   c2 <- c4
+   V(c1)$name <- as.character(1:4)
+   V(c2)$name <- as.character(4:7)
+   sf4 <- c1 + c2  # structural fold four-clique
+   sf4 <- del.names(sf4)
+   plot.toys(sf4, "sf4.png", "kk")
+   c1 <- c5
+   c2 <- c5
+   V(c1)$name <- as.character(1:5)
+   V(c2)$name <- as.character(5:9)
+   sf5 <- c1 + c2  # structural fold five-clique
+   sf5 <- del.names(sf5)
+   plot.toys(sf5, "sf5.png", "kk")
+   b3 <- c3 + c3
+   b3 <- add_vertices(b3, 1)
+   b3 <- b3 + edge(7,1)
+   b3 <- b3 + edge(7,4) # broker between triangles
+   plot.toys(b3, "broker3.png", "kk")
+   b4 <- c4 + c4
+   b4 <- add_vertices(b4, 1)
+   b4 <- b4 + edge(9,1)
+   b4 <- b4 + edge(9,5) # broker between four-cliques
+   plot.toys(b4, "broker4.png", "kk")
 ```
 
-```{r Toy Networks Plots}
-   source(here("Functions", "distinction.R"))
-   source(here("Functions", "plot.graph.norm.R"))
-   png(here("Plots", "Toys", "star.png"))
-   plot.graph.norm(g1, l = "kk")
-   dev.off()
-   png(here("Plots", "Toys", "sf.png"))
-   plot.graph.norm(g2, l = "kk")
-   dev.off()
-   png(here("Plots", "Toys", "intra.png"))
-   plot.graph.norm(g3, l = "auto")
-   dev.off()
-   png(here("Plots", "Toys", "inter.png"))
-   plot.graph.norm(g4, l = "auto")
-   dev.off()
-   png(here("Plots", "Toys", "circle.png"))
-   plot.graph.norm(g5, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "circle-plus-triangle.png"))
-   plot.graph.norm(g6, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "circle-plus-long.png"))
-   plot.graph.norm(g7, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "clique.png"))
-   plot.graph.norm(g8, l = "kk")
-   dev.off()
-   png(here("Plots", "Toys", "kite.png"))
-   plot.graph.norm(g9, l = "kk")
-   dev.off()
-   png(here("Plots", "Toys", "wheel.png"))
-   plot.graph.norm(g10, l = "kk")
-   dev.off()
-   png(here("Plots", "Toys", "path.png"))
-   plot.graph.norm(g11, l = "kk")
-   dev.off()
-   source(here("Functions", "plot.graph.cat.R"))
-   png(here("Plots", "Toys", "bonacich1.png"))
-   plot.graph.cat(g13, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "bonacich2.png"))
-   plot.graph.cat(g14, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "estrada1.png"))
-   plot.graph.cat(g15, l = "circle")
-   dev.off()
-   png(here("Plots", "Toys", "estrada2.png"))
-   plot.graph.cat(g16, l = "circle")
-   dev.off()
+```{r Triadic Closure}
+   ct <- r7 + edge(6,1) # circle graph plus triangle
+   plot.toys(ct, "circle-triangle1.png", "circle")
+   cl <- r7 + edge(7,4) # circle graph plus long tie
+   plot.toys(cl, "circle-long.png", "circle")
+   st1 <- s7 + edge(2,3) # star graph plus one triangle
+   plot.toys(st1, "start-triangle1.png", "kk")
+   st2 <- st1 + edge(5,6) # star graph plus two triangles
+   plot.toys(st2, "start-triangle2.png", "kk")
+```
+
+```{r Mediator Parameters}
+   t222 <- t2 + t2
+   t222 <- add_vertices(t222, 1)
+   t222 <- t222 + edge(7, 1)
+   t222 <- t222 + edge(7, 4) # tree mediator two branch
+   plot.toys(t222, "tree-mediator2.png", "kk")
+   t232 <- t3 + t3
+   t232 <- add_vertices(t232, 1)
+   t232 <- t232 + edge(9, 1)
+   t232 <- t232 + edge(9, 5) # tree mediator three branch
+   plot.toys(t232, "tree-mediator3.png", "kk")
+   t222l <- t222 + edge(6, 2) # tree mediator two branch plus long
+   plot.toys(t222l, "tree-mediator2-long.png", "auto")
+   t232l <- t232 + edge(7, 2) # tree mediator three branch plus long
+   plot.toys(t232l, "tree-mediator3-long.png", "auto")
+```
+```{r Mediator Parameters}
+   c1 <- make_ring(4)
+   c2 <- make_ring(4)
+   V(c1)$name <- as.character(1:4)
+   V(c2)$name <- as.character(4:7)
+   cw <- c1 + c2  # circle weld
+   tc <- cw + edge(2, 4)
+   tc <- tc + edge(4, 6) # two-connected
+   tcl <- tc + edge(1, 7) # two-connected plus long tie
+   cw <- del.names(cw)
+   tc <- del.names(tc)
+   tcl <- del.names(tcl)
+   plot.toys(cw, "circle-weld.png", "auto")
+   plot.toys(tc, "two-connected.png", "kk")
+   plot.toys(tcl, "two-connected-long.png", "kk")
+
 ```
@@
 ```
+
+```{r}
+   library(networkdata)
+   distinction(karate, norm = "max")
+   plot.graph.norm(karate)
+```

### 2025-09-07 Functions/distinction.R

@@ -63,3 +63,4 @@ distinction <- function(x, norm = "abm", digits  = 4) {
   rownames(dat) <- 1:nrow(dat) #adding row names
   return(dat)
 } #end function
+

### 2025-09-07 Functions/make-bonacich.R

@@ -1,0 +1,38 @@
+make.bonacich <- function() {
+   g1 <- make_empty_graph(10, directed = FALSE)
+   g1 <- g1 + edge(1,2)
+   g1 <- g1 + edge(1,3)
+   g1 <- g1 + edge(1,9)
+   g1 <- g1 + edge(2,3)
+   g1 <- g1 + edge(2,10)
+   g1 <- g1 + edge(3,4)
+   g1 <- g1 + edge(4,5)
+   g1 <- g1 + edge(4,6)
+   g1 <- g1 + edge(5,10)
+   g1 <- g1 + edge(5,6)
+   g1 <- g1 + edge(6,7)
+   g1 <- g1 + edge(7,8)
+   g1 <- g1 + edge(7,9)
+   g1 <- g1 + edge(8,10)
+   g1 <- g1 + edge(8,9) #Bonacich (2007) regular network Fig. 5
+   g2 <- make_empty_graph(12, directed = FALSE)
+   g2 <- g2 + edge(1,2)
+   g2 <- g2 + edge(1,6)
+   g2 <- g2 + edge(1,7)
+   g2 <- g2 + edge(2,3)
+   g2 <- g2 + edge(2,10)
+   g2 <- g2 + edge(3,4)
+   g2 <- g2 + edge(3,8)
+   g2 <- g2 + edge(4,5)
+   g2 <- g2 + edge(4,11)
+   g2 <- g2 + edge(5,6)
+   g2 <- g2 + edge(5,9)
+   g2 <- g2 + edge(6,12)
+   g2 <- g2 + edge(7,8)
+   g2 <- g2 + edge(7,9)
+   g2 <- g2 + edge(8,9)
+   g2 <- g2 + edge(10,11)
+   g2 <- g2 + edge(10,12)
+   g2 <- g2 + edge(11,12)
+   return(list(g1 = g1, g2 = g2))
+}

### 2025-09-07 Functions/plot.graph.norm.R

@@ -1,6 +1,6 @@
-plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8, c = 0.05) { #plotting function
+plot.graph.norm <- function(x, l = "kk", vs = 16, ts = 8, c = 0.05, n = "max") { #plotting function
   library(ggraph)
-  d <- distinction(x)[, 3]
+  d <- distinction(x, norm = n)[, 3]
   nc <- vector(mode = "character", length = length(d))
   nc[which(d < -c)] <- "tan2"
   nc[which(d > c)] <- "blue"

### 2025-09-07 make.estrada.R

@@ -1,0 +1,26 @@
+make.estrada <- function() {
+   g1 <- make_empty_graph(8, directed = FALSE)
+   g1 <- g1 + edge(1,2)
+   g1 <- g1 + edge(1,5)
+   g1 <- g1 + edge(1,8)
+   g1 <- g1 + edge(2,3)
+   g1 <- g1 + edge(2,8)
+   g1 <- g1 + edge(3,4)
+   g1 <- g1 + edge(3,6)
+   g1 <- g1 + edge(4,5)
+   g1 <- g1 + edge(4,7)
+   g1 <- g1 + edge(5,6)
+   g1 <- g1 + edge(6,7)
+   g1 <- g1 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
+   g2 <- make_full_graph(9, directed = FALSE)
+   g2 <- g2 - edge("1|6")
+   g2 <- g2 - edge("1|5")
+   g2 <- g2 - edge("2|4")
+   g2 <- g2 - edge("2|9")
+   g2 <- g2 - edge("3|6")
+   g2 <- g2 - edge("3|8")
+   g2 <- g2 - edge("4|7")
+   g2 <- g2 - edge("5|8")
+   g2 <- g2 - edge("7|9") #Fig 1(b) https://doi.org/10.1103/PhysRevE.71.056103
+  return(list(g1 = g1, g2 = g2))
+}

### 2025-09-13 analysis.qmd
new tabs who dis

@@
 ---
+
+## Setup
 
@@
    source(here("Functions", "plot.graph.norm.R"))
+   source(here("Functions", "tab.cent.R"))
    plot.toys <- function(x, n, l) {
@@
 ```{r Basic Toy Graphs}
+   ## Star
    s7 <- make_star(7, mode = "undirected") # 7-star graph
    plot.toys(s7, "star.png", "kk")
+   tab.cent(distinction(s7), name = "star", 
+   label = "star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for the star graph.")
+   ## Clique
    c7 <- make_full_graph(7, directed = FALSE) # 7-clique
    plot.toys(c7, "clique.png", "circle")
+   tab.cent(distinction(c7), name = "clique", 
+   label = "clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for the clique graph.")
+   ## Circle
    r7 <- make_ring(7) # 7-circle graph
    plot.toys(r7, "circle.png", "circle")
+   tab.cent(distinction(r7), name = "circle", 
+   label = "circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for the circle graph.")
+   ## Kite
    c6 <- make_full_graph(6, directed = FALSE) # 6-clique
@@
    plot.toys(k7, "kite.png", "kk")
+   tab.cent(distinction(k7), name = "kite", 
+   label = "kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
+   caption = "Distinction centrality scores for the kite graph.")
+   ## Wheel
    r6 <- make_ring(6) # 6-circle graph
@@
    plot.toys(w7, "wheel.png", "kk")
+   tab.cent(distinction(w7), name = "wheel", 
+   label = "wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
+   caption = "Distinction centrality scores for the wheel graph.")
+   ## Path
    r8 <- make_ring(8) # 8-circle graph
@@
    plot.toys(p7, "path.png", "kk")
+   source(here("Functions", "tab.cent.R"))
+   tab.cent(distinction(p7), name = "path", 
+   label = "path", rownames = c("1, 7", "2, 6", "3, 5", "4"),
+   caption = "Distinction centrality scores for the path graph.")
 ```
@@
 ```{r Mediator versus Weld}
+   ## Structural Fold (4-Clique)
    c1 <- c4
@@
    plot.toys(sf4, "sf4.png", "kk")
+   tab.cent(distinction(sf4), name = "structfold4", 
+   label = "sf4", rownames = c("4", "1, 2, 3, 5, 6, 7"),
+   caption = "Distinction centrality scores for the structural fold graph (4-Clique).")
+   ## Structural Fold (5-Clique)
    c1 <- c5
@@
    plot.toys(sf5, "sf5.png", "kk")
+   tab.cent(distinction(sf5), name = "structfold5", 
+   label = "sf5", rownames = c("5", "1, 2, 3, 4, 6, 7, 8, 9"),
+   caption = "Distinction centrality scores for the structural fold graph (5-Clique).")
+   ## Triangle Broker
    b3 <- c3 + c3
@@
    plot.toys(b3, "broker3.png", "kk")
+   tab.cent(distinction(sf5), name = "broker3", 
+   label = "b3", rownames = c("1", "2, 3, 5, 6", "4", "7"),
+   caption = "Distinction centrality scores for broker graph (3-clique).")
+   ## Clique Broker
    b4 <- c4 + c4
@@
    plot.toys(b4, "broker4.png", "kk")
+   tab.cent(distinction(b4), name = "broker4", 
+   label = "b4", rownames = c("1, 5", "2, 3, 4, 6, 7, 8", "9"),
+   caption = "Distinction centrality scores for broker graph (4-Clique).")
 ```
@@
 ```{r Triadic Closure}
+   ## Circle Graph Plus Triangle
    ct <- r7 + edge(6,1) # circle graph plus triangle
    plot.toys(ct, "circle-triangle1.png", "circle")
+   tab.cent(distinction(ct), name = "circletriangle", 
+   label = "circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
+   caption = "Distinction centrality scores for the circle graph with triangle.")
+   ## Circle Graph Plus Long Tie
    cl <- r7 + edge(7,4) # circle graph plus long tie
    plot.toys(cl, "circle-long.png", "circle")
+   tab.cent(distinction(cl), name = "circlelong", 
+   label = "circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
+   caption = "Distinction centrality scores for the circle graph with long tie.")
+   ## Star Graph Plus Triangle
    st1 <- s7 + edge(2,3) # star graph plus one triangle
-   plot.toys(st1, "start-triangle1.png", "kk")
+   plot.toys(st1, "star-triangle1.png", "kk")
+   tab.cent(distinction(st1), name = "startriangle1", 
+   label = "star1", rownames = c("1", "2, 3", "4, 5, 6, 7"),
+   caption = "Distinction centrality scores for the star graph with one triangle.")
+   ## Star Graph Plust Two Triangles
    st2 <- st1 + edge(5,6) # star graph plus two triangles
-   plot.toys(st2, "start-triangle2.png", "kk")
+   plot.toys(st2, "star-triangle2.png", "kk")
+   tab.cent(distinction(st2), name = "startriangle2", 
+   label = "star2", rownames = c("1", "2, 3, 5, 6", "4, 7"),
+   caption = "Distinction centrality scores for the star graph with two triangles.")
 ```
@@
 ```{r Mediator Parameters}
+   ## Tree Mediator (Two Branch)
    t222 <- t2 + t2
@@
    plot.toys(t222, "tree-mediator2.png", "kk")
+   tab.cent(distinction(t222), name = "treemediator2", 
+   label = "tree2", rownames = c("1, 4", "2, 3, 5, 6", "7"),
+   caption = "Distinction centrality scores for tree broker graph (two-branches).")
+   ## Tree Mediator (Three Branch)
    t232 <- t3 + t3
@@
    plot.toys(t232, "tree-mediator3.png", "kk")
+   tab.cent(distinction(t232), name = "treemediator3", 
+   label = "tree3", rownames = c("1, 5", "2, 3, 4, 6, 7, 8", "9"),
+   caption = "Distinction centrality scores for tree broker graph (three-branches).")
+   ## Tree Mediator (Two Branch Plus Long Tie)
    t222l <- t222 + edge(6, 2) # tree mediator two branch plus long
    plot.toys(t222l, "tree-mediator2-long.png", "auto")
+   tab.cent(distinction(t222l), name = "treemediatorlong2", 
+   label = "treelong2", rownames = c("1, 4", "2, 6", "3, 5", "7"),
+   caption = "Distinction centrality scores for tree broker graph (two-branches plus long tie).")
    t232l <- t232 + edge(7, 2) # tree mediator three branch plus long
    plot.toys(t232l, "tree-mediator3-long.png", "auto")
-```
-```{r Mediator Parameters}
+   tab.cent(distinction(t232l), name = "treemediatorlong3", 
+   label = "treelong3", rownames = c("1, 5", "2, 7", "3, 4, 6, 8", "9"),
+   caption = "Distinction centrality scores for tree broker graph (three-branches plus long tie).")
    c1 <- make_ring(4)
@@
    tcl <- del.names(tcl)
+   ## Circle Weld
    plot.toys(cw, "circle-weld.png", "auto")
+   tab.cent(distinction(cw), name = "circleweld", 
+   label = "cw", rownames = c("1, 3, 5, 7", "2, 6", "4"),
+   caption = "Distinction centrality scores for the circle weld graph.")
+   ## Two-Connected
    plot.toys(tc, "two-connected.png", "kk")
+   tab.cent(distinction(tc), name = "twoconnected", 
+   label = "tc", rownames = c("1, 3, 5, 7", "2, 6", "4"),
+   caption = "Distinction centrality scores for the two-connected graph.")
+   ## Two-Connected Plus Long Tie
    plot.toys(tcl, "two-connected-long.png", "kk")
-
-```
-
-```{r Toy Network Distinction Tables}
-   source(here("Functions", "tab.cent.R"))
-   tab.cent(distinction(g1), name = "star", 
-   label = "star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for the star graph.")
-   tab.cent(distinction(g2), name = "structfold", 
-   label = "sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for the structural fold graph.")
-   tab.cent(distinction(g3), name = "intraclust", 
-   label = "intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
-   caption = "Distinction centrality scores for the intra-connected clusters graph.")
-   tab.cent(distinction(g4), name = "interclust", 
-   label = "inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
-   caption = "Distinction centrality scores for the inter-connected clusters graph.")
-   tab.cent(distinction(g5), name = "circle", 
-   label = "circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for the circle graph.")
-   tab.cent(distinction(g6), name = "circletriangle", 
-   label = "circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
-   caption = "Distinction centrality scores for the circle graph with triangle.")
-   tab.cent(distinction(g7), name = "circlelong", 
-   label = "circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
-   caption = "Distinction centrality scores for the circle graph with long tie.")
-   tab.cent(distinction(g8), name = "clique", 
-   label = "clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for the clique graph.")
-   tab.cent(distinction(g9), name = "kite", 
-   label = "kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
-   caption = "Distinction centrality scores for the kite graph.")
-   tab.cent(distinction(g10), name = "wheel", 
-   label = "wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
-   caption = "Distinction centrality scores for the wheel graph.")
-   tab.cent(distinction(g11), name = "path", 
-   label = "path", rownames = c("1, 7", "2, 6", "3, 5", "4"),
-   caption = "Distinction centrality scores for the path graph.")
+   tab.cent(distinction(tcl), name = "twoconnectedlong", 
+   label = "tcl", rownames = c("1, 7", "2, 6", "3, 5", "4"),
+   caption = "Distinction centrality scores for the two-connected graph (plus long tie).")
 ```
@@
 ```
+
 ## Connected Caves Computational Experiments
-```{r}
+
+```{r Connected Caves}
    source(here("Functions", "connect.caves.R"))

### 2025-09-13 manuscript.tex
Hi

@@
 
-\input{Tabs/star}
+\input{Tabs/Figure1}
 
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
-            \caption{Clique Graph}
-            \label{fig:clique}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
+            \caption{Kite Graph}
+            \label{fig:kite}
     \end{subfigure}
-    \label{fig:star-circle-clique}
     \caption{Distinction Centrality in toy graphs.
@@
 However, the actual incentives and consequences for each of the nodes in a triadic closure will be dependent on the overall existing network structure.
-Node 7 is worse off because of the structure of the circle graph, not necessarily because in all conditions Node 7 will be worse off.
+Node 7 is worse off due to the structure of the circle graph, rather than because it will always be worse off under all conditions.
 If Node 7 is actually highly central to the graph, near neighbor triadic closure can be distinction increasing.
@@
     \centering
-
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-triangle.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-triangle1.png}
             \caption{Circle Graph with Near Neighbor Closure}
-            \label{fig:circleplus}
+            \label{fig:circletriangle}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-plus-long.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-long.png}
             \caption{Circle Graph with Long Tie}
-            \label{fig:circleplus}
+            \label{fig:circlelong}
+    \end{subfigure} \\
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle1.png}
+            \caption{Star Graph with Near Neighbor Closure}
+            \label{fig:startriangle1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle2.png}
+            \caption{Star Graph with Two Triangles}
+            \label{fig:startriangle2}
     \end{subfigure}
@@
 This position of brokerage is more constrained than the star graph because the other actors are connected in subgroups.
-The actors in the subgroup are able to combine their interests to mitigate against the independence of Node 1 in the center.
+The actors in the subgroup can combine their interests to counterbalance the independence of Node 1 in the center.
 In an unadjusted measure of distinction, the different nodes become remarkably close in their distinction measure.
@@
      \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
-            \caption{Inter-Group Brokerage}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
+            \caption{Brokerage Mediated (3-Cliques)}
+            \label{fig:classicbrokerage3}
+    \end{subfigure} 
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
+            \caption{Structural Fold (4-Clique)}
             \label{fig:sf}
     \end{subfigure} 
+    \label{fig:struct-fold}
      \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
-            \caption{Structural Fold}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
+            \caption{Brokerage Mediated (4-Cliques)}
+            \label{fig:classicbrokerage3}
+    \end{subfigure} 
+     \begin{subfigure}[b]{0.35\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
+            \caption{Structural Fold (5-Clique)}
             \label{fig:sf}
     \end{subfigure} 
-    \label{fig:classicbrokerage}
+    \label{fig:struct-fold}
     \caption{Comparison of betweenness brokerage and a structural fold goes here}
@@
      \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
-            \caption{Structural Fold}
-            \label{fig:sf}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
+            \caption{Mediator between two trees with two branches (2, 2, 2)}
+            \label{fig:treemediator2}
     \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
-            \caption{2-Connected Subgraphs}
-            \label{fig:intra}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
+            \caption{Mediator between two trees with three branches (2, 3, 2)}
+            \label{fig:treemediator3}
     \end{subfigure}
     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
-            \caption{2-Connected Subgraphs with Long Tie}
-            \label{fig:inter}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
+            \caption{Mediator between two trees with two branches (2, 2, 2) with long tie}
+            \label{fig:treemediatorlong2}
     \end{subfigure}
     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
-            \caption{Wheel Graph}
-            \label{fig:wheel}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
+            \caption{Mediator between two trees with three branches (2, 2, 2) with long tie}
+            \label{fig:treemediatorlong3}
     \end{subfigure}
     \label{fig:struct-folds}
-    \caption{Examples of varying parameters of mediator brokerage (Burt brokerage).
-Distinction Centrality in toy graphs.
+    \caption{Examples of varying parameters of mediator brokerage in tree graphs (Burt brokerage).
 Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
@@
      \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
-            \caption{Structural Fold}
-            \label{fig:sf}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
+            \caption{Two-Connected}
+            \label{fig:twoconnected}
     \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
-            \caption{2-Connected Subgraphs}
-            \label{fig:intra}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
+            \caption{Circle Weld}
+            \label{fig:circleweld}
     \end{subfigure}
     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected-long.png}
             \caption{2-Connected Subgraphs with Long Tie}
-            \label{fig:inter}
+            \label{fig:twoconnectedlong}
     \end{subfigure}
@@
 %hypothesis: size of the normalization gaps is causing the differences between normalized and unnormalized.
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
-            \caption{Kite Graph}
-            \label{fig:kite}
-    \end{subfigure}
-    \caption{Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-    \label{fig:toys}
-\end{figure}
 
@@
 
-A puzzle that results from the empirics however is how the balance between antagonistic factions created by the Medici came to be undone within a decade of Padgett and Ansell’s focus.
-Brokerage created social stability, yet in 1432 Rinaldo Albizzi as leader of the combination of conservative old oligarchic families seized the reigns of the Florentine government, exiling the leading Medici from Florence.
+A puzzle that results from the empirics, however, is how the balance between antagonistic factions created by the Medici came to be undone within a decade of Padgett and Ansell’s focus.
+Brokerage created social stability, yet in 1432, Rinaldo Albizzi, as leader of the combination of conservative old oligarchic families, seized the reins of the Florentine government, exiling the leading Medici from Florence.
 Why was the network position of the Medici as brokers so unstable?

### 2025-09-14 manuscript.tex
Updates from Overleaf

@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
-            \caption{Kite Graph}
-            \label{fig:kite}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
+            \caption{Clique Graph}
+            \label{fig:clique}
     \end{subfigure}
@@
 \end{figure}
-
-\input{Tabs/circle}
 
@@
 
-\input{Tabs/clique}
 %Clique addition experiment
@@
 
+%triadic closure graphs
+\begin{figure}[t!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-triangle1.png}
+            \caption{Circle Graph with Near Neighbor Closure}
+            \label{fig:circletriangle}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-long.png}
+            \caption{Circle Graph with a Long Tie}
+            \label{fig:circlelong}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/star-triangle1.png}
+            \caption{Star Graph with Near Neighbor Closure}
+            \label{fig:startriangle1}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/star-triangle2.png}
+            \caption{Star Graph with Two Triangles}
+            \label{fig:startriangle2}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected-long.png}
+            \caption{2-Connected Subgraphs with Long Tie}
+            \label{fig:twoconnectedlong}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
+            \caption{Wheel Graph, 6 Triads}
+            \label{fig:wheel}
+    \end{subfigure}
+    \caption{Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
+\end{figure}
+
+%triadic closure centrality scores
+\input{Tabs/Figure3}
+
+%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103
+%\input{Tabs/intraclust}
+%\input{Tabs/interclust}
+
 Figure 3 \textit{Model (b)} and Table 5 present a graph and corresponding measures of a long tie formation spanning the circle graph.
@@
 The addition of a single connection between node 1 and 6 in Figure 3 \textit{Model (a)} stratified a network from equality into four levels of hierarchy with a single additional connection.
-
-%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-triangle1.png}
-            \caption{Circle Graph with Near Neighbor Closure}
-            \label{fig:circletriangle}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-long.png}
-            \caption{Circle Graph with Long Tie}
-            \label{fig:circlelong}
-    \end{subfigure} \\
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle1.png}
-            \caption{Star Graph with Near Neighbor Closure}
-            \label{fig:startriangle1}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle2.png}
-            \caption{Star Graph with Two Triangles}
-            \label{fig:startriangle2}
-    \end{subfigure}
-    \caption{Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-    \label{fig:toys}
-\end{figure}
-
-\input{Tabs/circletriangle}
-\input{Tabs/circlelong}
-\input{Tabs/kite}
-
-\input{Tabs/structfold.tex}
-\input{Tabs/intraclust}
-\input{Tabs/interclust}
-\input{Tabs/clique}
 
@@
 
-\begin{figure}
+%brokerage and structural folds Figure 4
+\begin{figure}[H]
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
-     \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
+            \caption{Structural Fold (4-Clique)}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
+            \caption{Structural Fold (5-Clique)}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
+            \caption{Two-Connected}
+            \label{fig:twoconnected}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
+            \caption{Circle Weld}
+            \label{fig:circleweld}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
@@
     \end{subfigure} 
-     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
-            \caption{Structural Fold (4-Clique)}
-            \label{fig:sf}
-    \end{subfigure} 
     \label{fig:struct-fold}
-     \begin{subfigure}[b]{0.35\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
         \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
@@
     \end{subfigure} 
-     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
-            \caption{Structural Fold (5-Clique)}
-            \label{fig:sf}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
+            \caption{Tree with 2 Branches, 2 Leaves}
+            \label{fig:treemediator2}
     \end{subfigure} 
-    \label{fig:struct-fold}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
+            \caption{Tree with 2 Branches, 3 Leaves}
+            \label{fig:treemediator3}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
+            \caption{Tree with 2 Branches, 2 Leaves, 1 Long Tie}
+            \label{fig:treemediatorlong2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
+            \caption{Tree with 2 Branches, 3 Leaves, 1 Long Tie}
+            \label{fig:treemediatorlong3}
+    \end{subfigure}
     \caption{Comparison of betweenness brokerage and a structural fold goes here}
@@
 
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
-            \caption{Mediator between two trees with two branches (2, 2, 2)}
-            \label{fig:treemediator2}
-    \end{subfigure} 
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
-            \caption{Mediator between two trees with three branches (2, 3, 2)}
-            \label{fig:treemediator3}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
-            \caption{Mediator between two trees with two branches (2, 2, 2) with long tie}
-            \label{fig:treemediatorlong2}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
-            \caption{Mediator between two trees with three branches (2, 2, 2) with long tie}
-            \label{fig:treemediatorlong3}
-    \end{subfigure}
-    \label{fig:struct-folds}
-    \caption{Examples of varying parameters of mediator brokerage in tree graphs (Burt brokerage).
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
-    \centering
-     \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
-            \caption{Two-Connected}
-            \label{fig:twoconnected}
-    \end{subfigure} 
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
-            \caption{Circle Weld}
-            \label{fig:circleweld}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected-long.png}
-            \caption{2-Connected Subgraphs with Long Tie}
-            \label{fig:twoconnectedlong}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
-            \caption{Wheel Graph}
-            \label{fig:wheel}
-    \end{subfigure}
-    \label{fig:struct-folds}
-    \caption{Examples of varying degrees of connectedness within welded subgraphs.
-Distinction Centrality in toy graphs.
-Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
-\end{figure}
+%brokerage centrality scores
+\input{Tabs/Figure4}
 
@@
 \subsubsection{Kite Graphs and Eigenvector Normalization}
+
+\input{Tabs/Figure5(kites)}
 
@@
 
-\input{Tabs/political.tex}
+\input{Tabs/Figure6.tex}
 

### 2025-09-20 analysis.qmd
new data who dis

@@
 
+## Political Graphs
+```{r Loading TestPolitical Data}
+   poli1 <- as.matrix(read.csv(here("Data", "poli1.csv")))
+   poli1 <- graph_from_edgelist(poli1, directed = FALSE)
+   poli2 <- as.matrix(read.csv(here("Data", "poli2.csv")))
+   poli2 <- graph_from_edgelist(poli2, directed = FALSE)
+   poli3 <- as.matrix(read.csv(here("Data", "poli3.csv")))
+   poli3 <- graph_from_edgelist(poli3, directed = FALSE)
+   poli4 <- as.matrix(read.csv(here("Data", "poli4.csv")))
+   poli4 <- graph_from_edgelist(poli4, directed = FALSE)
+```
+
 ## Medici
@@
 ```
+
+## Kite Computational Experiments
+
+```{r}
+   # Vary size of kite clique
+   # Vary kite density holding clique size constant
+```

### 2025-09-20 analysis.qmd
poli plots

--- 2025-09-13 analysis.qmd
@@
 
+## Political Data
+
+```{r Loading TestPolitical Data}
+   poli1 <- as.matrix(read.csv(here("Data", "poli1.csv")))
+   poli1 <- graph_from_edgelist(poli1, directed = FALSE)
+   poli2 <- as.matrix(read.csv(here("Data", "poli2.csv")))
+   poli2 <- graph_from_edgelist(poli2, directed = FALSE)
+   poli3 <- as.matrix(read.csv(here("Data", "poli3.csv")))
+   poli3 <- graph_from_edgelist(poli3, directed = FALSE)
+   poli4 <- as.matrix(read.csv(here("Data", "poli4.csv")))
+   poli4 <- graph_from_edgelist(poli4, directed = FALSE)
+   png(here("Plots", "poli1.png"), height = 600, width = 1000)
+   plot.graph.norm(poli1, l = "auto")
+   dev.off()
+   png(here("Plots", "poli2.png"), height = 600, width = 1000)
+   plot.graph.norm(poli2, l = "auto")
+   dev.off()
+   png(here("Plots", "poli3.png"), height = 600, width = 1000)
+   plot.graph.norm(poli3, l = "auto")
+   dev.off()
+   png(here("Plots", "poli4.png"), height = 600, width = 1000)
+   plot.graph.norm(poli4, l = "auto")
+   dev.off()
+```
+
 ## Search

### 2025-09-20 manuscript.tex
9/13 changes
Updates from Overleaf

@@
 With regard to conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side.
-The decisions derive from ensuring the continuation of their position at the center of the network.
+The decisions are based on ensuring their continued position at the center of the network.
 
@@
 According to \citet{everett2010induced-817}, an induced centrality is obtained whenever we calculate the difference that removing a node in the graph makes to some global property of the graph (a graph invariant).
-\citet{everett2010induced-817} suggest taking the sum of the centralities scores of the nodes in the node-deleted subgraph produced by removing a given node as that node's contribution to the centralities of other nodes in the graph, as a measure of that node's centrality.
+\citet{everett2010induced-817} suggests taking the sum of the centrality scores of the nodes in the node-deleted subgraph produced by removing a given node as that node's contribution to the centrality of other nodes in the graph, as a measure of that node's centrality.
 They propose examples extending this idea to the classical centrality measures like degree, closeness, and betweenness \citep{freeman79}.
@@
 The causes of this regularity, and the reasons for its occasional failure, are largely based on consideration of valence.
-Positive or negative affect drive the resulting triadic relations.
+Positive or negative affect drives the resulting triadic relations.
 The original consideration was for the cognitive balance of the individual, or the psychological congruity of affect by an individual for two objects that they see as causally connected.
-As such, the valenced relationship of any three actors are brought into combined consideration because any two are considered affectively combined through their joint combination as "the parts of a causal unit (Heider 1946:107)."
+As such, the valenced relationship of any three actors is brought into combined consideration because any two are considered affectively combined through their joint combination as ``the parts of a causal unit'' \citep[107]{heider1946attitudes-ff3}.
 
@@
 
-In addition to these explanations, the distinction measure also reveals the utility of a distinction based theory of triadic closure.
+In addition to these explanations, the distinction measure also reveals the utility of a distinction-based theory of triadic closure.
 Figure 3 \textit{Model (a)} and Table 4 present a graph and corresponding measures of near-neighbor triadic closure.
 The distinction of nodes 1 and 6 increases to .106, compared to 0 in the circle graph, while all other nodes fall below 0 due to the reverberating effects of the new connection.
-Notably, node 7 increases in eigenvector status from the combination, but overall decrease in scaled distinction due to the tie.
+Notably, node 7 increases in eigenvector status from the combination, but overall decreases in scaled distinction due to the tie.
 This example demonstrates the fragility of the circle graph as an equality condition in a distinction-based theoretical framework, as there are opportunities for mutual increases in distinction through triadic closure.
@@
 Node 7 is worse off due to the structure of the circle graph, rather than because it will always be worse off under all conditions.
-If Node 7 is actually highly central to the graph, near neighbor triadic closure can be distinction increasing.
-Beyond questions of balancing valence as is the current framework for understanding triadic closure, a distinction-based theoretical framework can explain the propensity towards triadic closure, but also its failure to form depending on the initial patterning of relationships.
+If Node 7 is actually highly central to the graph, near-neighbor triadic closure can be distinguished beyond questions of balancing valence, as is the current framework for understanding triadic closure.
+A distinction-based theoretical framework can explain the propensity towards triadic closure, but also its failure to form, depending on the initial patterning of relationships.
 
@@
 What the difference between these two examples suggests is that, based on considerations for distinction, the initial spread of social organization occurs locally through the triadic balance of near neighbors.
-This would suggest that the natural form of organizational formation is the pyramid formed from combinations of local triads that are further connected by brokers or welds creating structural folds.
+This suggests that the natural form of organizational formation is a pyramid formed from combinations of local triads, further connected by brokers or welds, which create structural folds.
 However, the transitivity created by the initial triad formation would spread quickly throughout the network, making welding structural folds a highly advantageous strategy for members of triads who could facilitate that connection, which is further explored below.
@@
 The resulting measurement scores are in Table 2.
-While node 1 maintains high eigenvector centrality, the eigenvector centrality of the other nodes increases, while their constraint decreases.
+While node 1 maintains a high status score, the status of the other nodes increases, while their constraint decreases.
 It is actually the constraint of Node 1 that increases, reaching 1.00 because all its neighbors are maximally interconnected in their respective subgroups.
@@
 %brokerage and structural folds Figure 4
-\begin{figure}[H]
+\begin{figure}
     \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}

### 2025-09-27 analysis.qmd
new graphs who dis

@@
 
+```{r Kites and Extended Networks}
+   k3 <- add_vertices(c3, 1)
+   k3 <- k3 + edge(1, 4)
+   r6 <- add_vertices(make_ring(6), 1)
+   r6 <- r6 + edge(1, 7)
+   c10 <- add_vertices(make_full_graph(10, directed = FALSE), 1)
+   c10 <- c10 + edge(1, 11)
+```
+
+```{r}
+   r10 <- make_ring(10)
+   r10 <- add_edges(r10, c(1,3, 1,9, 1,4, 1,8, 1,5, 1,7, 1,6))
+   V(r10)$name <- as.character(1:10)
+   V(c5)$name <- as.character(1:5)
+   h <- r10 + c5
+   h <- del.names(h)
+   c5 <- del.names(c5)
+   circ <- layout_(h, in_circle())
+   plot(h, layout = circ)
+   h1 <- add_vertices(h, 1) + edge(1, 11)
+   h2 <- add_vertices(h, 1) + edge(2, 11)
+   h3 <- add_vertices(h, 1) + edge(10, 11)
+   set.seed(456)
+   kr <- make_ring(10)
+   kr <- add_edges(kr, c(1,3, 1,9, 2,4, 5,7, 4,6, 6,8, 7,9, 10,8, 10,2, 3,5))
+   kr1 <- add_vertices(kr, 1) + edge(1, 11)
+   plot.graph.norm(kr1, l = "circle")
+```
 ## Medici

### 2025-09-27 analysis.qmd
new new plots

--- 2025-09-20 analysis.qmd
@@
 
+```{r Kites and Extended Networks}
+   k3 <- add_vertices(c3, 1)
+   k3 <- k3 + edge(1, 4)
+   r6 <- add_vertices(make_ring(6), 1)
+   r6 <- r6 + edge(1, 7)
+   plot.toys(r6, "circle-edge.png", "circle")
+   c10 <- add_vertices(make_full_graph(10, directed = FALSE), 1)
+   c10 <- c10 + edge(1, 11)
+   plot.toys(c10, "ten-clique-edge.png", "auto")
+```
+
+```{r}
+   r10 <- make_ring(10)
+   r10 <- add_edges(r10, c(1,3, 1,9, 1,4, 1,8, 1,5, 1,7, 1,6))
+   V(r10)$name <- as.character(1:10)
+   V(c5)$name <- as.character(1:5)
+   h <- r10 + c5
+   h <- del.names(h)
+   c5 <- del.names(c5)
+   h1 <- add_vertices(h, 1) + edge(1, 11)
+   h2 <- add_vertices(h, 1) + edge(2, 11)
+   h3 <- add_vertices(h, 1) + edge(10, 11)
+   plot.toys(h, "wheel-clique.png", "auto")
+   plot.toys(h1, "wheel-clique-edge-star.png", "auto")
+   plot.toys(h2, "wheel-clique-edge-clique.png", "auto")
+   plot.toys(h3, "wheel-clique-edge-peri.png", "auto")
+   set.seed(456)
+   kr <- make_ring(10)
+   kr <- add_edges(kr, c(1,3, 1,9, 2,4, 5,7, 4,6, 6,8, 7,9, 10,8, 10,2, 3,5))
+   plot.toys(kr, "regular-four.png", "auto")
+   kr1 <- add_vertices(kr, 1) + edge(1, 11)
+   plot.toys(kr1, "regular-edge.png", "auto")
+```
 ## Medici

### 2025-09-27 manuscript.tex

@@
 
-Which tells us that the distinction of the peripheral node in the star graph is proportional to its own (scaled) status, discounted by the distinction of the star node divided by the same scaling factor.
+This tells us that the distinction of the peripheral node in the star graph is proportional to its own (scaled) status, discounted by the distinction of the star node divided by the same scaling factor.
 
@@
 This long tie stratifies the network even more than in Model (c), bringing Nodes 2 and 7 quite close to 4 and 5.
-The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs as in Model (b).
+The formation of the long tie served to bolster the individual distinction of 2 and 7 more than the formation of the tie that would create the completely connected subgraphs, as in Model (b).
 In fact, all nodes except 3 and 6 have higher distinction in such a case.
@@
 % in the normalized kite graph, 1.0, the other get close, decreases the scalar, evs don't mean anything
-%computtional experiment where you make kite less dense, or size of kite
+% computational experiment where you make kite less dense, or size of kite
 %kite graph-outsider breaks mechanical solidarity
@@
 This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs.
-While a star graph clearly creates a hierarchy, when additional weight is added to the broker's alters, the hierarchy can be flipped, especially when they form denser subgraphs.
+While a star graph clearly creates a hierarchy, adding weight to the broker's alters can flip the hierarchy, particularly when they form denser subgraphs.
 This is in keeping with the observed structural holes above.

### 2025-11-09 analysis.qmd
do it

--- 2025-09-20 analysis.qmd
@@
 
+```{r Kites and Extended Networks}
+   k3 <- add_vertices(c3, 1)
+   k3 <- k3 + edge(1, 4)
+   r6 <- add_vertices(make_ring(6), 1)
+   r6 <- r6 + edge(1, 7)
+   plot.toys(r6, "circle-edge.png", "circle")
+   c10 <- add_vertices(make_full_graph(10, directed = FALSE), 1)
+   c10 <- c10 + edge(1, 11)
+   plot.toys(c10, "ten-clique-edge.png", "auto")
+   tab.cent(distinction(c10), name = "ten-clique-edge", 
+   label = "cten", rownames = c("1", "2, 3, 4, 5, 6, 7, 8, 9, 10", "11"),
+   caption = "Distinction centrality scores for the ten clique plus pendant graph.")
+   r10 <- make_ring(10)
+   r10 <- add_edges(r10, c(1,3, 1,9, 1,4, 1,8, 1,5, 1,7, 1,6))
+   V(r10)$name <- as.character(1:10)
+   V(c5)$name <- as.character(1:5)
+   h <- r10 + c5
+   h <- del.names(h)
+   c5 <- del.names(c5)
+   h <- add_edges(h, c(3,10))
+   h1 <- add_vertices(h, 1) + edge(1, 11)
+   h2 <- add_vertices(h, 1) + edge(2, 11)
+   h3 <- add_vertices(h, 1) + edge(10, 11)
+```
+
+```{r}
+   plot.toys(h, "wheel-clique.png", "auto")
+   plot.toys(h1, "wheel-clique-edge-star.png", "auto")
+   plot.toys(h2, "wheel-clique-edge-clique.png", "auto")
+   plot.toys(h3, "wheel-clique-edge-peri.png", "auto")
+   set.seed(456)
+   kr <- make_ring(10)
+   kr <- add_edges(kr, c(1,3, 1,9, 2,4, 5,7, 4,6, 6,8, 7,9, 10,8, 10,2, 3,5))
+   plot.toys(kr, "regular-four.png", "auto")
+   kr1 <- add_vertices(kr, 1) + edge(1, 11)
+   plot.toys(kr1, "regular-edge.png", "auto")
+```
 ## Medici

### 2025-11-09 manuscript.tex

@@
 
+%%% FIGURE 5 KITE GRAPHS
+\begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
+    \centering
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
+            \caption{Three-Clique/Wheel}
+            \label{fig:sf}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
+            \caption{Six-Node Wheel}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
+            \caption{Six-Clique}
+            \label{fig:sf}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
+            \caption{Ten-Clique}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique.png}
+            \caption{Three Levels of Hierarchy}
+            \label{fig:classicbrokerage3}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-star.png}
+            \caption{Kite Connects to Highest Distinction Node}
+            \label{fig:classicbrokerage3}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-clique.png}
+            \caption{Kite Connects to Moderate Distinction Node}
+            \label{fig:twoconnected}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-peri.png}
+            \caption{Kite Connects to Lowest Distinction Node}
+            \label{fig:circleweld}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
+            \caption{Kite Connects to Moderate Distinction Node}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
+            \caption{Kite Connects to Lowest Distinction Node}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
+            \caption{HOLD}
+            \label{fig:sf}
+    \end{subfigure} 
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
+            \caption{HOLD}
+            \label{fig:sf}
+    \end{subfigure} 
+    \caption{Comparison of kite graphs with varying parameters}
+\end{figure}
+
 \input{Tabs/Figure5(kites)}

### 2025-11-10 manuscript.tex

@@
 \begin{document}
-\title{Network Origins of Social Distinction}
+\title{A Network Approach to Social Distinction}
 \author[1]{Author Isaac Jilbert\thanks{isaac.jilbert@gmail.com}}
@@
 \begin{abstract}	
-This paper introduces the concept of network \textit{distinction} and develops a relational metric that captures it.
-The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, where other actors and their actions provide opportunities and constraints to maximize social positioning.
-The basic idea behind the network metric of distinction is to subtract the \textit{autonomy} of each actor within the network from their \textit{constraint}, such that highly autonomous (and therefore less constrained) actors have more distinction.
-Autonomy is given by the focal actor's Eigenvector Centrality score (recording connections to well-placed others), and constraint is defined by the average Eigenvector Centrality score of each actor's neighbors in a hypothetical network where the focal actor is removed (indicating how others would benefit from that actor's exiting the network).
+This paper introduces the concept of network \textit{distinction} and develops a relational metric to capture it.
+The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, in which other actors and their actions provide opportunities and constraints for maximizing social positioning.
+The basic idea behind the network metric of distinction is to subtract each actor's \textit{autonomy} from their \textit{constraint}, so that highly autonomous (and therefore less constrained) actors have greater distinction.
+Autonomy is measured by the focal actor's Eigenvector Centrality score (indicating connections to well-placed others), and constraint is defined by the average Eigenvector Centrality score of each actor's neighbors in a hypothetical network in which the focal actor is removed (indicating how others would benefit from that actor's exit from the network).
 A scalar is then applied to create mathematical and sociological equivalence between autonomy and constraint.
-The resulting node-level measures create a measure of \textit{distinction}, where the uniqueness of an actor's relations is more heavily rewarded than under the standard Eigenvector Centrality score.
-We analyze two classic datasets, Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club, to demonstrate that the observed actions of the agents involved are consistent with the maximization of distinction.
+The resulting node-level measures yield a measure of \textit{distinction}, in which the uniqueness of an actor's relations is more heavily rewarded than under the standard Eigenvector Centrality score.
+We analyze two classic datasets, Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club, to show that the observed actions of the agents involved are consistent with the maximization of distinction.
 We close by outlining how the resulting distinction measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.
@@
 The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation enacted by designated institutional authorities \citep{bourdieu1984distinction}.
-
 In this last respect, the more encompassing notion of \textit{social} distinction, implying an actor's embeddedness in a relational field \citep{erikson2013formalist-400, fuhse2021social-9cb}, is often measured as the shadow counterpart of cultural distinction or collapsed into the concept of status more generally \citep{podolny2010status-1a6}.
-This approach overlooks questions of how network constraints produced by other agents impact the capacity of actors to be distinct.
-A generalized, measured ordering of social distinction that is derivative from a network of concrete social relations would give Bourdieu's generalized conception of distinction a broader methodological base from which to conduct empirical analysis.
+This approach overlooks how network constraints imposed by other agents affect actors' capacity to be distinct.
+A generalized, measured ordering of social distinction, derived from a network of concrete social relations, would give Bourdieu's conception a broader methodological base for empirical analysis.
 
@@
 An actor's position in the field influences their habitus.
-Similarly, their habitus determines their future possibilities within the field, while also shaping the opportunities available to others in the field.
-Actors compete for positions in the field via various forms of capital or resources that are socially agreed upon as desirable within a field \citep{martin2003field}, thereby facilitating the formation of connections that both order and reflect the hierarchy of the field.
-The interaction of the desirability and uniqueness of the capitals possessed by an individual determines their place in the field's positional hierarchy.
+Similarly, their habitus determines their future possibilities within the field while also shaping the opportunities available to others.
+Actors compete for positions in the field via various forms of capital or resources that are socially agreed upon as desirable within the field \citep{martin2003field}, thereby facilitating the formation of connections that both order and reflect the field's hierarchy.
+The interaction between an individual's desirability and the uniqueness of their capital determines their place in the field's positional hierarchy.
 
 Bourdieu \citeyearpar{bourdieu1984distinction} most famously used the conceptualization of distinction to explain the persistence of the relationship between class and cultural hierarchies.
-Cultural elites in France distinguished themselves from their inferiors by adopting differentiated cultural practices that had undergone a process of consecration, which set them apart from the common.
+Cultural elites in France distinguished themselves from their inferiors by adopting practices that had undergone a process of consecration, thereby setting them apart from the common.
 There is a strong correlation between those in the position of cultural and economic elites.
 Still, such a correlation is not guaranteed at the individual level, even if it is relevant at the field level.
+
 While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}.
@@
 The field of action refers to the agency of actors actively advancing their interests.
-In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be upset by positional transformations.
+In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be disrupted by the actor's positional transformations.
 
 In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}.
-Translated into network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle reflects the constraints that neighbors impose on an actor.
+Translated into network terms, Bourdieu's field of action can be understood as the network's status hierarchy, while the field of struggle reflects the constraints neighbors impose on an actor.
 An actor with high influence is well-connected to others who can be mobilized for effective action.
 An actor with high autonomy is not constrained by their pattern connections or forced into action by them \citep{burt76}.
-We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy.
-Nevertheless, we use ``status" and ``autonomy" below as general terms to describe the ability of actors to take action versus the level of imposition from the forces of constraint.
-
-In developing a broader understanding and measure of social distinction, actor-level incentives and structural impediments to action become apparent.
-When we understand the underlying motivation that actors have to proactively reshape their network connections to achieve more distinct positions, historical patterns of network change can be better accounted for and, in some cases, even properly forecasted.
+We often use context-specific words to denote position in the hierarchy and the ability to act within it.
+Nevertheless, we use ``status" and ``autonomy" below as general terms to describe the actors' ability to maneuver for better positioning against the level of constraint imposed by external forces, which usually means other actors and their relations.
+
+In developing a broader understanding and measure of social distinction, the interplay between actor-level incentives and structural impediments to action becomes apparent.
+When we understand the underlying motivations that drive actors to proactively reshape their network connections to achieve more distinct positions, historical patterns of network change can be better accounted for and, in some cases, even predicted.
 
 \subsection{Position as the Relational Basis for a Distinction Measure}
-Bourdieu's separation of distinction into habitus and position is not a sociological problem in itself, but rather creates the analytical challenge of how an actor's network position generates dispositions and how these dispositions, in turn, create opportunities for network mobility.
-Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when creating a network measure of distinction, only the relational basis of position can be considered.
-
-However, to the extent that position and habitus reflect each other through their symbiotic fabrication, the ability to empirically capture only one of the two components is sufficiently accurate to measure a social system's distinction hierarchy with confidence over a short window of time.
+Bourdieu's separation of distinction into habitus and position is not a sociological problem in itself; rather, it poses the analytical challenge of how an actor's network position generates dispositions, and how these dispositions, in turn, create opportunities for network mobility.
+Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when developing a network measure of distinction, only the relational basis of position can be considered.
+
+However, to the extent that position and habitus reflect each other through their symbiotic connection, empirically capturing only one of the two components is sufficient to measure a social system's distinction hierarchy with confidence over a short time window.
 Actors should not hold a network position that does not align with their habitus, and their current habitus and social position determine their ability to radically change positions.
@@
 
-To establish a firm theoretical foundation for the measure of distinction, it is first essential to make explicit the relationship between empirical data and social theory that forms the basis of social network analysis.
-Network measures are fundamentally based on the idea that researchers are capturing a relationship between two objects in some way.
+To establish a firm theoretical foundation for the measure of distinction, it is first essential to make explicit the relationship between empirical data and social theory that underlies social network analysis.
+Network measures are fundamentally based on the idea that researchers are capturing a relationship between two agents.
 A tie between two nodes captures, in some way, their connection, however it is defined.
-Such connections can be broadly classified as mutual, in the case where the relationship quality is equal in both directions, or directional, in the case where the qualities are unequal.
+Such connections can be broadly classified as mutual, when the relationship quality is equal in both directions, or directional, when the qualities are unequal.
 In the absence of direct measurement of qualities, however, many networks are measured as consisting of mutual ties.
-However, even in the case of networks composed of only mutual ties, hierarchy can still be assessed from the pattern of relationships.
+However, even in networks composed solely of mutual relations, hierarchy can still be assessed from the pattern of relationships.
 In such networks, we can still rank the direction of power and deference through the absence of ties between lower and higher nodes.
-For example, in an organizational pyramid, we can detect the CEO by observing the presence of ties with vice presidents and the absence of ties with middle management and production workers.
-We can do this through the measurement of a node's network status.
+For example, in an organizational pyramid, we can detect the CEO by observing the presence of relations with vice presidents and the absence of ties with middle management and production workers.
+We can do this by measuring a node's network status.
 
@@
 Status refers to the internal stratification of all network members, along with the connections of deference and obligation.
-In the case of politics, status refers to the ability to access those who themselves have higher levels of access, with those most central to the access network having the authority to make decisions.
+In politics, status refers to the ability to access those who themselves have greater access, with those most central to the access network having the authority to make decisions.
 This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972factoring-03e}.
 Status is higher for actors when the people they are connected to are themselves influential, and accessibility is merely a political reframe of the context.
-The internal stratification of individuals is determined by who has greater connections to those with even greater connections, with those having few connections to other important people being at the bottom of the hierarchy \citep{bonacich1972factoring-03e}.
+The internal stratification of individuals is determined by who has stronger connections to those with even stronger connections, with those having few connections to other important people at the bottom of the hierarchy \citep{bonacich1972factoring-03e}.
 
@@
 Being structurally unique minimizes the social constraints placed on an individual.
-The tighter the interconnections of the group, the more its pressures constrain the individual.
+The tighter the group's interconnections, the more its pressures constrain the individual.
 In politics, this aspect of distinction takes the form of constraint.
-When an actor is one of many densely interconnected individuals, their ability to act contrary to their networked group is greatly weakened.
+When an actor is one of many densely interconnected individuals, their ability to act contrary to their group is significantly weakened.
 However, when one is only a weakly dependent and connected member of a group, they have a greater ability to operate independently.
-Their ability to act is a source of distinction as they are able to take independent action.
+Their ability to act is a source of distinction, as they can take independent action.
 The question of structural uniqueness and autonomy is the same underlying consideration as captured by measures of path centrality.
@@
 \citet[1263-4]{padgett1993robust} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions.
-Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because strong actions favoring one side would upset the other side.
-However, such a constraint was not an issue because Medici’s interests were in perpetuating his central role as broker, and, as the only source of interest, he was able to maintain the position.
-With regard to conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side.
+Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because decisive steps favoring one side would upset the other.
+However, this constraint was not an issue because Medici’s interests lay in perpetuating his central role as broker, and, as the only source of interest, he was able to maintain his position.
+When conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side.
 The decisions are based on ensuring their continued position at the center of the network.
 
-The interaction of influence and autonomy combines to create an actor’s overall distinction in the network.
+The interaction between influence and autonomy creates an actor’s overall distinction in the network.
 The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction.
 An increase in one aspect can often, but not necessarily, lead to a decrease in the other.
-For example, a connection with someone with high accessibility can lead to a decrease in one’s autonomy, and new access comes with new constraints.
+For example, a connection with someone with high accessibility can lead to a reduction of one’s autonomy, and new access comes with new constraints.
 However, the trade-off can maximize one’s overall distinction, so there are gains from the connection.
@@
 \section{A Generalized Measure of Network Distinction}
-In this section, we present our measure of distinction centrality, which incorporates a scalar adjustment factor to mitigate arbitrary scaling issues.
+In this section, we present our measure of distinction centrality, which incorporates a scalar adjustment factor to mitigate issues arising from arbitrary scaling.
 We also indicate the availability of an \textit{R} custom function to facilitate the easy implementation of the measure in further work.
@@
 A distinction measure can reflect this by considering an actor's status and then discounting it by the counterfactual status of their neighbors when the focal actor is absent from the network.
-The more reliant an actor's neighbors are on the actor for their status, the lower the focal actor's ability to exert influence over them, and thus the lower their distinction.
+The more reliant an actor's neighbors are on the focal actor for their status, the lower the focal actor's ability to exert influence over them, and thus the lower the focal actor's distinction.
 In other words, autonomy is determined by how much one's neighbors rely on you to maintain their advantageous position in the network.
@@
     \end{subfigure}
-    \caption{Comparison of betweenness brokerage and a structural fold goes here}
+    \caption{Comparison of betweenness brokerage and a structural folds Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
 \end{figure}
@@
     \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
-            \caption{Six-Node Wheel}
+        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-edge.png}
+            \caption{Six-Node Circle}
             \label{fig:sf}
@@
     \end{subfigure} 
-    \caption{Comparison of kite graphs with varying parameters}
+    \caption{Comparison of kite graphs with varying parameters.
+Distinction Centrality in toy graphs.
+Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
 \end{figure}
@@
 \subsection{Capital Conversion as Network Integration of Fields}
+
+%Add portion on pop[ culture being a low constraint activity]
+%distinction signals position which is why it's so important
+
 One of the problems with the relationship between multiple fields is how capital might be converted between fields.

### 2025-11-10 analysis.qmd
small world

--- 2025-09-27 analysis.qmd
@@
    r6 <- r6 + edge(1, 7)
+   plot.toys(r6, "circle-edge.png", "circle")
    c10 <- add_vertices(make_full_graph(10, directed = FALSE), 1)
    c10 <- c10 + edge(1, 11)
-```
-
-```{r}
+   plot.toys(c10, "ten-clique-edge.png", "auto")
+   tab.cent(distinction(c10), name = "ten-clique-edge", 
+   label = "cten", rownames = c("1", "2, 3, 4, 5, 6, 7, 8, 9, 10", "11"),
+   caption = "Distinction centrality scores for the ten clique plus pendant graph.")
    r10 <- make_ring(10)
@@
    c5 <- del.names(c5)
-   circ <- layout_(h, in_circle())
-   plot(h, layout = circ)
+   h <- add_edges(h, c(3,10))
    h1 <- add_vertices(h, 1) + edge(1, 11)
    h2 <- add_vertices(h, 1) + edge(2, 11)
-   h3 <- add_vertices(h, 1) + edge(10, 11)
+   h3 <- add_vertices(h, 1) + edge(8, 11)
+   plot.toys(h, "wheel-clique.png", "auto")
+   plot.toys(h1, "wheel-clique-edge-star.png", "auto")
+   plot.toys(h2, "wheel-clique-edge-clique.png", "auto")
+   plot.toys(h3, "wheel-clique-edge-peri.png", "auto")
+```
+
+```{r Small Worlds}
    set.seed(456)
@@
    kr <- add_edges(kr, c(1,3, 1,9, 2,4, 5,7, 4,6, 6,8, 7,9, 10,8, 10,2, 3,5))
+   krsw <- add_edges(kr, c(4,9))
+   plot.toys(kr, "regular-four.png", "auto")
+   plot.toys(krsw, "small-world.png", "auto")
    kr1 <- add_vertices(kr, 1) + edge(1, 11)
-   plot.graph.norm(kr1, l = "circle")
+   kr1sw <- add_edges(kr1, c(4,9))
+   plot.toys(kr1, "regular-edge.png", "auto")
+   plot.toys(kr1sw, "small-world-edge.png", "auto")
 ```

### 2025-11-10 analysis.qmd
tabs

@@
 
+```{r}
+   tab.cent(distinction(h), name = "wheel-clique", 
+   label = "wc", rownames = c("1", "2, 4", "3, 5", "6, 10", "7, 9", "8"),
+   caption = "Distinction centrality scores for the wheel plus clique graph.")
+   tab.cent(distinction(h1), name = "wheel-clique-pendant1", 
+   label = "wcp1", rownames = c("1", "2, 4", "3, 5", "6, 10", "7, 9", "8", "10"),
+   caption = "Distinction centrality scores for the wheel plus clique plus pendant graph.")
+   tab.cent(distinction(h2), name = "wheel-clique-pendant2", 
+   label = "wcp2", rownames = c("1", "2, 4", "3, 5", "6, 10", "7, 9", "8", "10", "11"),
+   caption = "Distinction centrality scores for the wheel plus clique plus pendant graph.")
+   tab.cent(distinction(h3), name = "wheel-clique-pendant3", 
+   label = "wcp3", rownames = c("1", "2, 4", "3, 5", "6, 10", "7, 9", "8", "11"),
+   caption = "Distinction centrality scores for the wheel plus clique plus pendant graph.")
+```
+
 ```{r Small Worlds}
@@
    plot.toys(kr, "regular-four.png", "auto")
-   plot.toys(krsw, "small-world.png", "auto")
+   plot.toys(krsw, "small-world.png", "circle")
    kr1 <- add_vertices(kr, 1) + edge(1, 11)

### 2025-11-10 analysis.qmd
sw who dis

@@
    plot.toys(h, "wheel-clique.png", "auto")
-   plot.toys(h1, "wheel-clique-edge-star.png", "auto")
-   plot.toys(h2, "wheel-clique-edge-clique.png", "auto")
-   plot.toys(h3, "wheel-clique-edge-peri.png", "auto")
+   plot.toys(h1, "wheel-clique-edge-star.png", "fr")
+   plot.toys(h2, "wheel-clique-edge-clique.png", "kk")
+   plot.toys(h3, "wheel-clique-edge-peri.png", "kk")
 ```
@@
    kr <- add_edges(kr, c(1,3, 1,9, 2,4, 5,7, 4,6, 6,8, 7,9, 10,8, 10,2, 3,5))
-   krsw <- add_edges(kr, c(4,9))
-   plot.toys(kr, "regular-four.png", "auto")
-   plot.toys(krsw, "small-world.png", "circle")
+   sw1 <- add_edges(kr, c(4,9))
+   plot.toys(kr, "regular-four.png", "circle")
+   plot.toys(sw1, "small-world1.png", "circle")
+   sw2 <- add_edges(sw1, c(7,2))
+   plot.toys(sw2, "small-world2.png", "circle")
+   sw3 <- add_edges(sw2, c(6,1))
+   plot.toys(sw3, "small-world3.png", "circle")
    kr1 <- add_vertices(kr, 1) + edge(1, 11)
    kr1sw <- add_edges(kr1, c(4,9))
-   plot.toys(kr1, "regular-edge.png", "auto")
-   plot.toys(kr1sw, "small-world-edge.png", "auto")
+   plot.toys(kr1, "regular-edge.png", "circle")
+   plot.toys(kr1sw, "small-world-edge.png", "kk")
 ```
